### 2021-03-29 Writeups/paper.tex
Done with data

\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{gensymb, comment}
\usepackage{textcomp}
\usepackage{threeparttable}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{setspace} 
\doublespacing
\usepackage{indentfirst}
\setlength{\parindent}{25pt}
\usepackage{bbm}
\usepackage{multicol}
\usepackage{makecell}
\usepackage{booktabs}
\newtheorem{prop}{Proposition} 
\newtheorem{assumption}{Assumption} 
\newtheorem{implication}{Implication} 
\usepackage{longtable}

\setcounter{totalnumber}{8}

\title{Winter weather on exam days and admission for a prestigious university in Japan}%: \\ Empirical analysis on auditing reports in Brazil}
%\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu. The authors would like to thank Laura Schechter for her numerous feedback and support. We are also grateful to Joshua Deutschmann, Paul Dower, Jeremy Foltz, Priya Mukherjee, Andrew Stevens, and seminar participants at the UW-Madison Agricultural and Applied Economics department for helpful comments and suggestions. Any errors in this draft are the sole responsibility of the authors.}}
\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu}}
\date{\today \\ \vspace{1cm} Preliminary draft \\ Please do not cite or circulate}

\begin{document}

\maketitle
\begin{abstract}
  \singlespacing
     \noindent

  \medskip
  \vspace{1cm}
 \noindent Keywords: Temperature, Education, University admission, Cognitive performance
\end{abstract}

\newpage

\section{Introduction}

External factors can impact various outcomes.
One active area of research is the effect of high temperature on performance at high-stakes exams.
Given the importance of high education for later outcomes, this is nice.

What is missing in the literature is the effect of \textit{low} temperature on performance at exams.

In this study, I analyze the effect of winter weathers on exam outcomes in Japan.
I use the weather on the days of National Center Test for University Admission (Center Test hereafter) and investigate its effect on the admission for the most prestigious university in Japan, the University of Tokyo (UTokyo henceforth).

If I use a middle-ranked university, reduction in admission share can be attributed to both lower and higher scores:
while students with lower scores can fail to get into the university, students with higher scores can choose to apply to and get admitted to higher-ranked universities.
Since UTokyo is the most prestigious university in Japan (** cite some university ranking **), it is unlikely that students who get high scores in Center Test go to better universities.\footnote{
  Medical departments in several universities are higher-ranked than UTokyo based on standard score.
  However, the career paths for those in the non-medical department of UTokyo and medical departments in universities are substantially different:
  while most students graduating from medical departments become medical doctors, the majority of students from UTokyo become bureaucrats, work for private firms, or go to graduate schools.
  Hence, it is unlikely that high scores at Center Test induce students who would otherwise get into UTokyo to go to a medical department.
}
Therefore, if I observe a reduction in admission share, I consider this as an evidence that the performance in Center Test is negatively affected.

\section{Background}

For admission for most (especially almost all public) universities, students are required to take two exams.
The first stage is Center Test.
Students take an exam on consecutive two days (Saturday and Sunday on mid January).
While different students can choose which subjects to take, most universities require students to take exams on math, English, language, natural science, and social science.
Questions are multiple-choice and common for all exam takers across Japan.
Exam takers do not receive their exact scores until the next May at earliest.
However, since they can record their answers to the exam booklets and can bring them back home, they know their scores by comparing their own answers and correct answers, which are made public through newspaper or websites of cramming schools.
High-school seniors take the test at designated cites in the area where their high schools are located.
On the other hand, high-school graduates are assigned to test cites in the area where the homes used in their application forms are located.

After taking Center Test, students apply for public and private universities.\footnote{
  There are private universities who accept applications before Center Test.
}
Applicants for public universities typically take the second-stage exam.
This exam is made by each university, and students go to the universities and take the exam.
In other words, every applicant for a university takes the exam at the same location.

For public universities, there are three exam periods: the first one is typically at the end of February, the second one is on the first week of March, and the third one is typically around March 10th.
While different universities accept applications for different periods, most universities have only one (typically the first period) or two (typically the first and the third periods) periods.
UTokyo has two exam periods, the first and the third ones, although most of the admissions are provided for exam takers during the first exam period.

For UTokyo, scores at Center Test are used for two purposes.
First, the scores are used for eligibility to take the second-stage exam.
Thresholds varying across years and across majors are set, and if scores at Center Test are below the thresholds, students cannot take the second-stage exam.
Since the thresholds are announced after the application, exam takers do not know if their scores are above or below the thresholds.

Secondly, the scores at Center Test are taken into consideration for admission.
The final score of a students is calculated by the weighted average of exam scores at the first- and second-stage exams.

\section{Data}

I use two sets of data: weather and admission information for UTokyo.
For weather information, I get data from Japan Meteorological Agency.
Their website maintains the past weather across Japan.
In this study, based on hourly weather on exam days at prefecture capitals, I use average weathers between 6AM to 6PM.
Prefecture capitals tend to be most populated in each prefecture, and in many prefectures highly-ranked high schools from which many students go to UTokyo are located at prefecture capitals.
%\footnote{
%  According to inter-edu, \url{https://www.inter-edu.com/univ/2019/jisseki/todai/ranking/}
%}

For admission information for UTokyo, I use University Basic Information maintained by National Institution for Academic Degrees and Quality Enhancement of Higher Education.
This data contains information from 2012 to 2020 on the number of admitted students by prefectures at which their high schools are located.
I create the admission share of each prefecture, which is the ratio of the number of admitted students from a prefecture to the number of all admitted students.

The summary statistics are provided in Table \ref{tab:sum_stat}.
While the mean of the admission share (\%) is $2.08$,\footnote{
  Since there are admissions from abroad, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
} the distribution is starkly skewed.
As shown in Figure \ref{fig:admission_map}, many prefecture have less 1\% shares.
Also, the admission shares of the top 5 prefectures total more than 60\%.
This results in a small median admission share, $0.79$.

\begin{table}[H]
  \centering
  \caption{Summary Statistics}
  \resizebox{\linewidth}{!}{
  \input{"../Output/tex/sum_stat.tex"}
  }
  \label{tab:sum_stat}
  \footnotesize
  \begin{tablenotes}
    \item 
      Notes:
      Admission share (\%) is the share of newly admitted students to the University of Tokyo from each prefecture.
      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
  \end{tablenotes}
\end{table}

\begin{figure}[H]
  \centering
  \caption{Map of admission shares (\%) (average across years)}
  \includegraphics[width = 0.9\textwidth]{../Output/images/admission_map.png}
  \label{fig:admission_map}
  \footnotesize
  \begin{tablenotes}
    \item Notes:
      This map shows the admission shares (\%) for the University of Tokyo from each prefecture.
      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
      Average of the shares across years is shown in the map.
      Although not shown in the legend due to the lack of the space, the lightest color in the map means the admission share between 0 to 0.5\% 
  \end{tablenotes}
\end{figure}

\section{Empirical Strategy}

The objective of the analysis is to analyze the effect of temperature and other weather variables on exam days on the admission share for UTokyo.
The outcome variable, $Y_{jt}$ is the admission share (\%) for UTokyo of a prefecture $j$ in year $t$.
Let $T_{jt}$ be average temperature on exam days in $j$ in year $t$.
I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
I include other weather variables such as rainfall, snowfall, and cumulated snow on exam days as a vector $X_{jt}$.
As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
Finally, the error term is represented as $\epsilon_{jt}$.

I run the following regression equation:
\begin{equation*}
  Y_{jt} = f(T_{jt}) + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
\end{equation*}
I exploit the variation of temperature on exam days, which I consider exogenous after controlling for prefecture-specific time-variant factors and time-varying aggregate shocks through prefecture and year fixed effects.
As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variation in temperature on exam days.\footnote{
  Similar figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
}

One potential problem in the analysis is that a students from a high school in a prefecture does not necessarily take Center Test in the same municipality.
This means that, for these students, the weather at the exam cites are measured with errors.
The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get in any university for the first year and retake Center Test next year in his home prefecture.
I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
Hence, this classical measurement error can make the estimates conservative.

\begin{figure}[H]
  \centering
  \caption{Average temperature on two exam days in each prefecture each year}
  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
  \label{fig:temperature_diff}
  \footnotesize
  \begin{tablenotes}
    \item Notes:
      Temperature at prefecture capitals between 6AM and 6PM on days of Center Test is used.
      Average across two test days in each year is shown in the figure.
      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
  \end{tablenotes}
\end{figure}

\section{Results}

\subsection{Main Results}

The main empirical results are provided in Table \ref{tab:main_reg}.
The column (1) shows the result with a linear specification.
While the point estimate is positive, which means admission shares are higher if an exam is held on warmer days, it is statistically insignificant. 
The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impacts of cold weather. 
Since the mean admission share is $2.08$\%, the coefficient on the lowest temperature bins means that reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest bin, the admission share decreases by 9\%.
Moreover, due to the stark skewness in the distribution of admission shares, the median admission share is $0.79$.
Therefore, the same temperature change decreases the admission share by 22\% of the median value.
Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in the column (1) could not capture the non-linear effect of temperature and why the coefficient is statistically insignificant.
Although for a quite different temperature range, similar plateau effects are found in Park (2020) and Melo and Suzuki (2021).

In column (3) and (4), I add other weather variables.
While temperature coefficients are barely affected, I find that rainfall and snowfall during exam time do not impact the admission shares.
On the other hand, the cumulated snow on the ground has a negative impact.
To capture the effect of existence of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
This specification gives a result that, when there is snow on the ground cumulated more than 10cm ($\approx$ 3 feet) decreases the admission share by 0.13 percentage point.

In summary, I find a both statistically and economically significant impacts of weather on exam days.
In particular, the estimation results show that low temperature and snow cumulated on the ground have negative impact on the admission shares for UTokyo.
In the next two subsections, I investigate the mechanisms underlying the findings.

\begin{table}[H]
  \center
  \caption{Regression: Admission share (\%) and weather on exam days}
  \input{"../Output/tex/main_reg.tex"}
  \label{tab:main_reg}
  \small
  \begin{tablenotes}
    \item
      The outcome variable is the admission shares (\%) for the University of Tokyo from each prefecture.
      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
      Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{table}

\subsection{Weather in the morning vs. during exam}

\begin{table}[H]
  \center
  \caption{Regression: Admission share (\%) and weather in the morning vs. during exam}
  \scriptsize
  \input{"../Output/tex/reg_morning_exam.tex"}
  \label{tab:reg_morning_exam}
  \scriptsize
  \begin{tablenotes}
    \item
      The outcome variable is the admission shares (\%) for the University of Tokyo from each prefecture.
      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
      For variables in the morning, I use average weather variables at prefecture capitals between 6AM to 9AM on exam days.
      For variables during the exam, I use average weather variables at prefecture capitals between 9AM to 6PM on exam days.
      Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{table}

\subsection{Preparation vs. Cognitive performance on exam days}

One possible interpretation is that the temperature on exam days capture the weathers before the exam, which can affect preparation for the exam. 
For instance, cold weather can make it hard for students to focus on studying, or snowfalls can prevent students from going to schools or cramming schools for studying.
To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for all the variables. 
Therefore, I consider that the findings in Table \ref{tab:main_reg} are due to the effect of weather variables on the exam days.

\section{Conclusion}

In this paper I study the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
Instead of exam scores, I use the admission share for the most prestigious university in Japan, the University of Tokyo.
To identify the causal impact, I exploiting the variation in weathers at each prefecture on exam days.
Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains unknown.
This study fills the gap and identifies the causal impact of winter weather on the admission.

The results show that both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam days.
Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the admission share of a prefecture by 0.18 percentage point, which is 9\% of the mean admission share, or 22\% of the median admissions share.
Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
Using the weathers in the morning and during the exams, I find a suggestive evidence that the temperature effect is mainly caused by low temperature in the morning.
This result suggest that adverse conditions for exam takers on the way to test cites affect their cognitive performance.

Several implications can be derived from the findings.
First, the result that low temperature in the morning rather than during the exam matters suggest that equipments to improve the condition at the exam sites may have limited impacts.
Rather, investment on recovering students can result in better improvement.
For instance, providing socks and slippers for students whose shoes and socks get wet due to walking through stacked snow.
Also, it may be effective to provide sufficient time before the exam at the exam site so that students can recover in a warm room.
%This study provides guidance on how to set the leveling field for exam takers across Japan.

Secondly, my results have implications on the admission process of universities.
Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measure to pick students.
Examples include extracurricular activities and statement of purposes, which are actively utilized in other countries such as the U.S..
On the other hand, it may be effective to change the weights for Center Test and the second-stage exam.
Since the second-stage exam is held at each university, exam takers are exposed to similar environments.
This rules out the possibility that exam takers at different places are affected differently by their conditions.
Given the importance of college choice, it is desirable that universities take measures to mitigate the effect of nuisance factors on admission.

\appendix

\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand\thefigure{\Alph{section}.\arabic{figure}}
\renewcommand\thetable{\Alph{section}.\arabic{table}}

\section{Appendix figures}\label{sec:appendix_figure}

\begin{figure}[H]
  \centering
  \caption{Average hourly rainfall (m) on two exam days in each prefecture each year}
  \includegraphics[width = 0.9\textwidth]{../Output/images/rainfall_diff.pdf}
  \label{fig:rainfall_diff}
  \footnotesize
  \begin{tablenotes}
    \item Notes:
      Rainfall (mm) at prefecture capitals between 6AM and 6PM on days of Center Test is used.
      Average across two test days in each year is shown in the figure.
      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
  \end{tablenotes}
\end{figure}

\begin{figure}[H]
  \centering
  \caption{Average hourly snowfall (m) on two exam days in each prefecture each year}
  \includegraphics[width = 0.9\textwidth]{../Output/images/snowfall_diff.pdf}
  \label{fig:cum_snow_diff}
  \footnotesize
  \begin{tablenotes}
    \item Notes:
      Snowfall (m) at prefecture capitals between 6AM and 6PM on days of Center Test is used.
      Average across two test days in each year is shown in the figure.
      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
  \end{tablenotes}
\end{figure}

\begin{figure}[H]
  \centering
  \caption{Average cumulated snow (m) on two exam days in each prefecture each year}
  \includegraphics[width = 0.9\textwidth]{../Output/images/cum_snow_diff.pdf}
  \label{fig:cum_snow_diff}
  \footnotesize
  \begin{tablenotes}
    \item Notes:
      Cumulated snow (m) at prefecture capitals between 6AM and 6PM on days of Center Test is used.
      Average across two test days in each year is shown in the figure.
      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
  \end{tablenotes}
\end{figure}

%\begin{figure}[H]
%  \centering
%  \caption{Map of average temperature on two exam days (average across years)}
%  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_map.png}
%  \label{fig:temperature_map}
%  \footnotesize
%  \begin{tablenotes}
%    \item Notes:
%      Temperature at prefecture capitals between 6AM and 6PM on days of Center Test is used.
%      Average of the temperatures across years is shown in the map.
%  \end{tablenotes}
%\end{figure}
%
%\begin{figure}[H]
%  \centering
%  \caption{Map of average cumulated snow (m) on two exam days (average across years)}
%  \includegraphics[width = 0.9\textwidth]{../Output/images/cum_snow_map.png}
%  \label{fig:cum_snow_map}
%  \footnotesize
%  \begin{tablenotes}
%    \item Notes:
%      Cumulated snow (m) on the ground at prefecture capitals between 6AM and 6PM on days of Center Test is used.
%      Average of the values across years is shown in the map.
%  \end{tablenotes}
%\end{figure}

\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand\thefigure{\Alph{section}.\arabic{figure}}
\renewcommand\thetable{\Alph{section}.\arabic{table}}

\section{Appendix tables}

\begin{table}[H]
  \center
  \caption{Regression: Admission share (\%) and average weather for 10 days before exam}
  \input{"../Output/tex/reg_pre10.tex"}
  \label{tab:reg_pre10}
  \small
  \begin{tablenotes}
    \item
      The outcome variable is the admission shares (\%) for the University of Tokyo from each prefecture.
      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
      I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
      Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{table}

\end{document}

### 2021-03-29 Codes/R/admission_clean.R

@@ -1,0 +1,127 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load admission information =================
+
+load_admission_df <- function(file_path, year) {
+  
+  print(year)
+  
+  if (year <= 2015) {
+    output_df <- read_excel(file_path, skip = 2) %>% 
+      rename(
+        univ = 大学名,
+        department = 学部名,
+        gender = 県別入学者数
+      )
+  } else {
+    output_df <- read_excel(file_path, skip = 2) %>% 
+      rename(
+        univ = 学校名,
+        department = 学部名,
+        gender = 性別
+      )
+  }
+  
+  output_df <- output_df %>% 
+    filter(univ == "東京大学") %>% 
+    filter(str_detect(department, "文科系|理科系")) %>% 
+    dplyr::select(univ, department, gender, 北海道:その他) %>% 
+    mutate(
+      across(
+        .cols = is.numeric,
+        .fns = ~ replace_na(., 0)
+      )
+    ) %>% 
+    pivot_longer(cols = 北海道:その他, names_to = "prefecture",  values_to = "admission") %>% 
+    mutate(
+      department = str_extract(department, "（(.)*）") %>% str_replace_all("[（）]", ""),
+      department = ifelse(department == "文科系", "Arts", "Sciences"),
+      gender = ifelse(gender == "男", "male", "female")
+    ) %>% 
+    pivot_wider(names_from = gender, values_from = admission, names_prefix = "admission_") %>% 
+    mutate(admission_total = admission_male + admission_female) %>% 
+    # group_by(department) %>% 
+    # mutate(
+    #   across(
+    #     .cols = starts_with("admission"),
+    #     .fns = ~ . / sum(admission_total),
+    #     .names = "{col}_share"
+    #   )
+    # ) %>% 
+    # ungroup() %>% 
+    pivot_wider(names_from = department, values_from = starts_with("admission_")) %>% 
+    mutate(
+      admission_male_share = (admission_male_Arts + admission_male_Sciences) / (sum(admission_total_Arts) + sum(admission_total_Sciences)),
[…]

### 2021-03-29 Codes/R/admission_map.R

@@ -1,0 +1,79 @@
+packages <- c(
+  "rgdal",
+  "sp",
+  "raster",
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer",
+  "RColorBrewer",
+  "kableExtra",
+  "classInt"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load admission information =================
+admission_df <- read_csv(file.path(dropbox_dir, "Data/admission_data.csv"))
+
+# Draw map of average admission shares  ===============
+
+map_Japan <- shapefile(
+  file.path(
+    dropbox_dir,
+    "Data/shapefile",
+    "jpn_admbnda_adm0_2019.shp"
+  )
+)
+map <- shapefile(
+  file.path(
+    dropbox_dir,
+    "Data/shapefile",
+    "jpn_admbnda_adm1_2019.shp"
+  )
+)
+
+admission_df_avg <- admission_df %>% 
+  group_by(prefecture) %>% 
+  summarise_at(vars(admission_total_share), mean)
+
+map@data$ADM1_JA <- str_replace(map@data$ADM1_JA, "県|府", "")
+map@data$ADM1_JA <- str_replace(map@data$ADM1_JA, "東京都", "東京")
+
+map_avg <- merge(map, admission_df_avg, by.x = "ADM1_JA", by.y = "prefecture")
+
+filepath = file.path(git_dir, 'Output/images/admission_map.png')
+png(file = filepath)
+print(
+  spplot(
+    map_avg, 
+    "admission_total_share", 
+    sp.layout = list(map_Japan, lwd = 0.1), 
+    # col.regions = brewer.pal(n = 10, name = "OrRd"),
+    # at = classIntervals(map_avg$admission_total_share, n = 9, style = "quantile", intervalClosure = "right")$brks,
+    col.regions = brewer.pal(n = 9, name = "OrRd"),
+    # cuts = 8,
+    at = c(0, 0.5, 1.0, 2.0, 3.0, 5.0, 10.0, 40.0),
+    par.settings = list(axis.line = list(col = "transparent")),
+    colorkey = list(
+      labels = list(
[…]

### 2021-03-29 Codes/R/regression.R

@@ -1,0 +1,357 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load admission information =================
+admission_df <- read_csv(file.path(dropbox_dir, "Data/admission_data.csv"))
+
+# Load weather information on exam days=================
+weather_exam_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_on_exam_day.csv"))
+
+# Load weather information (previous 10 days) =================
+weather_pre10_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_pre10.csv"))
+
+# Load weather information (Oct, Nov, Dec before the exams) =================
+weather_pre_oct_dec_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_pre_oct_dec.csv"))
+
+# Regression with average weather =====================
+
+reg_df <- left_join(
+  admission_df,
+  weather_exam_df %>% 
+    group_by(prefecture, exam_year) %>% 
+    summarise_all(mean),
+  by = c("prefecture", "year" = "exam_year")
+  ) %>% 
+  left_join(weather_pre10_df, by = c("prefecture", "year" = "exam_year")) %>% 
+  left_join(weather_pre_oct_dec_df, by = c("prefecture", "year" = "exam_year")) %>% 
+  mutate(
+    temp_cut = cut(daytime_temperature_degree, c(-10, 0, 3, 6, 9, 25)),
+    temp_cut = relevel(as.factor(temp_cut), ref = 3),
+    daytime_snowfall_m = daytime_snowfall_cm / 100,
+    daytime_cum_snow_m = daytime_cum_snow_cm / 100,
+    temp_cut_pre10 = cut(temperature_pre10_avg, c(-10, 0, 3, 6, 9, 30)),
+    temp_cut_pre10 = relevel(as.factor(temp_cut_pre10), ref = 3),
+    snowfall_pre10_m = snowfall_pre10 / 100,
+    cum_snow_pre10_m = cum_snow_pre10 / 100,
[…]

### 2021-03-29 Codes/R/sumstat.R

@@ -1,0 +1,81 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer",
+  "kableExtra"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load admission information =================
+admission_df <- read_csv(file.path(dropbox_dir, "Data/admission_data.csv"))
+
+# Load weather information =================
+weather_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_on_exam_day.csv"))
+
+# Regression with average weather =====================
+
+reg_df <- left_join(
+  admission_df,
+  weather_df %>% 
+    group_by(prefecture, exam_year) %>% 
+    summarise_all(mean),
+  by = c("prefecture", "year" = "exam_year")
+  ) %>% 
+  mutate(
+    temp_cut = cut(daytime_temperature_degree, c(-10, 0, 3, 6, 9, 25)),
+    temp_cut = relevel(as.factor(temp_cut), ref = 3),
+    daytime_snowfall_m = daytime_snowfall_cm / 100,
+    daytime_cum_snow_m = daytime_cum_snow_cm / 100
+    )
+
+list(
+  function(x) sum(!is.na(x)), 
+  mean, sd, median, min, max
+) %>% 
+map(
+  function(x) 
+    reg_df %>% 
+    dplyr::select(
+      admission_total_share,
+      daytime_temperature_degree,
+      daytime_precipitation_mm,
+      daytime_snowfall_m,
+      daytime_cum_snow_m
+      ) %>% 
+    summarise_all(x)
+  ) %>% 
+  bind_rows() %>% 
+  as.matrix() %>% 
+  t() %>% 
+  as_tibble() %>% 
+  mutate(
+    V1 = formatC(V1),
+    across(
+      .cols = V2:V6,
+      .fns = ~ formatC(., digits = 2, format = "f")
+    )
+  ) %>% 
+  as.matrix() %>% 
+  set_colnames(NULL) %>% 
+  set_rownames(c(
+    "Admission share (%)",
+    "Temperature (degree C)",
+    "Hourly precipitation (mm)",
+    "Hourly snowfall (m)",
[…]

### 2021-03-29 Codes/R/weather_clean.R

@@ -1,0 +1,150 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Hourly weather ====================
+# Load data
+weather_hour_df <- read_csv(file.path(dropbox_dir, "Data/weather_hourly/all_weather_hour.csv"))
+
+weather_hour_output <- weather_hour_df %>% 
+  group_by(prefecture, year, month, day) %>% 
+  summarise_at(
+      vars(temperature_degree, precipitation_mm, snowfall_cm, cum_snow_cm),
+      mean, na.rm = TRUE
+  ) %>% 
+  left_join(
+    weather_hour_df %>% 
+      filter(hour >= 6, hour <= 18) %>% 
+      group_by(prefecture, year, month, day) %>% 
+      summarise_at(
+          vars(temperature_degree, precipitation_mm, snowfall_cm, cum_snow_cm),
+          mean, na.rm = TRUE
+      ) %>% 
+      rename(
+        daytime_temperature_degree = temperature_degree,
+        daytime_precipitation_mm = precipitation_mm,
+        daytime_snowfall_cm = snowfall_cm,
+        daytime_cum_snow_cm = cum_snow_cm
+      ),
+    by = c("prefecture", "year", "month", "day")
+  ) %>% 
+  left_join(
+    weather_hour_df %>% 
+      filter(hour >= 6, hour <= 9) %>% 
+      group_by(prefecture, year, month, day) %>% 
+      summarise_at(
+          vars(temperature_degree, precipitation_mm, snowfall_cm, cum_snow_cm),
+          mean, na.rm = TRUE
+      ) %>% 
+      rename(
+        morning_temperature_degree = temperature_degree,
+        morning_precipitation_mm = precipitation_mm,
+        morning_snowfall_cm = snowfall_cm,
+        morning_cum_snow_cm = cum_snow_cm
+      ),
+    by = c("prefecture", "year", "month", "day")
+  ) %>% 
+  left_join(
+    weather_hour_df %>% 
+      filter(hour >= 9, hour <= 18) %>% 
+      group_by(prefecture, year, month, day) %>% 
[…]

### 2021-03-29 Codes/R/weather_diff.R

@@ -1,0 +1,157 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer",
+  "kableExtra"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load weather information =================
+weather_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_on_exam_day.csv"))
+
+# Load location information
+loc_df <- read_delim(file.path(dropbox_dir, "Data/weather_station_id.txt"), delim = ",")
+prefecture_order <- loc_df$prefecture
+
+weather_df_avg <- weather_df %>% 
+  mutate(
+    daytime_cum_snow_m = daytime_cum_snow_cm / 100,
+    daytime_snowfall_m = daytime_snowfall_cm / 100,
+    ) %>% 
+  group_by(prefecture, exam_year, exam_month) %>% 
+  summarise_at(
+    vars(daytime_temperature_degree, daytime_cum_snow_m, daytime_snowfall_m, daytime_precipitation_mm), 
+    mean
+    ) %>% 
+  mutate(prefecture = rev(factor(prefecture, levels = prefecture_order)))
+
+# Daytime temperature
+p <- weather_df_avg %>% 
+  ggplot(aes(x = prefecture, y = daytime_temperature_degree, color = factor(exam_year))) +
+  geom_point() +
+  scale_x_discrete(limits = prefecture_order) +
+  scale_color_brewer(
+    palette = "YlOrRd",
+    name = "Year"
+  ) +
+  ylab("Temperature (degree Celsius)") +
+  xlab("Prefecture") +
+  theme_minimal() +
+  theme(
+    axis.line.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    axis.text.x = element_blank(),
+    axis.title = element_text(size = 15),
+    axis.text.y = element_text(size = 10),
+    legend.title = element_blank(),
+    legend.text = element_text(size = 15),
+    legend.position = "bottom"
+  )
+
+ggsave(
+  filename = file.path(git_dir, "Output/images/temperature_diff.pdf"),
+  plot = p,
+  width = 10,
+  height = 7
+)
+
+# Daytime cumulated snow
+p <- weather_df_avg %>% 
[…]

### 2021-03-29 Codes/R/weather_download.R

@@ -1,0 +1,642 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load location information
+loc_df <- read_delim(file.path(dropbox_dir, "Data/weather_station_id.txt"), delim = ",")
+
+# Hourly weather information =============================
+
+exam_date <- c(
+  "2012/1/14", "2012/1/15",
+  "2013/1/19", "2013/1/20",
+  "2014/1/18", "2014/1/19",
+  "2015/1/17", "2015/1/18",
+  "2016/1/16", "2016/1/17",
+  "2017/1/14", "2017/1/15",
+  "2018/1/13", "2018/1/14",
+  "2019/1/19", "2019/1/20",
+  "2020/1/18", "2020/1/19"
+)
+
+weather_df <- c()
+
+for (i in seq(18, nrow(loc_df))) {
+  
+  print(i)
+
+  loc_i <- loc_df %>% slice(i)
+  
+  for (j in seq_along(exam_date)) {
+    exam_date_lubridate <- exam_date[j] %>% as_date()
+    exam_year <- exam_date_lubridate %>% year()
+    exam_month <- exam_date_lubridate %>% month()
+    exam_day <- exam_date_lubridate %>% day()
+    
+    if (i %in% c(11)) {
+      
+      html_data <- read_html(
+        paste0(
+          "https://www.data.jma.go.jp/obd/stats/etrn/view/hourly_a1.php?prec_no=",
+          loc_i$prec_no, "&block_no=", loc_i$block_no,
+          "&year=", as.character(exam_year), 
+          "&month=", as.character(exam_month), 
+          "&day=", as.character(exam_day), 
+          "&view="
+          )
+      )
+      # Sys.sleep(runif(1, max = 10))
+    
+      html_table <- html_data %>% 
+        html_nodes("table") %>% 
+        .[5] %>% 
+        html_table(fill = TRUE) %>% 
+        .[[1]] %>% 
+        set_colnames(
+          c(
+            "hour", "precipitation_mm", "temperature_degree",
+            "wind_speed", "wind_direction",
+            "sunny_time", "snowfall_cm", "cum_snow_cm"
+            )
+          ) %>% 
+        as_tibble() %>% 
[…]

### 2021-03-29 Codes/R/weather_map.R

@@ -1,0 +1,99 @@
+packages <- c(
+  "rgdal",
+  "sp",
+  "raster",
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer",
+  "RColorBrewer",
+  "kableExtra"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load weather information =================
+weather_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_on_exam_day.csv"))
+
+# Draw map of average temperature  ===============
+
+map_Japan <- shapefile(
+  file.path(
+    dropbox_dir,
+    "Data/shapefile",
+    "jpn_admbnda_adm0_2019.shp"
+  )
+)
+map <- shapefile(
+  file.path(
+    dropbox_dir,
+    "Data/shapefile",
+    "jpn_admbnda_adm1_2019.shp"
+  )
+)
+
+weather_df_avg <- weather_df %>% 
+  mutate(daytime_cum_snow_m = daytime_cum_snow_cm / 100) %>% 
+  group_by(prefecture) %>% 
+  summarise_at(vars(daytime_temperature_degree, daytime_cum_snow_m), mean)
+
+map@data$ADM1_JA <- str_replace(map@data$ADM1_JA, "県|府", "")
+map@data$ADM1_JA <- str_replace(map@data$ADM1_JA, "東京都", "東京")
+
+map_avg <- merge(map, weather_df_avg, by.x = "ADM1_JA", by.y = "prefecture")
+
+# Average temperature -------------------
+
+filepath = file.path(git_dir, 'Output/images/temperature_map.png')
+png(file = filepath)
+print(
+  spplot(
+    map_avg, 
+    "daytime_temperature_degree", 
+    sp.layout = list(map_Japan, lwd = 0.1), 
+    col.regions = brewer.pal(n = 7, name = "OrRd"),
+    # cuts = 6,
+    at = seq(-5, 20, 5),
+    par.settings = list(axis.line = list(col = "transparent")),
+    colorkey = list(
+      labels = list(
+        at = seq(-5, 20, 5),
+        labels = as.character(seq(-5, 20, 5)),
+        cex = 1.0
+      )
+    ),
+    col = "transparent"
+  )
+)
+dev.off()
[…]

### 2021-04-03 Writeups/paper.tex
First draft done

@@
 \usepackage{graphicx}
-\usepackage{natbib}
+\usepackage[sort]{natbib}
 \usepackage{setspace} 
@@
 
-\title{Winter weather on exam days and admission for a prestigious university in Japan}%: \\ Empirical analysis on auditing reports in Brazil}
+\title{Winter weather on exam days and matriculation for a prestigious university in Japan}%: \\ Empirical analysis on auditing reports in Brazil}
 %\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison.
 Contact: msuzuki7@wisc.edu.
-The authors would like to thank Laura Schechter for her numerous feedback and support.
-We are also grateful to Joshua Deutschmann, Paul Dower, Jeremy Foltz, Priya Mukherjee, Andrew Stevens, and seminar participants at the UW-Madison Agricultural and Applied Economics department for helpful comments and suggestions.
-Any errors in this draft are the sole responsibility of the authors.}}
-\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu}}
+The author would like to thank Laura Schechter for her numerous feedback and support.
+I am also grateful to Joshua Deutschmann, Paul Dower, Jeremy Foltz, Priya Mukherjee, Andrew Stevens, and seminar participants at the UW-Madison Agricultural and Applied Economics department for helpful comments and suggestions.
+Any errors in this draft are the sole responsibility of the author.}}
+\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison.
+Contact: msuzuki7@wisc.edu.
+The authors would like to thank Laura Schechter for her numerous feedback and support.}}
 \date{\today \\ \vspace{1cm} Preliminary draft \\ Please do not cite or circulate}
@@
   \vspace{1cm}
- \noindent Keywords: Temperature, Education, University admission, Cognitive performance
+ \noindent Keywords: Temperature, Education, University matriculation, Cognitive performance
 \end{abstract}
@@
 
-External factors can impact various outcomes.
-One active area of research is the effect of high temperature on performance at high-stakes exams.
-Given the importance of high education for later outcomes, this is nice.
+Climate change is expected to increase the frequency of extreme weather events.
+This is considered to have not only macro-level impacts but also micro-level impacts such as individual behaviors.
+To understand the effect, emerging literature has studied effects of high temperature on various outcomes both in the long run and in the short run.
+What has been less studied in the literature is the economic impact of \textit{low} temperature.
+Given the possibility that the sea-ice loss, partly due to climate change, results in cold winters with severely low temperatures \citep{Kretschmer2016, Kim2014}, it is important to understand how low temperature can affect our lives.
 
-What is missing in the literature is the effect of \textit{low} temperature on performance at exams.
+This study analyzes the effect of winter weathers on exam outcomes in Japan.
+Most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth), for admission.
+Students take the exam on the same dates in mid-January in their prefectures.
+This creates a variation in weathers to which they are exposed to on the exam dates.
+I use the weather on the dates of Center Test and investigate its effect on the matriculation for the University of Tokyo (UTokyo henceforth).
+The advantage of using the matriculation share for UTokyo as an outcome is that it is the most prestigious university in Japan.
+This allows me to attribute a reduction in matriculation shares to the worse exam performance, instead of the better performance which could induce students to choose better universities.
 
-In this study, I analyze the effect of winter weathers on exam outcomes in Japan.
-I use the weather on the days of National Center Test for University Admission (Center Test hereafter) and investigate its effect on the admission for the most prestigious university in Japan, the University of Tokyo (UTokyo henceforth).
+The econometric analyses show that low temperature and snow cumulated on the ground on exam dates reduce the matriculation share.
+The estimates are not only statistically but also economically significant.
+Changing the temperature on the exam dates from 3-6 $^o$C to $<$ 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
+Moreover, additional analyses suggest that the temperature in the morning on exam dates rather than temperature during exams impact exam performance. 
+The results provide implications for effective measures to be taken to mitigate the negative impact of winter weathers.
+These include preparing waiting rooms for exam takers to warm up for equalizing their pre-exam conditions or adjusting the importance of the scores at Center Test in the admission process.
 
-If I use a middle-ranked university, reduction in admission share can be attributed to both lower and higher scores:
-while students with lower scores can fail to get into the university, students with higher scores can choose to apply to and get admitted to higher-ranked universities.
-Since UTokyo is the most prestigious university in Japan (** cite some university ranking **), it is unlikely that students who get high scores in Center Test go to better universities.\footnote{
-  Medical departments in several universities are higher-ranked than UTokyo based on standard score.
-  However, the career paths for those in the non-medical department of UTokyo and medical departments in universities are substantially different:
-  while most students graduating from medical departments become medical doctors, the majority of students from UTokyo become bureaucrats, work for private firms, or go to graduate schools.
-  Hence, it is unlikely that high scores at Center Test induce students who would otherwise get into UTokyo to go to a medical department.
-}
-Therefore, if I observe a reduction in admission share, I consider this as an evidence that the performance in Center Test is negatively affected.
+This study mainly contributes to the recent but growing literature of the effects of climate factors on the outcome of high-stakes exams.
+Several previous studies have found the adverse effect of high temperature on learning, which reduces the performance at exams \citep{Park2020b, Cho2017}.
+More closely to my study, \citet{GraffZivin2020} and \citet{Park2020a} show that heat on exam days decreases the exam scores at high-stakes exams in China and the U.S., respectively.
+Considering the importance of the effects the exam results can have on later life outcomes, it is important to understand how the external factors such as temperature affect exam performance and what we can do to ameliorate such effects.
+To complement the literature, I investigate the effect of \textit{low} temperature on exam performance.
 
-\section{Background}
+This study also has a contribution to the literature on the economic impact of low temperature.
+It has been shown with controlled experiments that cold stresses negatively affect such things as cognitive ability and memory, as reviewed in \citet{Taylor2016}.
+However, evidence based on data in the field is scarce.
+Country-level studies have shown a non-linear effect of temperature on economic growth, in that both low and high temperature has a negative impact \citep{Burke2015}.
+One study based on microdata is provided by \citet{Stevens2017}, who finds a negative impact of low temperature on labor productivity of blueberry pickers in California.
+I use prefecture-level information to investigate how low temperature affects cognitive performance of exam takers.
 
-For admission for most (especially almost all public) universities, students are required to take two exams.
-The first stage is Center Test.
-Students take an exam on consecutive two days (Saturday and Sunday on mid January).
-While different students can choose which subjects to take, most universities require students to take exams on math, English, language, natural science, and social science.
+This study proceeds as follows.
+In Section \ref{sec:background}, the context of this study is introduced.
+Section \ref{sec:data} describes the data. 
+Our empirical strategy is introduced in Section \ref{sec:empirical_strategy}.
+In Section \ref{sec:results}, I present the empirical results, and Section \ref{sec:conclusion} concludes.
+
+\section{Background}\label{sec:background}
+
+In Japan, for admission for most (almost all public) universities, students are required to take two exams.
+The first-stage test is called Center Test.
+Students take an exam on consecutive two days (Saturday and Sunday) on mid-January.
+While different students can choose which subjects to take, most public universities require students to take exams on social science, language, and English on the first day and math and natural science on the second day.
+The exams start at 9:30 AM on both days and end at 6:10 PM on the first day and 5:50 PM on the second day.
 Questions are multiple-choice and common for all exam takers across Japan.
-Exam takers do not receive their exact scores until the next May at earliest.
-However, since they can record their answers to the exam booklets and can bring them back home, they know their scores by comparing their own answers and correct answers, which are made public through newspaper or websites of cramming schools.
 High-school seniors take the test at designated cites in the area where their high schools are located.
@@
 
+Exam takers do not receive their scores until the next May at earliest.
+However, they can record their answers on their exam booklets and can bring them back home.
+Hence, they know their scores by comparing their own answers and correct answers, which are made public through newspapers or websites of cramming schools.
 After taking Center Test, students apply for public and private universities.\footnote{
@@
 Applicants for public universities typically take the second-stage exam.
-This exam is made by each university, and students go to the universities and take the exam.
-In other words, every applicant for a university takes the exam at the same location.
+This exam is made by each university, and students physically go to the universities and take the exam.
+Therefore, every applicant for a university takes the second-stage exam at the same location on the same days.
 
-For public universities, there are three exam periods: the first one is typically at the end of February, the second one is on the first week of March, and the third one is typically around March 10th.
+Most public universities, including UTokyo, have three periods for the second-stage exam:
+usually, the first one is at the end of February, the second one is on the first week of March, and the third one is on the second week of March.
+Students can apply for only one university at each exam period.
 While different universities accept applications for different periods, most universities have only one (typically the first period) or two (typically the first and the third periods) periods.
-UTokyo has two exam periods, the first and the third ones, although most of the admissions are provided for exam takers during the first exam period.
+Up to 2015, UTokyo had two exam periods, the first and the third ones, although most of the admissions were provided for exam takers at the first exam period.\footnote{
+  In 2015, while 3,008 students got admitted though the first-period exam, only 100 students got admitted through the third-period exam.
+  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01_h27.html
+}
+In 2016, UTokyo abolished the third-period exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test.
+In the latter process, students take interviews on November before Center Test, and after taking Center Test, final admissions are determined based on the results both of interviews and scores at Center Test.\footnote{
+  In 2020, among 3,083 admitted students, only 73 students got admitted through this process.
+  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01.html
+}
 
-For UTokyo, scores at Center Test are used for two purposes.
+In admission for UTokyo, scores at Center Test are used for two purposes for the first-period exam takers.
 First, the scores are used for eligibility to take the second-stage exam.
@@
 Since the thresholds are announced after the application, exam takers do not know if their scores are above or below the thresholds.
+Secondly, the scores at Center Test are taken into consideration for admission.
+The final score of a students is calculated by the weighted sum of exam scores at the first- and the second-stage exams.\footnote{
+  In 2020, for the first-period exam takers, the weights for Center Test and the second-stage exam are 20\% and 80\%.
+  Also, until 2015, for the third-period exam takers, scores at Center Test were used only for eligibility and were not accounted for the final admission.
+}
 
-Secondly, the scores at Center Test are taken into consideration for admission.
-The final score of a students is calculated by the weighted average of exam scores at the first- and second-stage exams.
+In summary, results at Center Test are crucial for applicants for UTokyo.
+This study will investigate how external factors such as temperature and weather on the dates of Center Test affect matriculation for UTokyo.
 
-\section{Data}
+\section{Data}\label{sec:data}
 
-I use two sets of data: weather and admission information for UTokyo.
-For weather information, I get data from Japan Meteorological Agency.
+I use two sets of data: weather and matriculation information for UTokyo.
+For weather information, I get data from \Citeauthor{jma}.
 Their website maintains the past weather across Japan.
 In this study, based on hourly weather on exam days at prefecture capitals, I use average weathers between 6AM to 6PM.
-Prefecture capitals tend to be most populated in each prefecture, and in many prefectures highly-ranked high schools from which many students go to UTokyo are located at prefecture capitals.
+Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
 %\footnote{
@@
 
-For admission information for UTokyo, I use University Basic Information maintained by National Institution for Academic Degrees and Quality Enhancement of Higher Education.
-This data contains information from 2012 to 2020 on the number of admitted students by prefectures at which their high schools are located.
-I create the admission share of each prefecture, which is the ratio of the number of admitted students from a prefecture to the number of all admitted students.
+For matriculation information for UTokyo, I use University Basic Information maintained by \Citeauthor{univ_info}.
+This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
+I create the matriculation share of each prefecture, which is the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
+  Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and decision to go to the university or not.
+  Due to the lack of the number of admitted students by prefecture, I use the information on matriculation.
+  For UTokyo, the number of admissions and the number of matriculations are very close:
+  In 2020, among 3,083 admitted students, 3,064 students matriculate at UTokyo.
+  Moreover, it is unlikely that weathers on exam days affect decisions of admitted students to matriculate or not.
+}
 
 The summary statistics are provided in Table \ref{tab:sum_stat}.
-While the mean of the admission share (\%) is $2.08$,\footnote{
-  Since there are admissions from abroad, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
+While the mean of the matriculation share (\%) is $2.08$,\footnote{
+  Since there are matriculations from abroad, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
+  I do not consider matriculations from abroad in the analyses since their admission is mostly based on interviews and essays.
 } the distribution is starkly skewed.
 As shown in Figure \ref{fig:admission_map}, many prefecture have less 1\% shares.
-Also, the admission shares of the top 5 prefectures total more than 60\%.
-This results in a small median admission share, $0.79$.
+Also, the matriculation shares of the top 5 prefectures total more than 60\%.
+This results in a small median matriculation share, $0.79 \%$.
 
-\begin{table}[H]
-  \centering
-  \caption{Summary Statistics}
-  \resizebox{\linewidth}{!}{
-  \input{"../Output/tex/sum_stat.tex"}
+%\begin{table}[H]
+%  \centering
+%  \caption{Summary Statistics}
+%  \resizebox{0.8\linewidth}{!}{
+%  \input{"../Output/tex/sum_stat.tex"}
+%  }
+%  \label{tab:sum_stat}
+%  \footnotesize
+%  \begin{tablenotes}
+%    \item 
+%      Notes:
+%      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
+%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+%      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
+%  \end{tablenotes}
+%\end{table}
+
+%\begin{figure}[H]
+%  \centering
+%  \caption{Map of matriculation shares (\%) (average across years)}
+%  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}
+%  \label{fig:admission_map}
+%  \footnotesize
+%  \begin{tablenotes}
+%    \item Notes:
+%      This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
+%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+%      Average of the shares across years is shown in the map.
+%      Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
+%  \end{tablenotes}
+%\end{figure}
+
+\section{Empirical Strategy}\label{sec:empirical_strategy}
+
+The objective of the analysis is to analyze the effect of temperature and other weather variables on exam days on the matriculation share for UTokyo.
+The reason why I use the matriculation share for UTokyo is as follows:
+consider an matriculation share for a middle-ranked university.
+Suppose also that low temperature has a negative impact on exam scores.
+Then, 
+(i) students from the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
+(ii) students from the prefecture who would get into a higher-ranked university may get into the middle-ranked university.
+Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
+However, the second effect is unlikely to be large for UTokyo for the following reasons.
+First, UTokyo is known to be the best university in Japan.
+Secondly, since UTokyo is a national university, the tuition is cheaper than most private universities.\footnote{
+  According to \citet{mext}, in 2018, the annual tuition for national universities was 538,633 JPY ($\approx$ 4,900 USD), while the average annual tuition for private university was 904,146 ($\approx$ 8,200 USD).
+  %https://www.mext.go.jp/a_menu/koutou/shinkou/07021403/1412031_00001.htm
 }
-  \label{tab:sum_stat}
-  \footnotesize
-  \begin{tablenotes}
-    \item 
-      Notes:
-      Admission share (\%) is the share of newly admitted students to the University of Tokyo from each prefecture.
-      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
-      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
-  \end{tablenotes}
-\end{table}
+Therefore, I can rule out the second possibility and attribute a reduction in matriculation shares to the worse exam performance.
 
-\begin{figure}[H]
-  \centering
-  \caption{Map of admission shares (\%) (average across years)}
-  \includegraphics[width = 0.9\textwidth]{../Output/images/admission_map.png}
-  \label{fig:admission_map}
-  \footnotesize
-  \begin{tablenotes}
-    \item Notes:
-      This map shows the admission shares (\%) for the University of Tokyo from each prefecture.
-      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
-      Average of the shares across years is shown in the map.
-      Although not shown in the legend due to the lack of the space, the lightest color in the map means the admission share between 0 to 0.5\% 
-  \end{tablenotes}
-\end{figure}
-
-\section{Empirical Strategy}
-
-The objective of the analysis is to analyze the effect of temperature and other weather variables on exam days on the admission share for UTokyo.
-The outcome variable, $Y_{jt}$ is the admission share (\%) for UTokyo of a prefecture $j$ in year $t$.
+In the analyses, the outcome variable, $Y_{jt}$ is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
 Let $T_{jt}$ be average temperature on exam days in $j$ in year $t$.
@@
 I exploit the variation of temperature on exam days, which I consider exogenous after controlling for prefecture-specific time-variant factors and time-varying aggregate shocks through prefecture and year fixed effects.
-As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variation in temperature on exam days.\footnote{
+As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam days.\footnote{
   Similar figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
@@
 
-One potential problem in the analysis is that a students from a high school in a prefecture does not necessarily take Center Test in the same municipality.
+One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take Center Test in the same municipality.
 This means that, for these students, the weather at the exam cites are measured with errors.
@@
 Hence, this classical measurement error can make the estimates conservative.
+
+%\begin{figure}[H]
+%  \centering
+%  \caption{Average temperature on two exam days in each prefecture each year}
+%  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
+%  \label{fig:temperature_diff}
+%  \footnotesize
+%  \begin{tablenotes}
+%    \item Notes:
+%      Temperature at prefecture capitals between 6AM and 6PM on days of Center Test is used.
+%      Average across two test days in each year is shown in the figure.
+%      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
+%  \end{tablenotes}
+%\end{figure}
+
+\section{Results}\label{sec:results}
+
+\subsection{Main Results}
+
+The main empirical results are provided in Table \ref{tab:main_reg}.
+The standard errors are clustered at the prefecture level.
+The column (1) shows the result with a linear specification.
+While the point estimate is positive, which means matriculation shares are higher if an exam is held on warmer days, it is statistically insignificant. 
+The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impacts of cold weather. 
+Since the mean matriculation share is $2.08$\%, the coefficient on the lowest temperature bins means that reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest bin, the matriculation share decreases by 9\%.
+Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$.
+Therefore, the same temperature change decreases the matriculation share by 22\% of the median value.
+Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in the column (1) could not capture the non-linear effect of temperature and why the coefficient is statistically insignificant.
+Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.
+
+In column (3) and (4), I add other weather variables.
+While temperature coefficients are barely affected, I find that rainfall and snowfall during exam time do not impact the matriculation shares.
+On the other hand, the cumulated snow on the ground has a negative impact.
+To capture the effect of existence of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
+This specification gives a result that, when there is snow on the ground cumulated more than 10cm ($\approx$ 3 feet) decreases the matriculation share by 0.13 percentage point.
+
+In summary, I find a both statistically and economically significant impacts of weather on exam days.
+In particular, the estimation results show that low temperature and snow cumulated on the ground have negative impact on the matriculation shares for UTokyo.
+In the next two subsections, I investigate the mechanisms underlying the findings.
+
+%\begin{table}[H]
+%  \center
+%  \caption{Regression: Matriculation share (\%) and weather on exam days}
+%  \input{"../Output/tex/main_reg.tex"}
+%  \label{tab:main_reg}
+%  \small
+%  \begin{tablenotes}
+%    \item
+%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+%      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
+%      Standard errors are clustered at the prefecture level.
+%  \end{tablenotes}
+%\end{table}
+
+\subsection{Weather in the morning vs. during exam}
+
+Here I investigate if the findings above are due to weathers in the morning or during the exams.
+This distinction can be important since different measures should be taken to mitigate the effect of each weather.
+The results are shown in Table \ref{tab:reg_morning_exam}.
+Columns (1) and (2) show statistically significant impact of low temperature in the morning.
+On the other hand, statistically insignificant estimates are obtained in columns (3) and (4) with weathers during the exams, although the magnitudes are large.
+Also, including both weathers simultaneously, column (5) shows the negative and significant impact of cold weather in the morning on the matriculation share.\footnote{
+  Estimates for cumulated snow are insignificant in column (5) due to multicollinearity, which blows up their standard errors.
+  Their correlation coefficient is 0.99.
+  This is reasonable since their differences can be caused by new snowfall or snow melting, which cannot happen drastically within hours.
+}
+This suggests that the morning weathers on the exam dates matter for exam performance.
+
+\subsection{Preparation vs. Cognitive performance on exam days}
+
+One possible interpretation is that the temperature on exam days capture the weathers before the exam, which can affect preparation for the exam. 
+For instance, cold weather can make it hard for students to focus on studying, or snowfalls can prevent students from going to schools or cramming schools for studying.
+To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
+The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for all the variables.
+Therefore, I consider that the findings in Table \ref{tab:main_reg} are due to the effect of weather variables on the exam days.
+
+%\begin{table}[H]
+%  \center
+%  \caption{Regression: Matriculation share (\%) and weather in the morning vs. during exam}
+%  \scriptsize
+%  \input{"../Output/tex/reg_morning_exam.tex"}
+%  \label{tab:reg_morning_exam}
+%  \scriptsize
+%  \begin{tablenotes}
+%    \item
+%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+%      For variables in the morning, I use average weather variables at prefecture capitals between 6AM to 9AM on exam days.
+%      For variables during the exam, I use average weather variables at prefecture capitals between 9AM to 6PM on exam days.
+%      Standard errors are clustered at the prefecture level.
+%  \end{tablenotes}
+%\end{table}
+
+\section{Conclusion}\label{sec:conclusion}
+
+In this paper I study the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
+Instead of exam scores, I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
+To identify the causal impact, I exploit the variation in weathers at each prefecture on exam days.
+Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
+This study fills the gap and identifies the causal impact of winter weather on the matriculation.
+
+The results show that both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam days.
+Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
+Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
+Using the weathers in the morning and during the exams, I find a suggestive evidence that the temperature effect is mainly caused by low temperature in the morning.
+This result suggest that adverse conditions for exam takers on the way to test cites affect their cognitive performance.
+
+Several implications can be derived from the findings.
+First, the result that low temperature in the morning rather than during the exam matters suggest that equipments to improve the condition at the exam sites may have limited impacts.
+Rather, investment on recovering students can result in better improvement.
+For instance, providing socks and slippers for students whose shoes and socks get wet due to walking through stacked snow.
+Also, it may be effective to provide sufficient time before the exam at the exam site so that students can recover in a warm room.
+%This study provides guidance on how to set the leveling field for exam takers across Japan.
+
+Secondly, my results have implications on the matriculation process of universities.
+Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measure to select students.
+Examples include extracurricular activities and statement of purposes, which are actively utilized in other countries such as the U.S..
+On the other hand, it may be effective to change the weights for Center Test and the second-stage exam.
+Since the second-stage exam is held at each university, all exam takers are exposed to similar environments.
+This rules out the possibility that exam takers at different places are affected differently by their conditions.
+Given the importance of exam results for later life outcomes, it is desirable that universities take measures to mitigate the effect of nuisance factors on matriculation.
+
+\clearpage
+\bibliographystyle{apalike}
+\bibliography{todai}
+
+\section{Figures}
+
+\begin{figure}[H]
+  \centering
+  \caption{Map of matriculation shares (\%) (average across years)}
+  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}
+  \label{fig:admission_map}
+  \footnotesize
+  \begin{tablenotes}
+    \item Notes:
+      This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      Average of the shares across years is shown in the map.
+      Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
+  \end{tablenotes}
+\end{figure}
 
@@
 
-\section{Results}
+\section{Tables}
 
-\subsection{Main Results}
-
-The main empirical results are provided in Table \ref{tab:main_reg}.
-The column (1) shows the result with a linear specification.
-While the point estimate is positive, which means admission shares are higher if an exam is held on warmer days, it is statistically insignificant. 
-The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impacts of cold weather. 
-Since the mean admission share is $2.08$\%, the coefficient on the lowest temperature bins means that reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest bin, the admission share decreases by 9\%.
-Moreover, due to the stark skewness in the distribution of admission shares, the median admission share is $0.79$.
-Therefore, the same temperature change decreases the admission share by 22\% of the median value.
-Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in the column (1) could not capture the non-linear effect of temperature and why the coefficient is statistically insignificant.
-Although for a quite different temperature range, similar plateau effects are found in Park (2020) and Melo and Suzuki (2021).
-
-In column (3) and (4), I add other weather variables.
-While temperature coefficients are barely affected, I find that rainfall and snowfall during exam time do not impact the admission shares.
-On the other hand, the cumulated snow on the ground has a negative impact.
-To capture the effect of existence of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
-This specification gives a result that, when there is snow on the ground cumulated more than 10cm ($\approx$ 3 feet) decreases the admission share by 0.13 percentage point.
-
-In summary, I find a both statistically and economically significant impacts of weather on exam days.
-In particular, the estimation results show that low temperature and snow cumulated on the ground have negative impact on the admission shares for UTokyo.
-In the next two subsections, I investigate the mechanisms underlying the findings.
+\begin{table}[H]
+  \centering
+  \caption{Summary Statistics}
+  \resizebox{0.8\linewidth}{!}{
+  \input{"../Output/tex/sum_stat.tex"}
+  }
+  \label{tab:sum_stat}
+  \footnotesize
+  \begin{tablenotes}
+    \item 
+      Notes:
+      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
+  \end{tablenotes}
+\end{table}
 
@@
   \center
-  \caption{Regression: Admission share (\%) and weather on exam days}
+  \caption{Regression: Matriculation share (\%) and weather on exam days}
   \input{"../Output/tex/main_reg.tex"}
@@
     \item
-      The outcome variable is the admission shares (\%) for the University of Tokyo from each prefecture.
-      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
       I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
@@
 
-\subsection{Weather in the morning vs. during exam}
-
 \begin{table}[H]
   \center
-  \caption{Regression: Admission share (\%) and weather in the morning vs. during exam}
+  \caption{Regression: Matriculation share (\%) and weather in the morning vs. during exam}
   \scriptsize
@@
     \item
-      The outcome variable is the admission shares (\%) for the University of Tokyo from each prefecture.
-      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
       For variables in the morning, I use average weather variables at prefecture capitals between 6AM to 9AM on exam days.
@@
 \end{table}
-
-\subsection{Preparation vs. Cognitive performance on exam days}
-
-One possible interpretation is that the temperature on exam days capture the weathers before the exam, which can affect preparation for the exam. 
-For instance, cold weather can make it hard for students to focus on studying, or snowfalls can prevent students from going to schools or cramming schools for studying.
-To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
-The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for all the variables. 
-Therefore, I consider that the findings in Table \ref{tab:main_reg} are due to the effect of weather variables on the exam days.
-
-\section{Conclusion}
-
-In this paper I study the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
-Instead of exam scores, I use the admission share for the most prestigious university in Japan, the University of Tokyo.
-To identify the causal impact, I exploiting the variation in weathers at each prefecture on exam days.
-Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains unknown.
-This study fills the gap and identifies the causal impact of winter weather on the admission.
-
-The results show that both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam days.
-Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the admission share of a prefecture by 0.18 percentage point, which is 9\% of the mean admission share, or 22\% of the median admissions share.
-Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
-Using the weathers in the morning and during the exams, I find a suggestive evidence that the temperature effect is mainly caused by low temperature in the morning.
-This result suggest that adverse conditions for exam takers on the way to test cites affect their cognitive performance.
-
-Several implications can be derived from the findings.
-First, the result that low temperature in the morning rather than during the exam matters suggest that equipments to improve the condition at the exam sites may have limited impacts.
-Rather, investment on recovering students can result in better improvement.
-For instance, providing socks and slippers for students whose shoes and socks get wet due to walking through stacked snow.
-Also, it may be effective to provide sufficient time before the exam at the exam site so that students can recover in a warm room.
-%This study provides guidance on how to set the leveling field for exam takers across Japan.
-
-Secondly, my results have implications on the admission process of universities.
-Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measure to pick students.
-Examples include extracurricular activities and statement of purposes, which are actively utilized in other countries such as the U.S..
-On the other hand, it may be effective to change the weights for Center Test and the second-stage exam.
-Since the second-stage exam is held at each university, exam takers are exposed to similar environments.
-This rules out the possibility that exam takers at different places are affected differently by their conditions.
-Given the importance of college choice, it is desirable that universities take measures to mitigate the effect of nuisance factors on admission.
 
@@
   \includegraphics[width = 0.9\textwidth]{../Output/images/snowfall_diff.pdf}
-  \label{fig:cum_snow_diff}
+  \label{fig:snowfall_diff}
   \footnotesize
@@
   \center
-  \caption{Regression: Admission share (\%) and average weather for 10 days before exam}
+  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
   \input{"../Output/tex/reg_pre10.tex"}
@@
     \item
-      The outcome variable is the admission shares (\%) for the University of Tokyo from each prefecture.
-      The admission share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of admission.
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
       I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.

### 2021-04-03 Codes/R/regression.R

@@ -87,7 +87,7 @@ res_5 <- felm(
 
 list(res_1, res_2, res_3, res_4, res_5) %>% 
   stargazer(
-    dep.var.labels = "Admission share (\\%)",
+    dep.var.labels = "Matriculation share (\\%)",
     covariate.labels = c(
       "Temperature (degree C)",
       "Temperature $\\le$ 0",
@@ -148,7 +148,7 @@ res_5 <- felm(
 
 list(res_1, res_2, res_3, res_4, res_5) %>% 
   stargazer(
-    dep.var.labels = "Admission share (\\%)",
+    dep.var.labels = "Matriculation share (\\%)",
     column.labels = c(rep("Morning", 2), rep("During-exam", 2)),
     order = c(seq(1, 4), seq(8, 11), seq(5, 7), seq(12, 14)),
     covariate.labels = c(
@@ -207,7 +207,7 @@ res_4 <- felm(
 
 list(res_1, res_2, res_3, res_4) %>% 
   stargazer(
-    dep.var.labels = "Admission share (\\%)",
+    dep.var.labels = "Matriculation share (\\%)",
     covariate.labels = c(
       "Temperature (degree C)",
       "Temperature $\\le$ 0",
@@ -353,5 +353,5 @@ reg_df %>%
   table()
 
 reg_df %>% 
-  select(exam_temperature_degree, morning_temperature_degree) %>% 
-  summary()
+  dplyr::select(morning_cum_snow_m, exam_cum_snow_m) %>% 
+  cor()

### 2021-04-03 Codes/R/sumstat.R

@@ -66,7 +66,7 @@ map(
   as.matrix() %>% 
   set_colnames(NULL) %>% 
   set_rownames(c(
-    "Admission share (%)",
+    "Matriculation share (%)",
     "Temperature (degree C)",
     "Hourly precipitation (mm)",
     "Hourly snowfall (m)",

### 2021-04-03 Writeups/paper.tex
Revision done

@@
 Students take the exam on the same dates in mid-January in their prefectures.
-This creates a variation in weathers to which they are exposed to on the exam dates.
+This creates a variation in weathers to which they are exposed on the exam dates.
 I use the weather on the dates of Center Test and investigate its effect on the matriculation for the University of Tokyo (UTokyo henceforth).
@@
 
-In Japan, for admission for most (almost all public) universities, students are required to take two exams.
+In Japan, for admission to most (almost all public) universities, students are required to take two exams.
 The first-stage test is called Center Test.
-Students take an exam on consecutive two days (Saturday and Sunday) on mid-January.
-While different students can choose which subjects to take, most public universities require students to take exams on social science, language, and English on the first day and math and natural science on the second day.
+Students take an exam on consecutive two days (Saturday and Sunday) in mid-January.
+%While different students can choose which subjects to take, most public universities require students to take exams on social science, language, and English on the first day and math and natural science on the second day.
 The exams start at 9:30 AM on both days and end at 6:10 PM on the first day and 5:50 PM on the second day.
 Questions are multiple-choice and common for all exam takers across Japan.
-High-school seniors take the test at designated cites in the area where their high schools are located.
-On the other hand, high-school graduates are assigned to test cites in the area where the homes used in their application forms are located.
+High-school seniors take the test at designated sites in the area where their high schools are located.
+On the other hand, high-school graduates are assigned to test sites in the area where the homes used in their applications are located.
 
-Exam takers do not receive their scores until the next May at earliest.
-However, they can record their answers on their exam booklets and can bring them back home.
-Hence, they know their scores by comparing their own answers and correct answers, which are made public through newspapers or websites of cramming schools.
-After taking Center Test, students apply for public and private universities.\footnote{
-  There are private universities who accept applications before Center Test.
-}
-Applicants for public universities typically take the second-stage exam.
+On exam dates, heave snows can affect public transportation.
+If this makes it difficult for exam takers to come to exam sites on time, the exam can start a few hours later than scheduled to accommodate them.
+It is also possible that affected students take make-up exams a week later.
+
+%Exam takers do not receive their scores until the next May at earliest.
+%However, they can record their answers on their exam booklets and can bring them back home.
+%Hence, they know their scores by comparing their own answers and correct answers, which are made public through newspapers or websites of cramming schools.
+%After taking Center Test, students apply for public and private universities.\footnote{
+%  There are private universities who accept applications before Center Test.
+%}
+%Applicants for public universities typically take the second-stage exam.
+
+After Center Test, applicants for public universities typically take the second-stage exam.
 This exam is made by each university, and students physically go to the universities and take the exam.
 Therefore, every applicant for a university takes the second-stage exam at the same location on the same days.
-
-Most public universities, including UTokyo, have three periods for the second-stage exam:
-usually, the first one is at the end of February, the second one is on the first week of March, and the third one is on the second week of March.
-Students can apply for only one university at each exam period.
-While different universities accept applications for different periods, most universities have only one (typically the first period) or two (typically the first and the third periods) periods.
-Up to 2015, UTokyo had two exam periods, the first and the third ones, although most of the admissions were provided for exam takers at the first exam period.\footnote{
-  In 2015, while 3,008 students got admitted though the first-period exam, only 100 students got admitted through the third-period exam.
-  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01_h27.html
-}
-In 2016, UTokyo abolished the third-period exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test.
-In the latter process, students take interviews on November before Center Test, and after taking Center Test, final admissions are determined based on the results both of interviews and scores at Center Test.\footnote{
-  In 2020, among 3,083 admitted students, only 73 students got admitted through this process.
-  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01.html
+UTokyo has the second-stage exam at the end of February for two days.\footnote{
+  Up to 2015, UTokyo had another second-stage exam in March and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
+%  Most of the admissions were provided for exam takers on February:
+%  In 2015, among 3,108 admitted students, only 100 exam takers in March got admitted.
+  In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test (around 2\% of all admitted students).
+  Since the majority of students are admitted through the second-stage exam on February, I focus on the admission process for those students. 
 }
 
-In admission for UTokyo, scores at Center Test are used for two purposes for the first-period exam takers.
+%Most public universities, including UTokyo, have three periods for the second-stage exam:
+%usually, the first one is at the end of February, the second one is on the first week of March, and the third one is on the second week of March.
+%Students can apply for only one university at each exam period.
+%While different universities accept applications for different periods, most universities have only one (typically the first period) or two (typically the first and the third periods) periods.
+%Up to 2015, UTokyo had two exam periods, the first and the third ones, although most of the admissions were provided for exam takers at the first exam period.\footnote{
+%  In 2015, while 3,008 students got admitted through the first-period exam, only 100 students got admitted through the third-period exam.
+%  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01_h27.html
+%}
+%In 2016, UTokyo abolished the third-period exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test.
+%In the latter process, students take interviews in November before Center Test, and after taking Center Test, final admissions are determined based on the results both of interviews and scores at Center Test.\footnote{
+%  In 2020, among 3,083 admitted students, only 73 students got admitted through this process.
+%  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01.html
+%}
+
+In admission for UTokyo, scores at Center Test are used for two purposes.
 First, the scores are used for eligibility to take the second-stage exam.
@@
 Secondly, the scores at Center Test are taken into consideration for admission.
-The final score of a students is calculated by the weighted sum of exam scores at the first- and the second-stage exams.\footnote{
+The final score of a student is calculated by the weighted sum of exam scores at the first- and second-stage exams.\footnote{
   In 2020, for the first-period exam takers, the weights for Center Test and the second-stage exam are 20\% and 80\%.
-  Also, until 2015, for the third-period exam takers, scores at Center Test were used only for eligibility and were not accounted for the final admission.
+  %Also, until 2015, for the third-period exam takers, scores at Center Test were used only for eligibility and were not accounted for the final admission.
 }
@@
 Their website maintains the past weather across Japan.
-In this study, based on hourly weather on exam days at prefecture capitals, I use average weathers between 6AM to 6PM.
+In this study, based on hourly weather on exam days at prefecture capitals, I use average weathers between 6 AM to 6 PM.
 Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
@@
 I create the matriculation share of each prefecture, which is the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
-  Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and decision to go to the university or not.
-  Due to the lack of the number of admitted students by prefecture, I use the information on matriculation.
+  Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and the decision to go to the university or not.
+  Due to the lack of the information on the number of admitted students by prefecture, I use the information on matriculation.
   For UTokyo, the number of admissions and the number of matriculations are very close:
@@
 } the distribution is starkly skewed.
-As shown in Figure \ref{fig:admission_map}, many prefecture have less 1\% shares.
+As shown in Figure \ref{fig:admission_map}, many prefectures have less than 1\% shares.
 Also, the matriculation shares of the top 5 prefectures total more than 60\%.
@@
 %      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
+%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
 %  \end{tablenotes}
@@
 The reason why I use the matriculation share for UTokyo is as follows:
-consider an matriculation share for a middle-ranked university.
+consider a matriculation share for a middle-ranked university.
 Suppose also that low temperature has a negative impact on exam scores.
@@
 However, the second effect is unlikely to be large for UTokyo for the following reasons.
-First, UTokyo is known to be the best university in Japan.
+First, UTokyo is known to be the best university in Japan.\footnote{
+  According to \citet{usnews}, UTokyo is the highest-ranked university in Japan (73rd ranked in the world ranking).
+  The second highest-ranked university in Japan is Kyoto University, which is 125th ranked in the world ranking.
+}
 Secondly, since UTokyo is a national university, the tuition is cheaper than most private universities.\footnote{
@@
 In the analyses, the outcome variable, $Y_{jt}$ is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
-Let $T_{jt}$ be average temperature on exam days in $j$ in year $t$.
+Let $T_{jt}$ be the average temperature on exam days in $j$ in year $t$.
 I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
@@
 \end{equation*}
-I exploit the variation of temperature on exam days, which I consider exogenous after controlling for prefecture-specific time-variant factors and time-varying aggregate shocks through prefecture and year fixed effects.
+I exploit the variation of temperature on exam days, which I consider exogenous after controlling for prefecture-specific time-invariant factors and time-varying aggregate shocks through prefecture and year fixed effects.
 As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam days.\footnote{
-  Similar figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
+  Figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
 }
@@
 One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take Center Test in the same municipality.
-This means that, for these students, the weather at the exam cites are measured with errors.
-The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get in any university for the first year and retake Center Test next year in his home prefecture.
+This means that, for these students, the weather at the exam sites is measured with errors.
+The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get into any university for the first year and retake Center Test next year in his home prefecture.
 I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
@@
 %    \item Notes:
-%      Temperature at prefecture capitals between 6AM and 6PM on days of Center Test is used.
+%      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
 %      Average across two test days in each year is shown in the figure.
@@
 While the point estimate is positive, which means matriculation shares are higher if an exam is held on warmer days, it is statistically insignificant. 
-The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impacts of cold weather. 
-Since the mean matriculation share is $2.08$\%, the coefficient on the lowest temperature bins means that reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest bin, the matriculation share decreases by 9\%.
+The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impact of cold weather. 
+Since the mean matriculation share is $2.08$\%, the coefficient on the lowest temperature bins means that, by reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest bin, the matriculation share decreases by 9\%.
 Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$.
@@
 On the other hand, the cumulated snow on the ground has a negative impact.
-To capture the effect of existence of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
-This specification gives a result that, when there is snow on the ground cumulated more than 10cm ($\approx$ 3 feet) decreases the matriculation share by 0.13 percentage point.
+To capture the effect of the existence of a certain amount of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
+This specification gives a result that, snow on the ground cumulated more than 10cm ($\approx$ 3 feet) decreases the matriculation share by 0.13 percentage point.
 
 In summary, I find a both statistically and economically significant impacts of weather on exam days.
-In particular, the estimation results show that low temperature and snow cumulated on the ground have negative impact on the matriculation shares for UTokyo.
+In particular, the estimation results show that low temperature and snow cumulated on the ground have negative impacts on the matriculation shares for UTokyo.
 In the next two subsections, I investigate the mechanisms underlying the findings.
@@
 %      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
+%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
 %      Standard errors are clustered at the prefecture level.
@@
 
-One possible interpretation is that the temperature on exam days capture the weathers before the exam, which can affect preparation for the exam. 
+One possible interpretation is that the temperature on exam days captures the weather before the exam, which can affect preparation for the exam. 
 For instance, cold weather can make it hard for students to focus on studying, or snowfalls can prevent students from going to schools or cramming schools for studying.
@@
 %      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      For variables in the morning, I use average weather variables at prefecture capitals between 6AM to 9AM on exam days.
-%      For variables during the exam, I use average weather variables at prefecture capitals between 9AM to 6PM on exam days.
+%      For variables in the morning, I use average weather variables at prefecture capitals between 6 AM to 9 AM on exam days.
+%      For variables during the exam, I use average weather variables at prefecture capitals between 9 AM to  on exam days.
 %      Standard errors are clustered at the prefecture level.
@@
 
-In this paper I study the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
+This paper studies the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
 Instead of exam scores, I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
@@
 Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
-Using the weathers in the morning and during the exams, I find a suggestive evidence that the temperature effect is mainly caused by low temperature in the morning.
-This result suggest that adverse conditions for exam takers on the way to test cites affect their cognitive performance.
+Using the weathers in the morning and during the exams, I find suggestive evidence that the temperature effect is mainly caused by low temperature in the morning.
+This result suggests that adverse conditions for exam takers on the way to test sites affect their cognitive performance.
 
@@
 First, the result that low temperature in the morning rather than during the exam matters suggest that equipments to improve the condition at the exam sites may have limited impacts.
-Rather, investment on recovering students can result in better improvement.
-For instance, providing socks and slippers for students whose shoes and socks get wet due to walking through stacked snow.
-Also, it may be effective to provide sufficient time before the exam at the exam site so that students can recover in a warm room.
+Rather, for instance, it may be effective to provide sufficient time before the exam at the exam site so that students can recover in a warm room.
+%For instance, it can be effective socks and slippers for students whose shoes and socks get wet due to walking through stacked snow.
 %This study provides guidance on how to set the leveling field for exam takers across Japan.
 
-Secondly, my results have implications on the matriculation process of universities.
-Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measure to select students.
+Secondly, my results have implications for the matriculation process of universities.
+Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
 Examples include extracurricular activities and statement of purposes, which are actively utilized in other countries such as the U.S..
@@
     \item Notes:
-      Temperature at prefecture capitals between 6AM and 6PM on days of Center Test is used.
+      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
       Average across two test days in each year is shown in the figure.
@@
       The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
+      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
   \end{tablenotes}
@@
       The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
+      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
       Standard errors are clustered at the prefecture level.
@@
       The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      For variables in the morning, I use average weather variables at prefecture capitals between 6AM to 9AM on exam days.
-      For variables during the exam, I use average weather variables at prefecture capitals between 9AM to 6PM on exam days.
+      For variables in the morning, I use average weather variables at prefecture capitals between 6 AM to 9 AM on exam days.
+      For variables during the exam, I use average weather variables at prefecture capitals between 9 AM to 6 PM on exam days.
       Standard errors are clustered at the prefecture level.
@@
     \item Notes:
-      Rainfall (mm) at prefecture capitals between 6AM and 6PM on days of Center Test is used.
+      Rainfall (mm) at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
       Average across two test days in each year is shown in the figure.
@@
     \item Notes:
-      Snowfall (m) at prefecture capitals between 6AM and 6PM on days of Center Test is used.
+      Snowfall (m) at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
       Average across two test days in each year is shown in the figure.
@@
     \item Notes:
-      Cumulated snow (m) at prefecture capitals between 6AM and 6PM on days of Center Test is used.
+      Cumulated snow (m) at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
       Average across two test days in each year is shown in the figure.
@@
 %    \item Notes:
-%      Temperature at prefecture capitals between 6AM and 6PM on days of Center Test is used.
+%      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
 %      Average of the temperatures across years is shown in the map.
@@
 %    \item Notes:
-%      Cumulated snow (m) on the ground at prefecture capitals between 6AM and 6PM on days of Center Test is used.
+%      Cumulated snow (m) on the ground at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
 %      Average of the values across years is shown in the map.

### 2021-04-06 Writeups/paper.tex
Decide not to include morning vs.during exam analyses

@@
 This is considered to have not only macro-level impacts but also micro-level impacts such as individual behaviors.
-To understand the effect, emerging literature has studied effects of high temperature on various outcomes both in the long run and in the short run.
+To understand the effect, emerging literature has studied effects of high temperature on various outcomes.\footnote{
+  Examples include \citet{Dell2012, Burke2015, Heyes2019, Garg2020, Geruso2018, Park2020a, Park2020b, GraffZivi2018, GraffZivin2014}.
+  \citet{Carleton2016} thoroughly review this literature.
+}
 What has been less studied in the literature is the economic impact of \textit{low} temperature.
-Given the possibility that the sea-ice loss, partly due to climate change, results in cold winters with severely low temperatures \citep{Kretschmer2016, Kim2014}, it is important to understand how low temperature can affect our lives.
+Given the possibility that the sea-ice loss, partly due to climate change, results in cold winters with severely low temperatures \citep{Kretschmer2016, Kim2014}, it is important to understand how low temperature can affect our economies and lives.
 
@@
 Most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth), for admission.
-Students take the exam on the same dates in mid-January in their prefectures.
+Students take the exam on the same dates in mid-January in their prefectures.\footnote{
+  There are 47 prefectures in Japan.
+}
 This creates a variation in weathers to which they are exposed on the exam dates.
+
 I use the weather on the dates of Center Test and investigate its effect on the matriculation for the University of Tokyo (UTokyo henceforth).
-The advantage of using the matriculation share for UTokyo as an outcome is that it is the most prestigious university in Japan.
+UTokyo is a national university and known to be the most prestigious in Japan.\footnote{
+  According to \citet{usnews}, UTokyo is the highest-ranked university in Japan (73rd ranked in the world ranking).
+  The second highest-ranked university in Japan is Kyoto University, which is 125th ranked in the world ranking.
+}
 This allows me to attribute a reduction in matriculation shares to the worse exam performance, instead of the better performance which could induce students to choose better universities.
@@
 Changing the temperature on the exam dates from 3-6 $^o$C to $<$ 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
-Moreover, additional analyses suggest that the temperature in the morning on exam dates rather than temperature during exams impact exam performance. 
-The results provide implications for effective measures to be taken to mitigate the negative impact of winter weathers.
+Moreover, additional analyses suggest that the temperature in the morning on exam dates rather than the temperature during exams impact exam performance. 
+The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
 These include preparing waiting rooms for exam takers to warm up for equalizing their pre-exam conditions or adjusting the importance of the scores at Center Test in the admission process.
@@
 This study mainly contributes to the recent but growing literature of the effects of climate factors on the outcome of high-stakes exams.
-Several previous studies have found the adverse effect of high temperature on learning, which reduces the performance at exams \citep{Park2020b, Cho2017}.
+Several previous studies have found the adverse effect of high temperature on learning, which reduces performance at exams \citep{Park2020b, Cho2017}.
 More closely to my study, \citet{GraffZivin2020} and \citet{Park2020a} show that heat on exam days decreases the exam scores at high-stakes exams in China and the U.S., respectively.
-Considering the importance of the effects the exam results can have on later life outcomes, it is important to understand how the external factors such as temperature affect exam performance and what we can do to ameliorate such effects.
+Considering the importance of the effects the exam results can have on later life outcomes, it is important to understand how external factors such as temperature affect exam performance and what we can do to ameliorate such effects.
 To complement the literature, I investigate the effect of \textit{low} temperature on exam performance.
@@
 One study based on microdata is provided by \citet{Stevens2017}, who finds a negative impact of low temperature on labor productivity of blueberry pickers in California.
-I use prefecture-level information to investigate how low temperature affects cognitive performance of exam takers.
+I use prefecture-level information to investigate how low temperature affects the cognitive performance of exam takers.
 
@@
 
-In Japan, for admission to most (almost all public) universities, students are required to take two exams.
+In Japan, for admission to public universities, students are usually required to take two exams.
 The first-stage test is called Center Test.
 Students take an exam on consecutive two days (Saturday and Sunday) in mid-January.
-%While different students can choose which subjects to take, most public universities require students to take exams on social science, language, and English on the first day and math and natural science on the second day.
+Most public universities, including UTokyo, require students to take exams on social science, language, and English on the first day and math and natural science on the second day.
 The exams start at 9:30 AM on both days and end at 6:10 PM on the first day and 5:50 PM on the second day.
@@
 High-school seniors take the test at designated sites in the area where their high schools are located.
-On the other hand, high-school graduates are assigned to test sites in the area where the homes used in their applications are located.
+On the other hand, high-school graduates are assigned to test sites in the area where the homes used in their applications are located.\footnote{
+  \citet{Watanabe2013} provides detailed descriptions on the administrations of Center Test.
+}
 
-On exam dates, heave snows can affect public transportation.
-If this makes it difficult for exam takers to come to exam sites on time, the exam can start a few hours later than scheduled to accommodate them.
-It is also possible that affected students take make-up exams a week later.
+Since January is the middle of winter in Japan, heavy snow can affect public transportation on exam dates.
+This sometimes makes it difficult for exam takers to arrive at exam sites on time.
+For the affected students, the following accommodations can be provided:
+(i) delaying the start of exams by a few hours for all exam takers at a test site,
+(ii) allowing them to take exams in a separate room, and
+(iii) allowing them to take make-up exams a week later.
+The same accommodations can be given to students who could not take exams for other reasons such as sickness or accidents in public transportation system.
 
@@
 %However, they can record their answers on their exam booklets and can bring them back home.
-%Hence, they know their scores by comparing their own answers and correct answers, which are made public through newspapers or websites of cramming schools.
+%Hence, they know their scores by comparing their own answers and correct answers, which are made public through newspapers or websites of cram schools.
 %After taking Center Test, students apply for public and private universities.\footnote{
@@
   Up to 2015, UTokyo had another second-stage exam in March and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
-%  Most of the admissions were provided for exam takers on February:
+%  Most of the admissions were provided for exam takers in February:
 %  In 2015, among 3,108 admitted students, only 100 exam takers in March got admitted.
   In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test (around 2\% of all admitted students).
-  Since the majority of students are admitted through the second-stage exam on February, I focus on the admission process for those students. 
+  Since the majority of students are admitted through the second-stage exam in February, below I focus on the admission process for those students. 
 }
@@
 Thresholds varying across years and across majors are set, and if scores at Center Test are below the thresholds, students cannot take the second-stage exam.
-Since the thresholds are announced after the application, exam takers do not know if their scores are above or below the thresholds.
+%Since the thresholds are announced after the application, exam takers do not know if their scores are above or below the thresholds.
 Secondly, the scores at Center Test are taken into consideration for admission.
@@
 
-I use two sets of data: weather and matriculation information for UTokyo.
-For weather information, I get data from \Citeauthor{jma}.
+I use two sets of data: weather and matriculation for UTokyo.
+For weather information, I obtain data from \Citeauthor{jma}.
 Their website maintains the past weather across Japan.
-In this study, based on hourly weather on exam days at prefecture capitals, I use average weathers between 6 AM to 6 PM.
+Based on hourly weather on exam days at prefecture capitals, I use average weather between 6 AM to 6 PM.
 Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
@@
 
-For matriculation information for UTokyo, I use University Basic Information maintained by \Citeauthor{univ_info}.
+For matriculation information for UTokyo, I use University Basic Information by \Citeauthor{univ_info}.
 This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
-I create the matriculation share of each prefecture, which is the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
+I calculate the matriculation shares of each prefecture as the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
   Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and the decision to go to the university or not.
-  Due to the lack of the information on the number of admitted students by prefecture, I use the information on matriculation.
+  Due to the lack of information on the number of admitted students by prefecture, I use the information on matriculation.
   For UTokyo, the number of admissions and the number of matriculations are very close:
   In 2020, among 3,083 admitted students, 3,064 students matriculate at UTokyo.
-  Moreover, it is unlikely that weathers on exam days affect decisions of admitted students to matriculate or not.
+  %Moreover, it is unlikely that weathers on exam days affect decisions of admitted students to matriculate or not.
 }
@@
 As shown in Figure \ref{fig:admission_map}, many prefectures have less than 1\% shares.
-Also, the matriculation shares of the top 5 prefectures total more than 60\%.
+Also, the matriculation shares of the top 5 prefectures amount to more than 60\%.
 This results in a small median matriculation share, $0.79 \%$.
@@
 Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
-However, the second effect is unlikely to be large for UTokyo for the following reasons.
-First, UTokyo is known to be the best university in Japan.\footnote{
-  According to \citet{usnews}, UTokyo is the highest-ranked university in Japan (73rd ranked in the world ranking).
-  The second highest-ranked university in Japan is Kyoto University, which is 125th ranked in the world ranking.
+However, the second effect is unlikely to be large for UTokyo since it is known to be the best university in Japan.\footnote{
+  \citet{Kawaguchi2008} describes that ``The University of Tokyo has occupied the top position of the single-peaked university hierarchy since its establishment in 1877.''
 }
-Secondly, since UTokyo is a national university, the tuition is cheaper than most private universities.\footnote{
-  According to \citet{mext}, in 2018, the annual tuition for national universities was 538,633 JPY ($\approx$ 4,900 USD), while the average annual tuition for private university was 904,146 ($\approx$ 8,200 USD).
-  %https://www.mext.go.jp/a_menu/koutou/shinkou/07021403/1412031_00001.htm
-}
-Therefore, I can rule out the second possibility and attribute a reduction in matriculation shares to the worse exam performance.
+%Secondly, since UTokyo is a national university, the tuition is cheaper than most private universities.\footnote{
+%  According to \citet{mext}, in 2018, the annual tuition for national universities was 538,633 JPY ($\approx$ 4,900 USD), while the average annual tuition for private university was 904,146 ($\approx$ 8,200 USD).
+%  %https://www.mext.go.jp/a_menu/koutou/shinkou/07021403/1412031_00001.htm
+%}
+Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse exam performance.
 
-In the analyses, the outcome variable, $Y_{jt}$ is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
-Let $T_{jt}$ be the average temperature on exam days in $j$ in year $t$.
+In the analyses, the outcome variable, $Y_{jt}$, is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
+Let $T_{jt}$ be the average temperature across two exam days in $j$ in year $t$.
 I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
-I include other weather variables such as rainfall, snowfall, and cumulated snow on exam days as a vector $X_{jt}$.
+I include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam days as a vector $X_{jt}$.
 As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
@@
   Figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
+}$^,$\footnote{
+  The figure shows that temperature is low for all prefectures in some years (eg. 2017) and is high in other years (eg. 2019).
+  This can bring up a concern that temperature \textit{deviations} from the prefecture average have limited variations within each year.
+  If this was the case, most variations for estimation would be absorbed by prefecture fixed effects and year fixed effects.
+  Figure \ref{fig:temperature_diff_by_year} shows that, even within each year, the temperature deviations have large variations across prefectures.
 }
@@
 
-\subsection{Main Results}
-
 The main empirical results are provided in Table \ref{tab:main_reg}.
 The standard errors are clustered at the prefecture level.
-The column (1) shows the result with a linear specification.
+Column (1) shows the result with a linear specification.
 While the point estimate is positive, which means matriculation shares are higher if an exam is held on warmer days, it is statistically insignificant. 
 The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impact of cold weather. 
-Since the mean matriculation share is $2.08$\%, the coefficient on the lowest temperature bins means that, by reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest bin, the matriculation share decreases by 9\%.
-Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$.
+Since the mean matriculation share is $2.08$\%, by reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest temperature bin, the matriculation share decreases by 9\%.
+Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$\%.
 Therefore, the same temperature change decreases the matriculation share by 22\% of the median value.
-Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in the column (1) could not capture the non-linear effect of temperature and why the coefficient is statistically insignificant.
+Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in column (1) could not capture the non-linear effect of temperature and why the coefficient is statistically insignificant.
 Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.
 
-In column (3) and (4), I add other weather variables.
+In columns (3) and (4), I add other weather variables.
 While temperature coefficients are barely affected, I find that rainfall and snowfall during exam time do not impact the matriculation shares.
@@
 To capture the effect of the existence of a certain amount of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
-This specification gives a result that, snow on the ground cumulated more than 10cm ($\approx$ 3 feet) decreases the matriculation share by 0.13 percentage point.
-
-In summary, I find a both statistically and economically significant impacts of weather on exam days.
-In particular, the estimation results show that low temperature and snow cumulated on the ground have negative impacts on the matriculation shares for UTokyo.
-In the next two subsections, I investigate the mechanisms underlying the findings.
+The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.13 percentage point.
 
@@
 
-\subsection{Weather in the morning vs. during exam}
-
-Here I investigate if the findings above are due to weathers in the morning or during the exams.
+I further investigate if the findings above are due to weather in the morning or during the exams.
 This distinction can be important since different measures should be taken to mitigate the effect of each weather.
@@
 On the other hand, statistically insignificant estimates are obtained in columns (3) and (4) with weathers during the exams, although the magnitudes are large.
-Also, including both weathers simultaneously, column (5) shows the negative and significant impact of cold weather in the morning on the matriculation share.\footnote{
+Also, including both kinds of weathers simultaneously, column (5) shows the negative and significant impact of cold weather in the morning on the matriculation share.\footnote{
   Estimates for cumulated snow are insignificant in column (5) due to multicollinearity, which blows up their standard errors.
@@
 }
-This suggests that the morning weathers on the exam dates matter for exam performance.
-
-\subsection{Preparation vs. Cognitive performance on exam days}
-
-One possible interpretation is that the temperature on exam days captures the weather before the exam, which can affect preparation for the exam. 
-For instance, cold weather can make it hard for students to focus on studying, or snowfalls can prevent students from going to schools or cramming schools for studying.
-To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
-The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for all the variables.
-Therefore, I consider that the findings in Table \ref{tab:main_reg} are due to the effect of weather variables on the exam days.
+This suggests that the morning weather on the exam dates matter for exam performance.
 
@@
 
+One possible interpretation of the results is that the temperature on exam days captures the weather before the exam, which can affect preparation for the exam. 
+For instance, cold weather can make it hard for students to focus on studying, or snowfalls can prevent students from going to schools or cram schools for studying.
+To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
+The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for all the variables.
+Therefore, I consider that the findings in Table \ref{tab:main_reg} are due to the effect of weather variables on the exam days.
+
 \section{Conclusion}\label{sec:conclusion}
@@
 This paper studies the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
-Instead of exam scores, I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
-To identify the causal impact, I exploit the variation in weathers at each prefecture on exam days.
+I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
+%To identify the causal impact, I exploit the variation in weathers at each prefecture on exam days.
 Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
-This study fills the gap and identifies the causal impact of winter weather on the matriculation.
+This study fills the gap and identifies the causal impact of winter weather on matriculation.
 
-The results show that both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam days.
+The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam days.
 Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
 Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
-Using the weathers in the morning and during the exams, I find suggestive evidence that the temperature effect is mainly caused by low temperature in the morning.
+Using the weather in the morning and during the exams, I find suggestive evidence that the temperature effect is mainly caused by low temperatures in the morning.
 This result suggests that adverse conditions for exam takers on the way to test sites affect their cognitive performance.
@@
 Several implications can be derived from the findings.
-First, the result that low temperature in the morning rather than during the exam matters suggest that equipments to improve the condition at the exam sites may have limited impacts.
-Rather, for instance, it may be effective to provide sufficient time before the exam at the exam site so that students can recover in a warm room.
-%For instance, it can be effective socks and slippers for students whose shoes and socks get wet due to walking through stacked snow.
-%This study provides guidance on how to set the leveling field for exam takers across Japan.
+First, the result that low temperature in the morning rather than during the exam matters suggests that investment to improve the condition at exam sites may have limited impacts.
+Rather, for instance, it may be effective to provide sufficient time before the exam at exam sites so that students can recover in warm rooms.
 
-Secondly, my results have implications for the matriculation process of universities.
+Secondly, my results have implications for the admission process of universities.
 Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
-Examples include extracurricular activities and statement of purposes, which are actively utilized in other countries such as the U.S..
-On the other hand, it may be effective to change the weights for Center Test and the second-stage exam.
-Since the second-stage exam is held at each university, all exam takers are exposed to similar environments.
+Examples include extracurricular activities and personal statements, which are actively utilized in other countries such as the United States.
+Also, they may change the weights for Center Test and the second-stage exam.
+Since the second-stage exams are held at each university, all exam takers are exposed to similar environments.
 This rules out the possibility that exam takers at different places are affected differently by their conditions.
-Given the importance of exam results for later life outcomes, it is desirable that universities take measures to mitigate the effect of nuisance factors on matriculation.
+Given the importance of exam results for later life outcomes, it is desirable that universities take measures to mitigate the effect of nuisance factors on admission.
 
@@
 
+\begin{figure}[H]
+  \centering
+  \caption{Deviation of temperatures from within-prefecture averages}
+  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff_by_year.pdf}
+  \label{fig:temperature_diff_by_year}
+  \footnotesize
+  \begin{tablenotes}
+    \item Notes:
+      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
+      Deviations of average temperatures across two test days from their within-prefecture means are shown in the figure by year.
+      In each panel, red dots are the deviations in the year shown above and gray dots are the deviations in the other years.
+      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
+  \end{tablenotes}
+\end{figure}
+
 %\begin{figure}[H]
@@
 
+\begin{table}[H]
+  \center
+  \caption{Regression: Matriculation share (\%) and weather on exam days by gender}
+  \input{"../Output/tex/reg_by_gender.tex"}
+  \label{tab:reg_by_gender}
+  \small
+  \begin{tablenotes}
+    \item
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{table}
+
+\begin{table}[H]
+  \center
+  \caption{Regression: Matriculation share (\%) and weather on exam days and one year after}
+  \scriptsize
+  \input{"../Output/tex/reg_placebo_exam.tex"}
+  \label{tab:reg_placebo_exam}
+  \scriptsize
+  \begin{tablenotes}
+    \item
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{table}
+
 \end{document}

### 2021-04-06 Codes/R/regression.R

@@ -16,8 +16,14 @@ git_dir <- "~/Documents/GitHub/todai_center/"
 # Load admission information =================
 admission_df <- read_csv(file.path(dropbox_dir, "Data/admission_data.csv"))
 
-# Load weather information on exam days=================
+# Load weather information on exam days =================
 weather_exam_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_on_exam_day.csv"))
+
+# Load weather information on exam days (1 year lag) =================
+weather_l1_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_l1.csv"))
+
+# Load weather information on exam days (1 year lead) =================
+weather_f1_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_f1.csv"))
 
 # Load weather information (previous 10 days) =================
 weather_pre10_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_pre10.csv"))
@@ -34,6 +40,18 @@ reg_df <- left_join(
     summarise_all(mean),
   by = c("prefecture", "year" = "exam_year")
   ) %>% 
+  left_join(
+    weather_l1_df %>% 
+      group_by(prefecture, exam_year) %>% 
+      summarise_all(mean),
+    by = c("prefecture", "year" = "exam_year")
+  ) %>% 
+  left_join(
+    weather_f1_df %>% 
+      group_by(prefecture, exam_year) %>% 
+      summarise_all(mean),
+    by = c("prefecture", "year" = "exam_year")
+  ) %>% 
   left_join(weather_pre10_df, by = c("prefecture", "year" = "exam_year")) %>% 
   left_join(weather_pre_oct_dec_df, by = c("prefecture", "year" = "exam_year")) %>% 
   mutate(
@@ -41,6 +59,14 @@ reg_df <- left_join(
     temp_cut = relevel(as.factor(temp_cut), ref = 3),
     daytime_snowfall_m = daytime_snowfall_cm / 100,
     daytime_cum_snow_m = daytime_cum_snow_cm / 100,
+    l1_temp_cut = cut(l1_temperature_degree, c(-10, 0, 3, 6, 9, 25)),
+    l1_temp_cut = relevel(as.factor(l1_temp_cut), ref = 3),
[…]

### 2021-04-06 Codes/R/weather_clean.R

@@ -68,7 +68,7 @@ weather_hour_output <- weather_hour_df %>%
       ),
     by = c("prefecture", "year", "month", "day")
   ) %>% 
-  group_by(prefecture, year, month, day) %>% 
+  group_by(prefecture, year, month) %>% 
   arrange(day, .by_group = TRUE) %>% 
   mutate(exam_first_second = row_number()) %>% 
   ungroup() %>% 
@@ -77,6 +77,62 @@ weather_hour_output <- weather_hour_df %>%
 write_csv(
   weather_hour_output,
   file.path(dropbox_dir, "Data/temp/weather_on_exam_day.csv")
+)
+
+# Hourly weather: 1 year lag  ====================
+# Load data
+weather_hour_df <- read_csv(file.path(dropbox_dir, "Data/weather_hourly_l1/all_weather_hour_l1.csv"))
+
+weather_hour_output <- weather_hour_df %>% 
+  filter(hour >= 6, hour <= 18) %>% 
+  group_by(prefecture, year, month, day) %>% 
+  summarise_at(
+      vars(temperature_degree, precipitation_mm, snowfall_cm, cum_snow_cm),
+      mean, na.rm = TRUE
+  ) %>% 
+  rename(
+    l1_temperature_degree = temperature_degree,
+    l1_precipitation_mm = precipitation_mm,
+    l1_snowfall_cm = snowfall_cm,
+    l1_cum_snow_cm = cum_snow_cm
+  ) %>% 
+  group_by(prefecture, year, month) %>% 
+  arrange(day, .by_group = TRUE) %>% 
+  mutate(exam_first_second = row_number()) %>% 
+  ungroup() %>% 
+  rename(exam_year = year, exam_month = month, exam_day = day)
+
+write_csv(
+  weather_hour_output,
+  file.path(dropbox_dir, "Data/temp/weather_l1.csv")
+)
+
+# Hourly weather: 1 year lead  ====================
+# Load data
+weather_hour_df <- read_csv(file.path(dropbox_dir, "Data/weather_hourly_f1/all_weather_hour_f1.csv"))
+
+weather_hour_output <- weather_hour_df %>% 
+  filter(hour >= 6, hour <= 18) %>% 
+  group_by(prefecture, year, month, day) %>% 
+  summarise_at(
+      vars(temperature_degree, precipitation_mm, snowfall_cm, cum_snow_cm),
+      mean, na.rm = TRUE
+  ) %>% 
+  rename(
[…]

### 2021-04-06 Codes/R/weather_diff.R

@@ -5,6 +5,9 @@ packages <- c(
   "magrittr",
   "lubridate",
   "readxl",
+  "grid",
+  "gridExtra",
+  "cowplot",
   "lfe",
   "stargazer",
   "kableExtra"
@@ -62,6 +65,56 @@ ggsave(
   width = 10,
   height = 7
 )
+
+# Deviations from within-prefecture means
+temp_diff_list <- map(
+  seq(2012, 2020),
+  function(x) weather_df_avg %>% 
+    group_by(prefecture) %>% 
+    mutate(daytime_temperature_degree = daytime_temperature_degree - mean(daytime_temperature_degree)) %>% 
+    ggplot(aes(
+      x = prefecture, y = daytime_temperature_degree, color = (exam_year == x),
+      alpha = (exam_year == x) * 1.0 + (exam_year != x) * 0.9
+      )) +
+    geom_point(size = 0.9, show.legend = FALSE) +
+    scale_x_discrete(limits = prefecture_order) +
+    scale_color_manual(values = c("black", "red")) +
+    ylab("Temperature (degree Celsius)") +
+    xlab("Prefecture") +
+    theme_minimal() +
+    ggtitle(paste0(x)) +
+    theme(
+      axis.line.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      axis.text.x = element_blank(),
+      axis.title = element_blank(),
+      axis.text.y = element_text(size = 8),
+      legend.title = element_blank(),
+      legend.text = element_blank(),
+      plot.title = element_text(size = 14, hjust = 0.5)
+    )
+)
+
+g <- grid.arrange(
+  arrangeGrob(
+    grobs = temp_diff_list, 
+    ncol = 3,
+    left = textGrob(
+      "Temperature (degree Celsicus) deviation from prefecture average", rot = 90, vjust = 0.5,
+      gp = gpar(fontsize = 18)
+    ),
+    bottom = textGrob("Prefecture", gp = gpar(fontsize = 18), vjust = 0.4)
+  )
+)
+
+ggsave(
+  filename = file.path(git_dir, "Output/images/temperature_diff_by_year.pdf"),
+  plot = g,
+  height = 10,
+  width = 10
+)
+
+
 
 # Daytime cumulated snow
 p <- weather_df_avg %>% 

### 2021-04-06 Codes/R/weather_download.R

@@ -13,8 +13,6 @@ git_dir <- "~/Documents/GitHub/todai_center/"
 # Load location information
 loc_df <- read_delim(file.path(dropbox_dir, "Data/weather_station_id.txt"), delim = ",")
 
-# Hourly weather information =============================
-
 exam_date <- c(
   "2012/1/14", "2012/1/15",
   "2013/1/19", "2013/1/20",
@@ -26,244 +24,6 @@ exam_date <- c(
   "2019/1/19", "2019/1/20",
   "2020/1/18", "2020/1/19"
 )
-
-weather_df <- c()
-
-for (i in seq(18, nrow(loc_df))) {
-  
-  print(i)
-
-  loc_i <- loc_df %>% slice(i)
-  
-  for (j in seq_along(exam_date)) {
-    exam_date_lubridate <- exam_date[j] %>% as_date()
-    exam_year <- exam_date_lubridate %>% year()
-    exam_month <- exam_date_lubridate %>% month()
-    exam_day <- exam_date_lubridate %>% day()
-    
-    if (i %in% c(11)) {
-      
-      html_data <- read_html(
-        paste0(
-          "https://www.data.jma.go.jp/obd/stats/etrn/view/hourly_a1.php?prec_no=",
-          loc_i$prec_no, "&block_no=", loc_i$block_no,
-          "&year=", as.character(exam_year), 
-          "&month=", as.character(exam_month), 
-          "&day=", as.character(exam_day), 
-          "&view="
-          )
-      )
-      # Sys.sleep(runif(1, max = 10))
-    
-      html_table <- html_data %>% 
-        html_nodes("table") %>% 
-        .[5] %>% 
-        html_table(fill = TRUE) %>% 
-        .[[1]] %>% 
-        set_colnames(
-          c(
-            "hour", "precipitation_mm", "temperature_degree",
-            "wind_speed", "wind_direction",
-            "sunny_time", "snowfall_cm", "cum_snow_cm"
-            )
-          ) %>% 
-        as_tibble() %>% 
-        slice(-1) %>% 
-        mutate(
-          across(
-            .fns = as.numeric
-          )
-        )
-      
-    } else {
-      
-      html_data <- read_html(
-        paste0(
-          "https://www.data.jma.go.jp/obd/stats/etrn/view/hourly_s1.php?prec_no=",
-          loc_i$prec_no, "&block_no=", loc_i$block_no,
-          "&year=", as.character(exam_year), 
[…]

### 2021-04-07 Writeups/paper.tex
Revised up to 5. Results

@@
 
-\title{Winter weather on exam days and matriculation for a prestigious university in Japan}%: \\ Empirical analysis on auditing reports in Brazil}
+\title{Winter weather on exam dates and matriculation for a prestigious university in Japan}%: \\ Empirical analysis on auditing reports in Brazil}
 %\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison.
@@
 This study analyzes the effect of winter weathers on exam outcomes in Japan.
-Most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth), for admission.
+For admission, most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth).
 Students take the exam on the same dates in mid-January in their prefectures.\footnote{
@@
 The estimates are not only statistically but also economically significant.
-Changing the temperature on the exam dates from 3-6 $^o$C to $<$ 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
-Moreover, additional analyses suggest that the temperature in the morning on exam dates rather than the temperature during exams impact exam performance. 
+Changing the temperature on the exam dates from 3-6 $^o$C to lower than 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
 The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
@@
 Several previous studies have found the adverse effect of high temperature on learning, which reduces performance at exams \citep{Park2020b, Cho2017}.
-More closely to my study, \citet{GraffZivin2020} and \citet{Park2020a} show that heat on exam days decreases the exam scores at high-stakes exams in China and the U.S., respectively.
-Considering the importance of the effects the exam results can have on later life outcomes, it is important to understand how external factors such as temperature affect exam performance and what we can do to ameliorate such effects.
+More closely to my study, \citet{GraffZivin2020} and \citet{Park2020a} show that heat on exam dates decreases the exam scores at high-stakes exams in China and the U.S., respectively.
+Considering the importance of the exam results for later life outcomes, it is important to understand how external factors such as temperature affect exam performance and what can be done to ameliorate such effects.
 To complement the literature, I investigate the effect of \textit{low} temperature on exam performance.
@@
 However, evidence based on data in the field is scarce.
-Country-level studies have shown a non-linear effect of temperature on economic growth, in that both low and high temperature has a negative impact \citep{Burke2015}.
-One study based on microdata is provided by \citet{Stevens2017}, who finds a negative impact of low temperature on labor productivity of blueberry pickers in California.
-I use prefecture-level information to investigate how low temperature affects the cognitive performance of exam takers.
+Country-level studies have shown a non-linear effect of temperature on economic growth, that is, both low and high temperature has a negative impact \citep{Burke2015}.
+One study based on microdata is \citet{Stevens2017}, who finds a negative impact of low temperature on labor productivity of blueberry pickers in California.
+I use prefecture-level information to investigate how low temperature affects the cognitive performance in a high-stakes exam.
 
@@
 Section \ref{sec:data} describes the data. 
-Our empirical strategy is introduced in Section \ref{sec:empirical_strategy}.
+I introduced my empirical strategy in Section \ref{sec:empirical_strategy}.
 In Section \ref{sec:results}, I present the empirical results, and Section \ref{sec:conclusion} concludes.
@@
 Questions are multiple-choice and common for all exam takers across Japan.
-High-school seniors take the test at designated sites in the area where their high schools are located.
-On the other hand, high-school graduates are assigned to test sites in the area where the homes used in their applications are located.\footnote{
+High-school seniors take the test at designated sites in the exam area\footnote{ \label{footnote:prefecture}
+  Typically, an exam area coincides with a prefecture (i.e. there is one exam area in one prefecture).
+  Large prefectures such as Hokkaido and Okinawa have several exam areas.
+  Also, several municipalities in a prefecture can be sometimes considered to be a part of a neighboring prefecture.
+  For instance, students in a couple of municipalities in Saitama prefecture could take Center Test in Tokyo.
+} where their high schools are located.
+On the other hand, high-school graduates are assigned to test sites in the exam area where the homes used in their applications are located.\footnote{
   \citet{Watanabe2013} provides detailed descriptions on the administrations of Center Test.
@@
 (i) delaying the start of exams by a few hours for all exam takers at a test site,
-(ii) allowing them to take exams in a separate room, and
-(iii) allowing them to take make-up exams a week later.
-The same accommodations can be given to students who could not take exams for other reasons such as sickness or accidents in public transportation system.
+(ii) allowing the affected students to take exams in a separate room, and
+(iii) allowing the affected students to take make-up exams a week later.
+The same accommodations can be given to students who could not take exams for other reasons such as sickness or accidents.
 
@@
 UTokyo has the second-stage exam at the end of February for two days.\footnote{
-  Up to 2015, UTokyo had another second-stage exam in March and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
+  Until 2015, UTokyo had another second-stage exam in March and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
 %  Most of the admissions were provided for exam takers in February:
@@
 Their website maintains the past weather across Japan.
-Based on hourly weather on exam days at prefecture capitals, I use average weather between 6 AM to 6 PM.
+Based on hourly weather on exam dates at prefecture capitals, I use average weather between 6 AM to 6 PM.
 Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
@@
   For UTokyo, the number of admissions and the number of matriculations are very close:
-  In 2020, among 3,083 admitted students, 3,064 students matriculate at UTokyo.
-  %Moreover, it is unlikely that weathers on exam days affect decisions of admitted students to matriculate or not.
+  In 2020, among 3,083 admitted students, 3,064 students matriculated at UTokyo.
+  %Moreover, it is unlikely that weathers on exam dates affect decisions of admitted students to matriculate or not.
 }
@@
 
-The objective of the analysis is to analyze the effect of temperature and other weather variables on exam days on the matriculation share for UTokyo.
+The objective of the analysis is to analyze the effect of temperature and other weather variables on exam dates on the matriculation share for UTokyo.
 The reason why I use the matriculation share for UTokyo is as follows:
@@
 In the analyses, the outcome variable, $Y_{jt}$, is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
-Let $T_{jt}$ be the average temperature across two exam days in $j$ in year $t$.
+Let $T_{jt}$ be the average temperature across two exam dates in $j$ in year $t$.
 I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
-I include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam days as a vector $X_{jt}$.
+I include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates as a vector $X_{jt}$.
 As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
@@
 \end{equation*}
-I exploit the variation of temperature on exam days, which I consider exogenous after controlling for prefecture-specific time-invariant factors and time-varying aggregate shocks through prefecture and year fixed effects.
-As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam days.\footnote{
+I exploit the variation of temperature on exam dates, which I consider exogenous after controlling for prefecture-specific time-invariant factors and time-varying aggregate shocks through prefecture and year fixed effects.
+As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam dates.\footnote{
   Figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
 }$^,$\footnote{
-  The figure shows that temperature is low for all prefectures in some years (eg. 2017) and is high in other years (eg. 2019).
+  The figure shows that temperature is low for most prefectures in some years (eg. 2017) and is high in other years (eg. 2019).
   This can bring up a concern that temperature \textit{deviations} from the prefecture average have limited variations within each year.
@@
 The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get into any university for the first year and retake Center Test next year in his home prefecture.
+%\footnote{
+%  In 2020, less than 40\% of the admitted students are high-school graduates.
+%  In the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
+%  If I assume that that this number corresponds to the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of the high-school graduates whose high schools and hometowns are in different prefectures as $0.40 * 0.039 = 1.6\%$.
+%}
 I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
 Hence, this classical measurement error can make the estimates conservative.
+Another potential concern is that, as discussed in footnote \ref{footnote:prefecture}, students in several municipalities in a prefecture could take Center Test in a neighboring prefecture.
+Since neighboring prefectures are geographically close, I consider that the effect of this measurement error on estimates is not large.
 
@@
 %  \centering
-%  \caption{Average temperature on two exam days in each prefecture each year}
+%  \caption{Average temperature on two exam dates in each prefecture each year}
 %  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
@@
 To capture the effect of the existence of a certain amount of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
-The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.13 percentage point.
+The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.13 percentage point.\footnote{
+  Following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual Center Test affect the matriculation shares.
+  The results in Table \ref{tab:reg_placebo_exam} show not only that the weather one year after Center Test has insignificant impacts on matriculation shares but also including the weather variables one year after Center Test barely change the coefficients on contemporaneous weather variables.
+}
 
@@
 %  \center
-%  \caption{Regression: Matriculation share (\%) and weather on exam days}
+%  \caption{Regression: Matriculation share (\%) and weather on exam dates}
 %  \input{"../Output/tex/main_reg.tex"}
@@
 
-I further investigate if the findings above are due to weather in the morning or during the exams.
-This distinction can be important since different measures should be taken to mitigate the effect of each weather.
-The results are shown in Table \ref{tab:reg_morning_exam}.
-Columns (1) and (2) show statistically significant impact of low temperature in the morning.
-On the other hand, statistically insignificant estimates are obtained in columns (3) and (4) with weathers during the exams, although the magnitudes are large.
-Also, including both kinds of weathers simultaneously, column (5) shows the negative and significant impact of cold weather in the morning on the matriculation share.\footnote{
-  Estimates for cumulated snow are insignificant in column (5) due to multicollinearity, which blows up their standard errors.
-  Their correlation coefficient is 0.99.
-  This is reasonable since their differences can be caused by new snowfall or snow melting, which cannot happen drastically within hours.
+One possible interpretation of the results is that the temperature on exam dates captures the weather before the exam due to the serial correlation.
+In other words, the effects found in Table \ref{tab:main_reg} could be interpreted as the effects on preparation for the exam. 
+For instance, cold weather can make it hard for students to focus on studying, suggested by existing studies \citep{Taylor2016}.
+%Also, snowfall can prevent students from going to schools or cram schools for studying.
+To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
+The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for temperature variables.
+This suggests that the negative impacts of low temperature found in Table \ref{tab:main_reg} are caused by the temperature on exam dates rather than temperature before exams.\footnote{
+  Notice that the coefficients on snowfall and cumulated snow on the ground are statistically significant.
+  Combined with the finding in Table \ref{tab:main_reg} that cumulated snow on the ground on the exam dates decreases students' performance, two potential explanations can be given:
+  (i) snow before the exams adversely can affect students' preparation, and
+  (ii) snowfall before the exams cumulates snow on the grdound and students' performance is affected by the cumulated snow on the exam dates.
+  Due to high collinearity of cumulated snow on the exam dates and 10 days before the exams, it is difficult to parse out these two mechanisms.
 }
-This suggests that the morning weather on the exam dates matter for exam performance.
 
@@
 %  \center
-%  \caption{Regression: Matriculation share (\%) and weather in the morning vs. during exam}
-%  \scriptsize
-%  \input{"../Output/tex/reg_morning_exam.tex"}
-%  \label{tab:reg_morning_exam}
-%  \scriptsize
+%  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
+%  \input{"../Output/tex/reg_pre10.tex"}
+%  \label{tab:reg_pre10}
+%  \small
 %  \begin{tablenotes}
@@
 %      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      For variables in the morning, I use average weather variables at prefecture capitals between 6 AM to 9 AM on exam days.
-%      For variables during the exam, I use average weather variables at prefecture capitals between 9 AM to  on exam days.
+%      I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
 %      Standard errors are clustered at the prefecture level.
@@
 %\end{table}
-
-One possible interpretation of the results is that the temperature on exam days captures the weather before the exam, which can affect preparation for the exam. 
-For instance, cold weather can make it hard for students to focus on studying, or snowfalls can prevent students from going to schools or cram schools for studying.
-To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
-The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for all the variables.
-Therefore, I consider that the findings in Table \ref{tab:main_reg} are due to the effect of weather variables on the exam days.
 
@@
 I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
-%To identify the causal impact, I exploit the variation in weathers at each prefecture on exam days.
+%To identify the causal impact, I exploit the variation in weathers at each prefecture on exam dates.
 Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
@@
 
-The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam days.
+The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam dates.
 Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
 Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
-Using the weather in the morning and during the exams, I find suggestive evidence that the temperature effect is mainly caused by low temperatures in the morning.
-This result suggests that adverse conditions for exam takers on the way to test sites affect their cognitive performance.
 
-Several implications can be derived from the findings.
-First, the result that low temperature in the morning rather than during the exam matters suggests that investment to improve the condition at exam sites may have limited impacts.
-Rather, for instance, it may be effective to provide sufficient time before the exam at exam sites so that students can recover in warm rooms.
-
-Secondly, my results have implications for the admission process of universities.
+The results have implications for the admission process of universities.
 Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
@@
   \centering
-  \caption{Average temperature on two exam days in each prefecture each year}
+  \caption{Average temperature on two exam dates in each prefecture each year}
   \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
@@
   \center
-  \caption{Regression: Matriculation share (\%) and weather on exam days}
+  \caption{Regression: Matriculation share (\%) and weather on exam dates}
+  \small
   \input{"../Output/tex/main_reg.tex"}
@@
   \center
-  \caption{Regression: Matriculation share (\%) and weather in the morning vs. during exam}
-  \scriptsize
-  \input{"../Output/tex/reg_morning_exam.tex"}
-  \label{tab:reg_morning_exam}
-  \scriptsize
+  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
+  \input{"../Output/tex/reg_pre10.tex"}
+  \label{tab:reg_pre10}
+  \small
   \begin{tablenotes}
@@
       The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      For variables in the morning, I use average weather variables at prefecture capitals between 6 AM to 9 AM on exam days.
-      For variables during the exam, I use average weather variables at prefecture capitals between 9 AM to 6 PM on exam days.
+      I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
       Standard errors are clustered at the prefecture level.
@@
   \centering
-  \caption{Average hourly rainfall (m) on two exam days in each prefecture each year}
+  \caption{Average hourly rainfall (m) on two exam dates in each prefecture each year}
   \includegraphics[width = 0.9\textwidth]{../Output/images/rainfall_diff.pdf}
@@
   \centering
-  \caption{Average hourly snowfall (m) on two exam days in each prefecture each year}
+  \caption{Average hourly snowfall (m) on two exam dates in each prefecture each year}
   \includegraphics[width = 0.9\textwidth]{../Output/images/snowfall_diff.pdf}
@@
   \centering
-  \caption{Average cumulated snow (m) on two exam days in each prefecture each year}
+  \caption{Average cumulated snow (m) on two exam dates in each prefecture each year}
   \includegraphics[width = 0.9\textwidth]{../Output/images/cum_snow_diff.pdf}
@@
 %  \centering
-%  \caption{Map of average temperature on two exam days (average across years)}
+%  \caption{Map of average temperature on two exam dates (average across years)}
 %  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_map.png}
@@
 %  \centering
-%  \caption{Map of average cumulated snow (m) on two exam days (average across years)}
+%  \caption{Map of average cumulated snow (m) on two exam dates (average across years)}
 %  \includegraphics[width = 0.9\textwidth]{../Output/images/cum_snow_map.png}
@@
 
-\begin{table}[H]
-  \center
-  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
-  \input{"../Output/tex/reg_pre10.tex"}
-  \label{tab:reg_pre10}
-  \small
-  \begin{tablenotes}
-    \item
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
-      Standard errors are clustered at the prefecture level.
-  \end{tablenotes}
-\end{table}
+%\begin{table}[H]
+%  \center
+%  \caption{Regression: Matriculation share (\%) and weather on exam dates by gender}
+%  \input{"../Output/tex/reg_by_gender.tex"}
+%  \label{tab:reg_by_gender}
+%  \small
+%  \begin{tablenotes}
+%    \item
+%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+%      Standard errors are clustered at the prefecture level.
+%  \end{tablenotes}
+%\end{table}
 
@@
   \center
-  \caption{Regression: Matriculation share (\%) and weather on exam days by gender}
-  \input{"../Output/tex/reg_by_gender.tex"}
-  \label{tab:reg_by_gender}
-  \small
-  \begin{tablenotes}
-    \item
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-      Standard errors are clustered at the prefecture level.
-  \end{tablenotes}
-\end{table}
-
-\begin{table}[H]
-  \center
-  \caption{Regression: Matriculation share (\%) and weather on exam days and one year after}
+  \caption{Falsification test: Matriculation share (\%) and weather on exam dates and one year after}
   \scriptsize
@@
       I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      I represent the contemporaneous weather variables with ``($t$)'' and the weather one year after Center Test with ``($t + 1$).''
       Standard errors are clustered at the prefecture level.

### 2021-04-07 Codes/R/regression.R

@@ -339,6 +339,10 @@ res_6 <- felm(
   data = reg_df
 )
 
+reg_df %>% 
+  select(daytime_temperature_degree, temperature_pre10_avg) %>% 
+  cor()
+
 list(res_1, res_2, res_3, res_4, res_5, res_6) %>% 
   stargazer(
     dep.var.labels = "Matriculation share (\\%)",

### 2021-04-07 Writeups/paper.tex
Revised 5. Results

@@
 
-In columns (3) and (4), I add other weather variables.
-While temperature coefficients are barely affected, I find that rainfall and snowfall during exam time do not impact the matriculation shares.
-On the other hand, the cumulated snow on the ground has a negative impact.
-To capture the effect of the existence of a certain amount of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
-The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.13 percentage point.\footnote{
+In columns (3) and (4), I add rainfall and snowfall in the regressions.
+While temperature coefficients are barely affected, I find that rainfall and snowfall on the exam dates do not impact the matriculation shares.
+In columns (5) and (6), instead of snowfall on the exam dates, I use cumulated snow on the ground and find its negative impact on the outcome. 
+To capture the effect of the existence of a certain amount of snow on the ground, column (7) allows a non-linear effect of cumulated snow.
+The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage point.\footnote{
   Following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual Center Test affect the matriculation shares.
@@
 For instance, cold weather can make it hard for students to focus on studying, suggested by existing studies \citep{Taylor2016}.
-%Also, snowfall can prevent students from going to schools or cram schools for studying.
+Also, snowfall can prevent students from going to schools or cram schools for studying.
 To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
 The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for temperature variables.
-This suggests that the negative impacts of low temperature found in Table \ref{tab:main_reg} are caused by the temperature on exam dates rather than temperature before exams.\footnote{
-  Notice that the coefficients on snowfall and cumulated snow on the ground are statistically significant.
+This suggests that the negative impacts of low temperature found in Table \ref{tab:main_reg} are caused by the temperature on exam dates rather than temperature before exams.
+
+In Table \ref{tab:reg_pre10}, the coefficients on snowfall and cumulated snow on the ground are statistically significant.
 Combined with the finding in Table \ref{tab:main_reg} that cumulated snow on the ground on the exam dates decreases students' performance, two potential explanations can be given:
-  (i) snow before the exams adversely can affect students' preparation, and
+(i) snow before the exams can adversely affect students' preparation, and
 (ii) snowfall before the exams cumulates snow on the grdound and students' performance is affected by the cumulated snow on the exam dates.
-  Due to high collinearity of cumulated snow on the exam dates and 10 days before the exams, it is difficult to parse out these two mechanisms.
-}
+Due to high collinearity of cumulated snow on the exam dates and 10 days before the exams, I cannot identify which mechanism is dominant.
 

### 2021-04-07 Writeups/paper.tex
Revision done

@@
 
-This study analyzes the effect of winter weathers on exam outcomes in Japan.
+This study analyzes the effect of winter weather on exam outcomes in Japan.
 For admission, most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth).
@@
 Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
-%\footnote{
-%  According to inter-edu, \url{https://www.inter-edu.com/univ/2019/jisseki/todai/ranking/}
-%}
 
@@
 I calculate the matriculation shares of each prefecture as the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
-  Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and the decision to go to the university or not.
+  %Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and the decision to go to the university or not.
   Due to the lack of information on the number of admitted students by prefecture, I use the information on matriculation.
@@
 Another potential concern is that, as discussed in footnote \ref{footnote:prefecture}, students in several municipalities in a prefecture could take Center Test in a neighboring prefecture.
-Since neighboring prefectures are geographically close, I consider that the effect of this measurement error on estimates is not large.
+Since neighboring prefectures are geographically close, I consider that this measurement error is not large.
 
@@
 (i) snow before the exams can adversely affect students' preparation, and
-(ii) snowfall before the exams cumulates snow on the grdound and students' performance is affected by the cumulated snow on the exam dates.
-Due to high collinearity of cumulated snow on the exam dates and 10 days before the exams, I cannot identify which mechanism is dominant.
+(ii) snowfall before the exams cumulates snow on the ground and students' performance is affected by the cumulated snow on the exam dates.
+Due to the high correlation of cumulated snow on the exam dates and 10 days before the exams, I cannot identify which mechanism is dominant.
 
@@
 Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
-Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
+Moreover, having more than 10cm of snow on the ground decreases the share by 0.11 percentage point.
 

### 2021-04-13 Writeups/paper.tex
Revision before sending to Laura

@@
     \noindent 
+    Whereas there are growing numbers of studies on how heat affects cognitive performance at high-stakes settings, the effect of cold weather has been less studied.
+    To fill this gap, I analyze the effects of winter weather on exam dates on performance at the centralized exam for university admission in Japan.
+    I find that low temperature and snow cumulated on the ground reduce matriculation shares for the most prestigious university in Japan, the University of Tokyo.
+    This result suggests that the winter weather on exam dates worsens exam performance. 
+    The implications on how to design university admissions are discussed.
 
@@
 The estimates are not only statistically but also economically significant.
-Changing the temperature on the exam dates from 3-6 $^o$C to lower than 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
+Changing the temperature on the exam dates from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
 The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
@@
 This study mainly contributes to the recent but growing literature of the effects of climate factors on the outcome of high-stakes exams.
-Several previous studies have found the adverse effect of high temperature on learning, which reduces performance at exams \citep{Park2020b, Cho2017}.
-More closely to my study, \citet{GraffZivin2020} and \citet{Park2020a} show that heat on exam dates decreases the exam scores at high-stakes exams in China and the U.S., respectively.
+Several previous studies have found the adverse effect of high temperature on learning, which exacerbates performance at exams \citep{Park2020b, Cho2017}.
+More closely to my study, \citet{GraffZivin2020} and \citet{Park2020a} show that heat on exam dates decreases the scores at high-stakes exams in China and the U.S., respectively.
 Considering the importance of the exam results for later life outcomes, it is important to understand how external factors such as temperature affect exam performance and what can be done to ameliorate such effects.
@@
 Section \ref{sec:data} describes the data. 
-I introduced my empirical strategy in Section \ref{sec:empirical_strategy}.
+I introduce my empirical strategy in Section \ref{sec:empirical_strategy}.
 In Section \ref{sec:results}, I present the empirical results, and Section \ref{sec:conclusion} concludes.
@@
 Students take an exam on consecutive two days (Saturday and Sunday) in mid-January.
-Most public universities, including UTokyo, require students to take exams on social science, language, and English on the first day and math and natural science on the second day.
+Most public universities, including UTokyo, require students to take exams on social science, language, and English on the first day and mathematics and natural science on the second day.
 The exams start at 9:30 AM on both days and end at 6:10 PM on the first day and 5:50 PM on the second day.
@@
 (iii) allowing the affected students to take make-up exams a week later.
-The same accommodations can be given to students who could not take exams for other reasons such as sickness or accidents.
+These accommodations can be given to students who could not take exams for other reasons such as sickness or accidents.
 
@@
 First, the scores are used for eligibility to take the second-stage exam.
-Thresholds varying across years and across majors are set, and if scores at Center Test are below the thresholds, students cannot take the second-stage exam.
+Thresholds varying across years and majors are set, and if scores at Center Test are below the thresholds, the students cannot take the second-stage exam.
 %Since the thresholds are announced after the application, exam takers do not know if their scores are above or below the thresholds.
@@
 The final score of a student is calculated by the weighted sum of exam scores at the first- and second-stage exams.\footnote{
-  In 2020, for the first-period exam takers, the weights for Center Test and the second-stage exam are 20\% and 80\%.
+  In 2020, the weights for Center Test and the second-stage exam are 20\% and 80\%.
+  Faculty of Medicine additionally conducts interviews on the next day of the second-stage exam to screen applicants based on community skills and personal maturity.
   %Also, until 2015, for the third-period exam takers, scores at Center Test were used only for eligibility and were not accounted for the final admission.
@@
 The summary statistics are provided in Table \ref{tab:sum_stat}.
-While the mean of the matriculation share (\%) is $2.08$,\footnote{
-  Since there are matriculations from abroad, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
-  I do not consider matriculations from abroad in the analyses since their admission is mostly based on interviews and essays.
-} the distribution is starkly skewed.
-As shown in Figure \ref{fig:admission_map}, many prefectures have less than 1\% shares.
-Also, the matriculation shares of the top 5 prefectures amount to more than 60\%.
-This results in a small median matriculation share, $0.79 \%$.
+Whereas the mean matriculation share is $2.08 \%$, the median share is much smaller ($0.79 \%$).\footnote{
+  Since there are matriculations from foreign high schools, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
+  %I do not consider matriculations from foreign high schools in the analyses since I do not know where the students take Center Test.
+  %Also, the majority of the students from foreign high schools are admitted mostly based on interviews and essays.
+  I do not consider matriculations of students from foreign high schools in the analyses since the majority of the students are admitted through a process called Special Screening Tests, which does not require Center Test scores.
+}
+This is because the distribution of the matriculation share is starkly skewed:
+while the matriculation shares of the top 5 prefectures amount to more than 60\%, many prefectures have less than 1\% shares (Figure \ref{fig:admission_map}).
 
@@
 %  \centering
-%  \caption{Map of matriculation shares (\%) (average across years)}
+%  \caption{Map of matriculation shares (\%)}
 %  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}
@@
 
-The objective of the analysis is to analyze the effect of temperature and other weather variables on exam dates on the matriculation share for UTokyo.
+I analyze the effect of temperature and other weather variables on exam dates on the matriculation share for UTokyo.
 The reason why I use the matriculation share for UTokyo is as follows:
@@
 Then, 
-(i) students from the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
-(ii) students from the prefecture who would get into a higher-ranked university may get into the middle-ranked university.
+(i) students in the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
+(ii) students in the prefecture who would get into a higher-ranked university may get into the middle-ranked university.
 Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
@@
 %}
-Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse exam performance.
+Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse performance at Center Test.
 
@@
 This means that, for these students, the weather at the exam sites is measured with errors.
-The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get into any university for the first year and retake Center Test next year in his home prefecture.
-%\footnote{
-%  In 2020, less than 40\% of the admitted students are high-school graduates.
-%  In the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
-%  If I assume that that this number corresponds to the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of the high-school graduates whose high schools and hometowns are in different prefectures as $0.40 * 0.039 = 1.6\%$.
-%}
-I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
-Hence, this classical measurement error can make the estimates conservative.
+The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get into any university and retake Center Test next year in his home prefecture.
+In 2020, 38\% of the admitted students are high-school graduates.
+Moreover, in the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
+%Hence, if I assume that that this number corresponds to the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of the high-school graduates whose high schools and hometowns are in different prefectures as $0.40 * 0.039 = 1.6\%$.
+Hence, if I use this number as an approximation for the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of students whose exam-date weather is measured with errors for the reason above as $0.38 * 0.039 = 1.5\%$.
+Given this small proportion of exam takers who are susceptible to the measurement error, I consider that the bias on the estimates is negligible.
+%I consider that, conditional on prefecture fixed effects, the measurement error (i.e.
+the difference in temperatures on the exam dates between the exam prefecture and home prefecture) is likely to be uncorrelated with the error term.
+%Hence, this classical measurement error can make the estimates conservative.
 Another potential concern is that, as discussed in footnote \ref{footnote:prefecture}, students in several municipalities in a prefecture could take Center Test in a neighboring prefecture.
-Since neighboring prefectures are geographically close, I consider that this measurement error is not large.
+Since neighboring prefectures are geographically close, I consider that the magnitude of the measurement error is small.
 
@@
 The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impact of cold weather. 
-Since the mean matriculation share is $2.08$\%, by reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest temperature bin, the matriculation share decreases by 9\%.
+Since the mean matriculation share is $2.08$\%, by reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest temperature bin (below 0 $^o$C), the matriculation share decreases by 9\%.
 Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$\%.
 Therefore, the same temperature change decreases the matriculation share by 22\% of the median value.
-Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in column (1) could not capture the non-linear effect of temperature and why the coefficient is statistically insignificant.
+Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in column (1) could not capture the non-linear effect of temperature and the estimate is statistically insignificant.
 Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.
@@
   Following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual Center Test affect the matriculation shares.
-  The results in Table \ref{tab:reg_placebo_exam} show not only that the weather one year after Center Test has insignificant impacts on matriculation shares but also including the weather variables one year after Center Test barely change the coefficients on contemporaneous weather variables.
+  The results in Table \ref{tab:reg_placebo_exam} show not only that the weather one year after Center Test has insignificant impacts on matriculation shares but also including the weather variables one year after Center Test barely changes the coefficients on contemporaneous weather variables.
 }
@@
 (i) snow before the exams can adversely affect students' preparation, and
-(ii) snowfall before the exams cumulates snow on the ground and students' performance is affected by the cumulated snow on the exam dates.
+(ii) snowfall before the exams cumulates snow on the ground and students' performance is negatively affected by the cumulated snow on the exam dates.
 Due to the high correlation of cumulated snow on the exam dates and 10 days before the exams, I cannot identify which mechanism is dominant.
@@
 
-The results have implications for the admission process of universities.
+The results in this study have implications for the admission process of universities.
 Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
 Examples include extracurricular activities and personal statements, which are actively utilized in other countries such as the United States.
-Also, they may change the weights for Center Test and the second-stage exam.
+Also, universities may adjust the weights for Center Test and the second-stage exam.
 Since the second-stage exams are held at each university, all exam takers are exposed to similar environments.
 This rules out the possibility that exam takers at different places are affected differently by their conditions.
-Given the importance of exam results for later life outcomes, it is desirable that universities take measures to mitigate the effect of nuisance factors on admission.
+Given the importance of exam results for later life outcomes of students, it is desirable that universities take measures to mitigate the effect of seemingly irrelevant factors on admission.
 
@@
   \centering
-  \caption{Map of matriculation shares (\%) (average across years)}
+  \caption{Map of matriculation shares (\%)}
   \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}

### 2021-04-13 Codes/R/regression.R

@@ -339,10 +339,6 @@ res_6 <- felm(
   data = reg_df
 )
 
-reg_df %>% 
-  select(daytime_temperature_degree, temperature_pre10_avg) %>% 
-  cor()
-
 list(res_1, res_2, res_3, res_4, res_5, res_6) %>% 
   stargazer(
     dep.var.labels = "Matriculation share (\\%)",
@@ -367,9 +363,6 @@ list(res_1, res_2, res_3, res_4, res_5, res_6) %>%
     digits = 2,
     float = FALSE
   )
-
-reg_df$cum_snow_pre10_m %>% sd
-0.12 * 0.19
 
 # Regression by male and female matriculations =====================
 

### 2021-04-13 Writeups/paper.tex
Changed the position of figures and tables

@@
 
-%Exam takers do not receive their scores until the next May at earliest.
-%However, they can record their answers on their exam booklets and can bring them back home.
-%Hence, they know their scores by comparing their own answers and correct answers, which are made public through newspapers or websites of cram schools.
-%After taking Center Test, students apply for public and private universities.\footnote{
-%  There are private universities who accept applications before Center Test.
-%}
-%Applicants for public universities typically take the second-stage exam.
-
 After Center Test, applicants for public universities typically take the second-stage exam.
@@
   Until 2015, UTokyo had another second-stage exam in March and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
-%  Most of the admissions were provided for exam takers in February:
-%  In 2015, among 3,108 admitted students, only 100 exam takers in March got admitted.
   In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test (around 2\% of all admitted students).
@@
 
-%Most public universities, including UTokyo, have three periods for the second-stage exam:
-%usually, the first one is at the end of February, the second one is on the first week of March, and the third one is on the second week of March.
-%Students can apply for only one university at each exam period.
-%While different universities accept applications for different periods, most universities have only one (typically the first period) or two (typically the first and the third periods) periods.
-%Up to 2015, UTokyo had two exam periods, the first and the third ones, although most of the admissions were provided for exam takers at the first exam period.\footnote{
-%  In 2015, while 3,008 students got admitted through the first-period exam, only 100 students got admitted through the third-period exam.
-%  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01_h27.html
-%}
-%In 2016, UTokyo abolished the third-period exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test.
-%In the latter process, students take interviews in November before Center Test, and after taking Center Test, final admissions are determined based on the results both of interviews and scores at Center Test.\footnote{
-%  In 2020, among 3,083 admitted students, only 73 students got admitted through this process.
-%  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01.html
-%}
-
 In admission for UTokyo, scores at Center Test are used for two purposes.
@@
 Thresholds varying across years and majors are set, and if scores at Center Test are below the thresholds, the students cannot take the second-stage exam.
-%Since the thresholds are announced after the application, exam takers do not know if their scores are above or below the thresholds.
 Secondly, the scores at Center Test are taken into consideration for admission.
@@
   Faculty of Medicine additionally conducts interviews on the next day of the second-stage exam to screen applicants based on community skills and personal maturity.
-  %Also, until 2015, for the third-period exam takers, scores at Center Test were used only for eligibility and were not accounted for the final admission.
 }
@@
 I calculate the matriculation shares of each prefecture as the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
-  %Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and the decision to go to the university or not.
   Due to the lack of information on the number of admitted students by prefecture, I use the information on matriculation.
@@
   In 2020, among 3,083 admitted students, 3,064 students matriculated at UTokyo.
-  %Moreover, it is unlikely that weathers on exam dates affect decisions of admitted students to matriculate or not.
 }
@@
   Since there are matriculations from foreign high schools, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
-  %I do not consider matriculations from foreign high schools in the analyses since I do not know where the students take Center Test.
-  %Also, the majority of the students from foreign high schools are admitted mostly based on interviews and essays.
   I do not consider matriculations of students from foreign high schools in the analyses since the majority of the students are admitted through a process called Special Screening Tests, which does not require Center Test scores.
@@
 
-%\begin{table}[H]
-%  \centering
-%  \caption{Summary Statistics}
-%  \resizebox{0.8\linewidth}{!}{
-%  \input{"../Output/tex/sum_stat.tex"}
-%  }
-%  \label{tab:sum_stat}
-%  \footnotesize
-%  \begin{tablenotes}
-%    \item 
-%      Notes:
-%      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
-%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-%  \end{tablenotes}
-%\end{table}
+\begin{table}[H]
+  \centering
+  \caption{Summary Statistics}
+  \resizebox{0.8\linewidth}{!}{
+  \input{"../Output/tex/sum_stat.tex"}
+  }
+  \label{tab:sum_stat}
+  \footnotesize
+  \begin{tablenotes}
+    \item 
+      Notes:
+      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+  \end{tablenotes}
+\end{table}
 
-%\begin{figure}[H]
-%  \centering
-%  \caption{Map of matriculation shares (\%)}
-%  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}
-%  \label{fig:admission_map}
-%  \footnotesize
-%  \begin{tablenotes}
-%    \item Notes:
-%      This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
-%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      Average of the shares across years is shown in the map.
-%      Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
-%  \end{tablenotes}
-%\end{figure}
+\begin{figure}[H]
+  \centering
+  \caption{Map of matriculation shares (\%)}
+  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}
+  \label{fig:admission_map}
+  \footnotesize
+  \begin{tablenotes}
+    \item Notes:
+      This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      Average of the shares across years is shown in the map.
+      Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
+  \end{tablenotes}
+\end{figure}
 
@@
 }
-%Secondly, since UTokyo is a national university, the tuition is cheaper than most private universities.\footnote{
-%  According to \citet{mext}, in 2018, the annual tuition for national universities was 538,633 JPY ($\approx$ 4,900 USD), while the average annual tuition for private university was 904,146 ($\approx$ 8,200 USD).
-%  %https://www.mext.go.jp/a_menu/koutou/shinkou/07021403/1412031_00001.htm
-%}
 Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse performance at Center Test.
@@
 Moreover, in the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
-%Hence, if I assume that that this number corresponds to the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of the high-school graduates whose high schools and hometowns are in different prefectures as $0.40 * 0.039 = 1.6\%$.
 Hence, if I use this number as an approximation for the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of students whose exam-date weather is measured with errors for the reason above as $0.38 * 0.039 = 1.5\%$.
 Given this small proportion of exam takers who are susceptible to the measurement error, I consider that the bias on the estimates is negligible.
-%I consider that, conditional on prefecture fixed effects, the measurement error (i.e.
-the difference in temperatures on the exam dates between the exam prefecture and home prefecture) is likely to be uncorrelated with the error term.
-%Hence, this classical measurement error can make the estimates conservative.
 Another potential concern is that, as discussed in footnote \ref{footnote:prefecture}, students in several municipalities in a prefecture could take Center Test in a neighboring prefecture.
@@
 
-%\begin{figure}[H]
-%  \centering
-%  \caption{Average temperature on two exam dates in each prefecture each year}
-%  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
-%  \label{fig:temperature_diff}
-%  \footnotesize
-%  \begin{tablenotes}
-%    \item Notes:
-%      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
-%      Average across two test days in each year is shown in the figure.
-%      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
-%  \end{tablenotes}
-%\end{figure}
+\begin{figure}[H]
+  \centering
+  \caption{Average temperature on two exam dates in each prefecture each year}
+  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
+  \label{fig:temperature_diff}
+  \footnotesize
+  \begin{tablenotes}
+    \item Notes:
+      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
+      Average across two test days in each year is shown in the figure.
+      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
+  \end{tablenotes}
+\end{figure}
 
@@
 
-%\begin{table}[H]
-%  \center
-%  \caption{Regression: Matriculation share (\%) and weather on exam dates}
-%  \input{"../Output/tex/main_reg.tex"}
-%  \label{tab:main_reg}
-%  \small
-%  \begin{tablenotes}
-%    \item
-%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-%      Standard errors are clustered at the prefecture level.
-%  \end{tablenotes}
-%\end{table}
+\begin{table}[H]
+  \center
+  \caption{Regression: Matriculation share (\%) and weather on exam dates}
+  \input{"../Output/tex/main_reg.tex"}
+  \label{tab:main_reg}
+  \small
+  \begin{tablenotes}
+    \item
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{table}
 
@@
 
-%\begin{table}[H]
-%  \center
-%  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
-%  \input{"../Output/tex/reg_pre10.tex"}
-%  \label{tab:reg_pre10}
-%  \small
-%  \begin{tablenotes}
-%    \item
-%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
-%      Standard errors are clustered at the prefecture level.
-%  \end{tablenotes}
-%\end{table}
+\begin{table}[H]
+  \center
+  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
+  \input{"../Output/tex/reg_pre10.tex"}
+  \label{tab:reg_pre10}
+  \small
+  \begin{tablenotes}
+    \item
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
+      Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{table}
 
@@
 I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
-%To identify the causal impact, I exploit the variation in weathers at each prefecture on exam dates.
 Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
@@
 
-\section{Figures}
-
-\begin{figure}[H]
-  \centering
-  \caption{Map of matriculation shares (\%)}
-  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}
-  \label{fig:admission_map}
-  \footnotesize
-  \begin{tablenotes}
-    \item Notes:
-      This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      Average of the shares across years is shown in the map.
-      Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
-  \end{tablenotes}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \caption{Average temperature on two exam dates in each prefecture each year}
-  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
-  \label{fig:temperature_diff}
-  \footnotesize
-  \begin{tablenotes}
-    \item Notes:
-      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
-      Average across two test days in each year is shown in the figure.
-      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
-  \end{tablenotes}
-\end{figure}
-
-\section{Tables}
-
-\begin{table}[H]
-  \centering
-  \caption{Summary Statistics}
-  \resizebox{0.8\linewidth}{!}{
-  \input{"../Output/tex/sum_stat.tex"}
-  }
-  \label{tab:sum_stat}
-  \footnotesize
-  \begin{tablenotes}
-    \item 
-      Notes:
-      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-  \end{tablenotes}
-\end{table}
-
-\begin{table}[H]
-  \center
-  \caption{Regression: Matriculation share (\%) and weather on exam dates}
-  \small
-  \input{"../Output/tex/main_reg.tex"}
-  \label{tab:main_reg}
-  \small
-  \begin{tablenotes}
-    \item
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-      Standard errors are clustered at the prefecture level.
-  \end{tablenotes}
-\end{table}
-
-\begin{table}[H]
-  \center
-  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
-  \input{"../Output/tex/reg_pre10.tex"}
-  \label{tab:reg_pre10}
-  \small
-  \begin{tablenotes}
-    \item
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
-      Standard errors are clustered at the prefecture level.
-  \end{tablenotes}
-\end{table}
+%\section{Figures}
+%
+%\begin{figure}[H]
+%  \centering
+%  \caption{Map of matriculation shares (\%)}
+%  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}
+%  \label{fig:admission_map}
+%  \footnotesize
+%  \begin{tablenotes}
+%    \item Notes:
+%      This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
+%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+%      Average of the shares across years is shown in the map.
+%      Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
+%  \end{tablenotes}
+%\end{figure}
+%
+%\begin{figure}[H]
+%  \centering
+%  \caption{Average temperature on two exam dates in each prefecture each year}
+%  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
+%  \label{fig:temperature_diff}
+%  \footnotesize
+%  \begin{tablenotes}
+%    \item Notes:
+%      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
+%      Average across two test days in each year is shown in the figure.
+%      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
+%  \end{tablenotes}
+%\end{figure}
+%
+%\section{Tables}
+%
+%\begin{table}[H]
+%  \centering
+%  \caption{Summary Statistics}
+%  \resizebox{0.8\linewidth}{!}{
+%  \input{"../Output/tex/sum_stat.tex"}
+%  }
+%  \label{tab:sum_stat}
+%  \footnotesize
+%  \begin{tablenotes}
+%    \item 
+%      Notes:
+%      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
+%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+%  \end{tablenotes}
+%\end{table}
+%
+%\begin{table}[H]
+%  \center
+%  \caption{Regression: Matriculation share (\%) and weather on exam dates}
+%  \small
+%  \input{"../Output/tex/main_reg.tex"}
+%  \label{tab:main_reg}
+%  \small
+%  \begin{tablenotes}
+%    \item
+%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+%      Standard errors are clustered at the prefecture level.
+%  \end{tablenotes}
+%\end{table}
+%
+%\begin{table}[H]
+%  \center
+%  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
+%  \input{"../Output/tex/reg_pre10.tex"}
+%  \label{tab:reg_pre10}
+%  \small
+%  \begin{tablenotes}
+%    \item
+%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+%      I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
+%      Standard errors are clustered at the prefecture level.
+%  \end{tablenotes}
+%\end{table}
 

### 2021-04-23 Writeups/paper.tex
Prepared tables and figures for beamer slides

@@
     To fill this gap, I analyze the effects of winter weather on exam dates on performance at the centralized exam for university admission in Japan.
+    Since students take the exam in their own prefectures, they are exposed to different weather conditions on the exam dates. 
     I find that low temperature and snow cumulated on the ground reduce matriculation shares for the most prestigious university in Japan, the University of Tokyo.
     This result suggests that the winter weather on exam dates worsens exam performance. 
-    The implications on how to design university admissions are discussed.
+    %The implications on how to design university admissions are discussed.
 
@@
 In Japan, for admission to public universities, students are usually required to take two exams.
-The first-stage test is called Center Test.
+The first-stage test is Center Test.
 Students take an exam on consecutive two days (Saturday and Sunday) in mid-January.
@@
   \centering
-  \caption{Average temperature on two exam dates in each prefecture each year}
+  \caption{Average temperature (\degree C) on two exam dates in each prefecture each year}
   \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
@@
 In columns (5) and (6), instead of snowfall on the exam dates, I use cumulated snow on the ground and find its negative impact on the outcome. 
-To capture the effect of the existence of a certain amount of snow on the ground, column (7) allows a non-linear effect of cumulated snow.
+To capture the effect of the existence of a certain amount of snow on the ground, columns (7) and (8) allow a non-linear effect of cumulated snow.
 The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage point.\footnote{
@@
   \caption{Regression: Matriculation share (\%) and weather on exam dates}
+  \footnotesize
   \input{"../Output/tex/main_reg.tex"}
@@
 For instance, cold weather can make it hard for students to focus on studying, suggested by existing studies \citep{Taylor2016}.
-Also, snowfall can prevent students from going to schools or cram schools for studying.
+Also, snowfall can prevent students from going to high schools or cram schools for studying.
 To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
-The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for temperature variables.
-This suggests that the negative impacts of low temperature found in Table \ref{tab:main_reg} are caused by the temperature on exam dates rather than temperature before exams.
+The results in columns (1) and (2) in Table \ref{tab:reg_pre10} show statistically insignificant estimates for the temperature variables.
+Moreover, including the weather variables for 10 days before the exams barely changes the estimates on the weather variables on the exam dates (columns (3) and (4)).
+These suggest that the negative impacts of low temperature found in Table \ref{tab:main_reg} are mainly caused by the temperature on exam dates rather than temperature before exams.
 
-In Table \ref{tab:reg_pre10}, the coefficients on snowfall and cumulated snow on the ground are statistically significant.
+In columns (1) and (2), the coefficients on snowfall and cumulated snow on the ground are statistically significant.
 Combined with the finding in Table \ref{tab:main_reg} that cumulated snow on the ground on the exam dates decreases students' performance, two potential explanations can be given:
-(i) snow before the exams can adversely affect students' preparation, and
+(i) snow before the exams can adversely affect students' preparation due to, for instance, more difficulty in going to high schools or cram schools, and
 (ii) snowfall before the exams cumulates snow on the ground and students' performance is negatively affected by the cumulated snow on the exam dates.
-Due to the high correlation of cumulated snow on the exam dates and 10 days before the exams, I cannot identify which mechanism is dominant.
+Including the weather variables on the exam dates, columns (3) and (4) show that only cumulated snow on exam dates has significant impact on the outcome.
+This suggests that the second mechanism is dominant.
 
@@
   \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
+  \scriptsize
   \input{"../Output/tex/reg_pre10.tex"}
   \label{tab:reg_pre10}
-  \small
+  \scriptsize
   \begin{tablenotes}
@@
       The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
+      For weather variables with "(exam dates)", I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      For weather variables with "(previous 10 days)", I use their averages at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
       Standard errors are clustered at the prefecture level.
@@
       Average across two test days in each year is shown in the figure.
-      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
+      The prefectures are ordered by the mean rainfall across years (lowest to left and highest to right).
   \end{tablenotes}
@@
       Average across two test days in each year is shown in the figure.
-      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
+      The prefectures are ordered by the mean snowfall across years (lowest to left and highest to right).
   \end{tablenotes}
@@
       Average across two test days in each year is shown in the figure.
-      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
+      The prefectures are ordered by the mean cumulated snow across years (lowest to left and highest to right).
   \end{tablenotes}
@@
       In each panel, red dots are the deviations in the year shown above and gray dots are the deviations in the other years.
-      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
+      The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
   \end{tablenotes}

### 2021-04-23 Codes/R/Data_clean/merge_data.R

@@ -1,0 +1,96 @@
+# Merge data for regressions
+
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load admission information =================
+admission_df <- read_csv(file.path(dropbox_dir, "Data/admission_data.csv"))
+
+# Load weather information on exam days =================
+weather_exam_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_on_exam_day.csv"))
+
+# Load weather information on exam days (1 year lag) =================
+weather_l1_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_l1.csv"))
+
+# Load weather information on exam days (1 year lead) =================
+weather_f1_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_f1.csv"))
+
+# Load weather information (previous 10 days) =================
+weather_pre10_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_pre10.csv"))
+
+# Load weather information (Oct, Nov, Dec before the exams) =================
+weather_pre_oct_dec_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_pre_oct_dec.csv"))
+
+# Load weather information (Previous summer from May to September) =================
+weather_summer_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_summer.csv"))
+
+# Regression with average weather =====================
+
+reg_df <- left_join(
+  admission_df,
+  weather_exam_df %>% 
+    group_by(prefecture, exam_year) %>% 
+    summarise_all(mean),
+  by = c("prefecture", "year" = "exam_year")
+  ) %>% 
+  left_join(
+    weather_l1_df %>% 
+      group_by(prefecture, exam_year) %>% 
+      summarise_all(mean),
+    by = c("prefecture", "year" = "exam_year")
+  ) %>% 
+  left_join(
[…]

### 2021-04-23 Codes/R/Data_clean/weather_clean.R

@@ -192,7 +192,36 @@ write_csv(
   file.path(dropbox_dir, "Data/temp/weather_pre_oct_dec.csv")
 )
 
+# Summer weather ====================
+# Load data
+weather_summer_df <- read_csv(file.path(dropbox_dir, "Data/weather_summer/all_weather_summer.csv"))
 
+temp_cut <- c(-10, 18, 20, 22, 24, 26, 28, 30, 50)
+temp_max_cut <- c(-10, 22, 24, 26, 28, 30, 32, 34, 50)
+weather_summer_output <- weather_summer_df %>% 
+  mutate(
+    temp_group = cut(
+      temperature_avg_degree, 
+      breaks = temp_cut,
+      labels = paste0("temp_group_", seq(length(temp_cut) - 1))
+      ),
+    temp_max_group = cut(
+      temperature_max_degree, 
+      breaks = temp_max_cut,
+      labels = paste0("temp_max_group_", seq(length(temp_max_cut) - 1))
+      ),
+    ) %>% 
+  mutate(value = 1) %>% 
+  spread(temp_group, value, fill = 0) %>% 
+  mutate(value = 1) %>% 
+  spread(temp_max_group, value, fill = 0) %>% 
+  group_by(year, prefecture) %>% 
+  summarise_at(vars(starts_with("temp_")), sum, na.rm = TRUE)
+
+write_csv(
+  weather_summer_output,
+  file.path(dropbox_dir, "Data/temp/weather_summer.csv")
+)
 
 
 

### 2021-04-23 Codes/R/Data_clean/weather_download.R

@@ -526,6 +526,130 @@ write_csv(
   file.path(dropbox_dir, "Data/weather_day/", "all_weather_day.csv")
   )
 
+# Download daily weather in the previous summer -----------------------
+
+get_summer_weather <- function(loc_i, year_month) {
+  
+  year <- year_month[[1]]
+  month <- year_month[[2]]
+
+  if (i %in% c(11)) {
+    
+    html_data <- read_html(
+      paste0(
+        "https://www.data.jma.go.jp/obd/stats/etrn/view/daily_a1.php?prec_no=",
+        loc_i$prec_no, "&block_no=", loc_i$block_no,
+        "&year=", as.character(year - 1), 
+        str_interp("&month=${month}"), "&day=1", "&view="
+        )
+    )
+    # Sys.sleep(runif(1, max = 10))
+  
+    html_table <- html_data %>% 
+      html_nodes("table") %>% 
+      .[6] %>% 
+      html_table(fill = TRUE) %>% 
+      .[[1]] %>% 
+      set_colnames(
+        c(
+          "day", 
+          "precipitation_sum_mm",  "precipitation_max_hour_mm",  "precipitation_max_10min_mm", 
+          "temperature_avg_degree", "temperature_max_degree", "temperature_min_degree",
+          "wind_speed_avg", "wind_speed_max", "wind_direction_max", 
+          "wind_speed_max_max", "wind_direction_max_max", "wind_direction_most_frequent",
+          "sunny_time", "snowfall_cm", "cum_snow_cm"
+          )
+        ) %>% 
+      as_tibble() %>% 
+      slice(- c(1, 2)) %>% 
+      mutate(
+        across(
+          .fns = as.numeric
+        )
+      )
+    
+  } else {
+    
+    html_data <- read_html(
+      paste0(
+        "https://www.data.jma.go.jp/obd/stats/etrn/view/daily_s1.php?prec_no=",
+        loc_i$prec_no, "&block_no=", loc_i$block_no,
+        "&year=", as.character(year - 1), 
+        str_interp("&month=${month}"), "&day=1", "&view="
+        )
+    )
+    # Sys.sleep(runif(1, min = 20, max = 40))
+  
+    html_table <- html_data %>% 
+      html_nodes("table") %>% 
+      .[6] %>% 
+      html_table(fill = TRUE) %>% 
+      .[[1]] %>% 
+      set_colnames(
+        c(
[…]

### 2021-04-23 Codes/R/Regression/art_science_regression.R

@@ -1,0 +1,95 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load regression data =================
+reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
+
+# Import function to make estimate figures
+source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
+
+# Regression for humanity and science majors separately =====================
+
+res_1 <- felm(
+  admission_Arts_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_2 <- felm(
+  admission_Arts_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_3 <- felm(
+  admission_Sciences_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_4 <- felm(
+  admission_Sciences_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+list(res_1, res_2, res_3, res_4) %>% 
+  stargazer(
+    dep.var.labels = c("Matriculation share (\\%, Humanity)", "Matriculation share (\\%, Science)"),
+    covariate.labels = c(
+      "Temperature (\\degree C) $\\le$ 0",
+      "Temperature (\\degree C) $>$ 0, $\\le$ 3",
+      "Temperature (\\degree C) $>$ 6, $\\le$ 9",
+      "Temperature (\\degree C) $>$ 9",
+      "Rainfall (mm)",
+      "Snowfall (m)",
+      "Cumulated snow (m)",
+      "Cumulated snow $>$ .10 m"
+    ),
+    title = "",
+    add.lines = list(
[…]

### 2021-04-23 Codes/R/Regression/gender_regression.R

@@ -1,0 +1,97 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load regression data =================
+reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
+
+# Import function to make estimate figures
+source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
+
+# Regression by male and female matriculations =====================
+
+res_1 <- felm(
+  admission_female_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_2 <- felm(
+  admission_female_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_3 <- felm(
+  admission_male_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_4 <- felm(
+  admission_male_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+list(res_1, res_2, res_3, res_4) %>% 
+  stargazer(
+    dep.var.labels = c("Matriculation share (\\%, female)", "Matriculation share (\\%, male)"),
+    covariate.labels = c(
+      "Temperature (\\degree C) $\\le$ 0",
+      "Temperature (\\degree C) $>$ 0, $\\le$ 3",
+      "Temperature (\\degree C) $>$ 6, $\\le$ 9",
+      "Temperature (\\degree C) $>$ 9",
+      "Rainfall (mm)",
+      "Snowfall (m)",
+      "Cumulated snow (m)",
+      "Cumulated snow $>$ .10 m"
+    ),
+    title = "",
+    add.lines = list(
+      c("Prefecture FE", rep("Yes", 4)),
[…]

### 2021-04-23 Codes/R/Regression/main_regression.R

@@ -1,0 +1,137 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer",
+  "latex2exp"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load regression data =================
+reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
+
+# Import function to make estimate figures
+source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
+
+# Main regression ==========================
+
+res_1 <- felm(
+  admission_total_share ~ daytime_temperature_degree | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_2 <- felm(
+  admission_total_share ~ temp_cut | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_3 <- felm(
+  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_snowfall_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_4 <- felm(
+  admission_total_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_5 <- felm(
+  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_cum_snow_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_6 <- felm(
+  admission_total_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_7 <- felm(
+  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + factor(daytime_cum_snow_m > .1) | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_8 <- felm(
[…]

### 2021-04-23 Codes/R/Regression/make_coef_figure.R

@@ -1,0 +1,54 @@
+# Function to make estimates coefficient figures
+
+make_coef_figure <- function(res, temp_cut_str = "^temp_cut") {
+
+  temp_cut_names <- grepl(temp_cut_str, rownames(res$coefficients))
+
+  coef <- res %>%
+    summary %>%
+    .$coef %>%
+    .[temp_cut_names, "Estimate"]
+  coef <- c(coef[1:2], 0, coef[3:4])
+  se <- res %>%
+    summary %>%
+    .$coef %>%
+    .[temp_cut_names, "Cluster s.e."]
+  se <- c(se[1:2], 0, se[3:4])
+
+  b <- as.numeric(coef)
+  lb <- as.numeric(coef - 1.645 * se)
+  ub <- as.numeric(coef + 1.645 * se)
+  x_label = c(
+    "<= 0", 
+    "0-3",
+    "3-6",
+    "6-9",
+    "> 9"
+    )
+  df <- tibble(x_label = x_label, b = b, ymin = lb, ymax = ub)
+
+  fig <- ggplot(df, aes(x = factor(x_label, levels = x_label), y = b)) + 
+    geom_point() +
+    geom_errorbar(aes(ymin = ymin, ymax = ymax), width = .2) +
+    geom_hline(yintercept = 0, alpha = 0.4) +
+    theme_classic() +
+    ylab("Coefficients") +
+    xlab("Temperature bins (Celsius)") +
+    theme(axis.title = element_text(size = 15),
+          axis.text = element_text(size = 12)) +
+    scale_x_discrete(
+      labels = expression(
+        "" <= 0,
+        0-3,
+        3-6,
+        6-9,
+        "" > 9
+      )
+    ) +
+    ylim(-0.4, 0.4)
+
+  
+  return(fig)
+}
+
+

### 2021-04-23 Codes/R/Regression/placebo_regression.R

@@ -1,0 +1,108 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load regression data =================
+reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
+
+# Import function to make estimate figures
+source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
+
+# Placebo regression with lead weather =====================
+
+res_1 <- felm(
+  admission_total_share ~ f1_temp_cut + f1_precipitation_mm + f1_snowfall_m |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_2 <- felm(
+  admission_total_share ~ f1_temp_cut + f1_precipitation_mm + f1_cum_snow_m |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_3 <- felm(
+  admission_total_share ~ 
+    temp_cut + daytime_precipitation_mm + daytime_snowfall_m +
+    f1_temp_cut + f1_precipitation_mm + f1_snowfall_m |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_4 <- felm(
+  admission_total_share ~ 
+    temp_cut + daytime_precipitation_mm + daytime_cum_snow_m +
+    f1_temp_cut + f1_precipitation_mm + f1_cum_snow_m |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+list(res_1, res_2, res_3, res_4) %>% 
+  stargazer(
+    dep.var.labels = "Matriculation share (\\%)",
+    order = c(seq(1, 4), seq(5, 7), seq(8, 11), seq(12, 14)),
+    covariate.labels = c(
+      "Temperature (\\degree C) $\\le$ 0 ($t$)",
+      "Temperature (\\degree C) $>$ 0, $\\le$ 3 ($t$)",
+      "Temperature (\\degree C) $>$ 6, $\\le$ 9 ($t$)",
[…]

### 2021-04-23 Codes/R/Regression/pre10_regression.R

@@ -1,0 +1,135 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load regression data =================
+reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
+
+# Import function to make estimate figures
+source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
+
+# Regression with weather for the previous 10 days =====================
+
+res_1 <- felm(
+  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10_m |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_2 <- felm(
+  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10_m |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_3 <- felm(
+  admission_total_share ~ 
+    temp_cut + daytime_precipitation_mm + daytime_snowfall_m +
+    temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10_m |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_4 <- felm(
+  admission_total_share ~ 
+    temp_cut + daytime_precipitation_mm + daytime_cum_snow_m +
+    temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10_m |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+list(res_1, res_2, res_3, res_4) %>% 
+  stargazer(
+    dep.var.labels = "Matriculation share (\\%)",
+    order = c(seq(1, 4), seq(5, 7), seq(8, 11), seq(12, 14)),
+    covariate.labels = c(
+      "Temperature (\\degree C) $\\le$ 0 (exam dates)",
+      "Temperature (\\degree C) $>$ 0, $\\le$ 3 (exam dates)",
+      "Temperature (\\degree C) $>$ 6, $\\le$ 9 (exam dates)",
[…]

### 2021-04-23 Codes/R/Regression/regression.R

@@ -13,73 +13,8 @@ pacman::p_load(packages, character.only = TRUE)
 dropbox_dir <- "~/Dropbox/todai_center/"
 git_dir <- "~/Documents/GitHub/todai_center/"
 
-# Load admission information =================
-admission_df <- read_csv(file.path(dropbox_dir, "Data/admission_data.csv"))
-
-# Load weather information on exam days =================
-weather_exam_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_on_exam_day.csv"))
-
-# Load weather information on exam days (1 year lag) =================
-weather_l1_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_l1.csv"))
-
-# Load weather information on exam days (1 year lead) =================
-weather_f1_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_f1.csv"))
-
-# Load weather information (previous 10 days) =================
-weather_pre10_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_pre10.csv"))
-
-# Load weather information (Oct, Nov, Dec before the exams) =================
-weather_pre_oct_dec_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_pre_oct_dec.csv"))
-
-# Regression with average weather =====================
-
-reg_df <- left_join(
-  admission_df,
-  weather_exam_df %>% 
-    group_by(prefecture, exam_year) %>% 
-    summarise_all(mean),
-  by = c("prefecture", "year" = "exam_year")
-  ) %>% 
-  left_join(
-    weather_l1_df %>% 
-      group_by(prefecture, exam_year) %>% 
-      summarise_all(mean),
-    by = c("prefecture", "year" = "exam_year")
-  ) %>% 
-  left_join(
-    weather_f1_df %>% 
-      group_by(prefecture, exam_year) %>% 
-      summarise_all(mean),
-    by = c("prefecture", "year" = "exam_year")
-  ) %>% 
-  left_join(weather_pre10_df, by = c("prefecture", "year" = "exam_year")) %>% 
-  left_join(weather_pre_oct_dec_df, by = c("prefecture", "year" = "exam_year")) %>% 
-  mutate(
[…]

### 2021-04-23 Codes/R/SumStat/sumstat.R

@@ -66,13 +66,13 @@ map(
   as.matrix() %>% 
   set_colnames(NULL) %>% 
   set_rownames(c(
-    "Matriculation share (%)",
-    "Temperature (degree C)",
+    "Matriculation share (\\%)",
+    "Temperature (\\degree C)",
     "Hourly precipitation (mm)",
     "Hourly snowfall (m)",
     "Cumulated snow (m)"
   )) %>% 
-  kbl("latex", booktabs = TRUE) %>% 
+  kbl("latex", booktabs = TRUE, escape = FALSE) %>% 
   add_header_above(
     c(" ", "N", "Mean", "SD", "Median", "Min", "Max")
   ) %>% 

### 2021-04-23 Codes/R/SumStat/weather_diff.R

@@ -37,6 +37,12 @@ weather_df_avg <- weather_df %>%
   mutate(prefecture = rev(factor(prefecture, levels = prefecture_order)))
 
 # Daytime temperature
+prefecture_order <- weather_df_avg %>% 
+  group_by(prefecture) %>% 
+  summarise_at(vars(daytime_temperature_degree), mean, na.rm = TRUE) %>% 
+  arrange(daytime_temperature_degree) %>% 
+  .$prefecture %>% 
+  as.vector()
 p <- weather_df_avg %>% 
   ggplot(aes(x = prefecture, y = daytime_temperature_degree, color = factor(exam_year))) +
   geom_point() +
@@ -67,6 +73,12 @@ ggsave(
 )
 
 # Deviations from within-prefecture means
+prefecture_order <- weather_df_avg %>% 
+  group_by(prefecture) %>% 
+  summarise_at(vars(daytime_temperature_degree), mean, na.rm = TRUE) %>% 
+  arrange(daytime_temperature_degree) %>% 
+  .$prefecture %>% 
+  as.vector()
 temp_diff_list <- map(
   seq(2012, 2020),
   function(x) weather_df_avg %>% 
@@ -114,9 +126,13 @@ ggsave(
   width = 10
 )
 
-
-
 # Daytime cumulated snow
+prefecture_order <- weather_df_avg %>% 
+  group_by(prefecture) %>% 
+  summarise_at(vars(daytime_cum_snow_m), mean, na.rm = TRUE) %>% 
+  arrange(daytime_cum_snow_m) %>% 
+  .$prefecture %>% 
+  as.vector()
 p <- weather_df_avg %>% 
   ggplot(aes(x = prefecture, y = daytime_cum_snow_m, color = factor(exam_year))) +
   geom_point() +
@@ -147,6 +163,12 @@ ggsave(
 )
 
 # Daytime snowfall
+prefecture_order <- weather_df_avg %>% 
+  group_by(prefecture) %>% 
+  summarise_at(vars(daytime_snowfall_m), mean, na.rm = TRUE) %>% 
+  arrange(daytime_snowfall_m) %>% 
+  .$prefecture %>% 
+  as.vector()
 p <- weather_df_avg %>% 
   ggplot(aes(x = prefecture, y = daytime_snowfall_m, color = factor(exam_year))) +
   geom_point() +
@@ -177,6 +199,12 @@ ggsave(
 )
 
 # Daytime rainfall
[…]

### 2021-04-23 Slides/todai_center.tex
am making slides for dev group meeting

\documentclass[9pt, pdfmx,hiresbb]{beamer}
\usepackage{natbib}
\usepackage{bbm}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{appendixnumberbeamer}
\usepackage{siunitx}
\usepackage{lipsum}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{indentfirst}
\usepackage{longtable}
\usepackage{multicol}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{graphicx}
\usepackage{setspace}

\usepackage{color}  % https://dkumor.com/posts/technical/2018/08/15/causal-tikz/
\usepackage{tikz}
\usetikzlibrary{shapes,decorations,arrows,calc,arrows.meta,fit,positioning}
\tikzset{
    -Latex,auto,node distance =1 cm and 1 cm,semithick,
    state/.style ={ellipse, draw, minimum width = 0.7 cm},
    point/.style = {circle, draw, inner sep=0.04cm,fill,node contents={}},
    bidirected/.style={Latex-Latex,dashed},
    el/.style = {inner sep=2pt, align=left, sloped}
}

\newtheorem{prop}{Proposition} 
\setbeamertemplate{thorems}[numbered]

\setbeamerfont{page number in head/foot}{size=\scriptsize}
\setbeamertemplate{footline}[frame number]

\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models$}}

\newcommand\Wider[2][3em]{
\makebox[\linewidth][c]{
  \begin{minipage}{\dimexpr\textwidth+#1\relax}
  \raggedright#2
  \end{minipage}
  }
}

%\usetheme{CambridgeUS}
\setbeamertemplate{navigation symbols}{}
\title[Temperature and Exam]{Temperature and Bureaucracy: \\ Empirical Analysis on Auditing Reports in Brazil}
\author[Suzuki]{Mizuhiro Suzuki}
\date{May 13th, 2021}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\section{Background}
\begin{frame}\frametitle{Roadmap}
  \begin{itemize}
    \item Background
    \item Data
    \item Empirical strategy
    \item Results
    \item (Some more results not in the paper for now)
  \end{itemize}
  \medskip
  \begin{itemize}
    \item Planning to submit the paper to JEEM short 
    \item Max 3,000 words (but ``modestly longer papers will be considered'')
    \item My paper now has 3,200 words
  \end{itemize}
\end{frame}

\begin{frame}\frametitle{Data}
  \begin{itemize}
    \item Weather information from Japan Meteorological Agency
      \begin{itemize}
        \item Hourly information on temperature, rainfall, snowfall, snow on the ground
        \item I use average between 6 AM to 6 PM
      \end{itemize}
    \item Matriculation for UTokyo from University Basic Information
      \begin{itemize}
        \item Information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located
        \item I calculate the matriculation shares for UTokyo from a prefecture $j$ in year $t$ as 
          \begin{equation*}
            \frac{\text{\# matriculations for UTokyo from $j$ in year $t$}}{\text{\# total matriculations for UTokyo in year $t$}}
          \end{equation*}
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}\frametitle{Summary Statistics}
  \begin{center}
    \begin{table}
      \caption{Summary Statistics}
      \footnotesize
      \input{../Output/tex/sum_stat.tex}
    \end{table}
  \end{center}
\end{frame}

\begin{frame}\frametitle{Map of matriculation shares (\%)}
  \begin{center}
    \begin{figure}
      %\caption{Map of matriculation shares (\%)}
      \includegraphics[width=7.5cm]{../Output/images/admission_map.pdf}
      \tiny
      \begin{tablenotes}
      \item Notes:
        This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
        The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
        Average of the shares across years is shown in the map.
        Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
      \end{tablenotes}
    \end{figure}
  \end{center}
\end{frame}

\begin{frame}\frametitle{Empirical Strategy}
  \begin{equation*}
    Y_{jt} = \sum_k \alpha_k T_{jt}^k + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
  \end{equation*}
  \begin{itemize}
    \item $Y_{jt}$: matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$
    \item $T_{jt}^k$: bin of average temperature across two exam dates in $j$ in year $t$
    \item $X_{jt}$: other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates
    \item $\mu_j$: prefecture fixed effects
    \item $\tau_t$: year fixed effects
    \item $\epsilon_{jt}$: error term
    \item Standard errors are clustered at the prefecture level
  \end{itemize}
\end{frame}

\begin{frame}\frametitle{Temperature variations in each prefecture}
  \begin{center}
    \begin{figure}
      %\caption{Map of matriculation shares (\%)}
      \includegraphics[width=9.5cm]{../Output/images/temperature_diff.pdf}
      \tiny
      \begin{tablenotes}
      \item Notes:
        Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
        Average across two test days in each year is shown in the figure.
        The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
      \end{tablenotes}
    \end{figure}
  \end{center}
\end{frame}

\begin{frame}\frametitle{Deviation of temperatures from within-prefecture averages}
  \begin{center}
    \begin{figure}
      %\caption{Map of matriculation shares (\%)}
      \includegraphics[width=7.5cm]{../Output/images/temperature_diff_by_year.pdf}
      \tiny
      \begin{tablenotes}
      \item Notes:
        Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
        Deviations of average temperatures across two test days from their within-prefecture means are shown in the figure by year.
        In each panel, red dots are the deviations in the year shown above and gray dots are the deviations in the other years.
        The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
      \end{tablenotes}
    \end{figure}
  \end{center}
\end{frame}

\begin{frame}\frametitle{Temperature effects on the matriculation shares (\%)}
  \begin{center}
    \begin{figure}
      \includegraphics[width=6.5cm]{../Output/images/main_reg_2.pdf}
      \tiny
      \begin{tablenotes}
      \item Notes:
        The figure shows the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
        I use temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test.
        Each interval on the x-axis does not include the right end.
        The 90\% confidence intervals are shown.
        Prefecture fixed effects and year fixed effects are also included.
        Standard errors are clustered at the prefecture level.
      \end{tablenotes}
    \end{figure}
  \end{center}
\end{frame}

\begin{frame}\frametitle{Effects of other weather variables on the matriculation shares (\%)}
    \begin{table}[h]
      \Wider[4em]{
      \center
      \fontsize{6}{8}\selectfont
      \input{../Output/tex/main_reg_beamer.tex}
      \tiny
      \begin{tablenotes}
      \item 
        The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
        The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
        I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
        Standard errors are clustered at the prefecture level.
      \end{tablenotes}
    }
    \end{table}
\end{frame}

\begin{frame}\frametitle{Placebo test (including temperature one year after the exams)}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Contemporaneous temperature
    \end{center}
    \begin{figure}[h]
      \centering
      \includegraphics[width = \textwidth]{../Output/images/reg_placebo_exam_4.pdf}
    \end{figure}
  \end{minipage}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Temperature one year later
    \end{center}
    \begin{figure}[h]
      \includegraphics[width = \textwidth]{../Output/images/reg_placebo_f1_4.pdf}
      \centering
    \end{figure}
  \end{minipage}
  \tiny
  \begin{tablenotes}
  \item Notes;
    The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
    In the left figure, the estimates on the contemporaneous temperature bins are shown.
    In the right figure, the estimates on the temperature one year later are shown.
    Rainfall and cumulated snow on the ground (both contemporaneous and one year later) are included in the regression.
    Each interval on the x-axis does not include the right end.
    The 90\% confidence intervals are shown.
    Prefecture fixed effects and year fixed effects are also included.
    Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{frame}

\begin{frame}\frametitle{Cognitive performance at the exam vs. Preparation}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Temperature at the exam dates
    \end{center}
    \begin{figure}[h]
      \centering
      \includegraphics[width = \textwidth]{../Output/images/reg_pre10_exam_4.pdf}
    \end{figure}
  \end{minipage}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Average temperature for 10 days before the exam
    \end{center}
    \begin{figure}[h]
      \includegraphics[width = \textwidth]{../Output/images/reg_pre10_pre10_4.pdf}
      \centering
    \end{figure}
  \end{minipage}
  \tiny
  \begin{tablenotes}
  \item Notes;
    The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
    In the left figure, the estimates on the temperature on the exam dates are shown.
    In the right figure, the estimates on the average temperature for 10 days before the exam are shown.
    Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
    Each interval on the x-axis does not include the right end.
    The 90\% confidence intervals are shown.
    Prefecture fixed effects and year fixed effects are also included.
    Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{frame}

\begin{frame}\frametitle{Effects of other weather variables on the matriculation shares (\%)}
  \begin{table}[h]
    \Wider[4em]{
    \center
    \fontsize{6}{7}\selectfont
    \input{../Output/tex/reg_pre10_beamer.tex}
    \tiny
    \begin{tablenotes}
    \item 
      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      Standard errors are clustered at the prefecture level.
    \end{tablenotes}
  }
  \end{table}
\end{frame}

\begin{frame}\frametitle{Female vs. Male}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Female \\
      (mean: 0.38 \%, median: 0.13 \%)
    \end{center}
    \begin{figure}[h]
      \centering
      \includegraphics[width = \textwidth]{../Output/images/reg_gender_2.pdf}
    \end{figure}
  \end{minipage}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Male \\
      (mean: 1.70 \%, median: 0.61 \%)
    \end{center}
    \begin{figure}[h]
      \includegraphics[width = \textwidth]{../Output/images/reg_gender_4.pdf}
      \centering
    \end{figure}
  \end{minipage}
  \tiny
  \begin{tablenotes}
  \item Notes;
    The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
    In the left figure, the outcome is the matriculation share of female students from each prefecture.
    In the right figure, the outcome is the matriculation share of male students from each prefecture.
    Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
    Each interval on the x-axis does not include the right end.
    The 90\% confidence intervals are shown.
    Prefecture fixed effects and year fixed effects are also included.
    Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{frame}

%\begin{frame}\frametitle{Humanity vs. Science}
%  \begin{minipage}{0.49\textwidth}
%    \begin{center}
%      Humanity \\
%      (mean: 2.07 \%, median: 0.76 \%)
%    \end{center}
%    \begin{figure}[h]
%      \centering
%      \includegraphics[width = \textwidth]{../Output/images/reg_major_2.pdf}
%    \end{figure}
%  \end{minipage}
%  \begin{minipage}{0.49\textwidth}
%    \begin{center}
%      Science \\
%      (mean: 2.09 \%, median: 0.76 \%)
%    \end{center}
%    \begin{figure}[h]
%      \includegraphics[width = \textwidth]{../Output/images/reg_major_4.pdf}
%      \centering
%    \end{figure}
%  \end{minipage}
%  \tiny
%  \begin{tablenotes}
%  \item Notes;
%    The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
%    In the left figure, the outcome is the matriculation share to humanity major from each prefecture.
%    In the right figure, the outcome is the matriculation share to science major from each prefecture.
%    Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
%    Each interval on the x-axis does not include the right end.
%    The 90\% confidence intervals are shown.
%    Prefecture fixed effects and year fixed effects are also included.
%    Standard errors are clustered at the prefecture level.
%  \end{tablenotes}
%\end{frame}

\end{document}

### 2021-04-23 Codes/R/Regression/main_regression.R

@@ -123,7 +123,6 @@ list(res_4, res_6, res_8) %>%
   )
 
 # Non-linear regression figures ============
-
 walk2(
   list(res_2, res_4, res_6, res_8),
   c(2, 4, 6, 8), 

### 2021-04-23 Codes/R/Regression/pre10_regression.R

@@ -98,12 +98,12 @@ list(res_1, res_2, res_3, res_4) %>%
     ),
     title = "",
     add.lines = list(
-      c("Temperature bins", rep("Yes", 3)),
-      c("Prefecture FE", rep("Yes", 3)),
-      c("Year FE", rep("Yes", 3))
+      c("Temperature bins", rep("Yes", 4)),
+      c("Prefecture FE", rep("Yes", 4)),
+      c("Year FE", rep("Yes", 4))
     ),
     type = "latex",
-    out = file.path(git_dir, "Output/tex/res_pre10_beamer.tex"),
+    out = file.path(git_dir, "Output/tex/reg_pre10_beamer.tex"),
     omit.stat = c("adj.rsq", "ser", "rsq"),
     digits = 2,
     float = FALSE

### 2021-04-23 Codes/R/SumStat/admission_map.R

@@ -48,8 +48,8 @@ map@data$ADM1_JA <- str_replace(map@data$ADM1_JA, "東京都", "東京")
 
 map_avg <- merge(map, admission_df_avg, by.x = "ADM1_JA", by.y = "prefecture")
 
-filepath = file.path(git_dir, 'Output/images/admission_map.png')
-png(file = filepath)
+filepath = file.path(git_dir, 'Output/images/admission_map.pdf')
+pdf(file = filepath)
 print(
   spplot(
     map_avg, 
@@ -72,8 +72,4 @@ print(
   )
 )
 dev.off()
-
-admission_df_avg %>% 
-  arrange(desc(admission_total_share)) %>% 
-  mutate(cum_admission = cumsum(admission_total_share))
 

### 2021-04-23 Codes/R/SumStat/sumstat.R

@@ -39,8 +39,8 @@ reg_df <- left_join(
 list(
   function(x) sum(!is.na(x)), 
   mean, sd, median, min, max
-) %>% 
-map(
+  ) %>% 
+  map(
   function(x) 
     reg_df %>% 
     dplyr::select(
@@ -78,4 +78,17 @@ map(
   ) %>% 
   save_kable(file.path(git_dir, "Output/tex/sum_stat.tex"))
 
-
+list(
+  function(x) sum(!is.na(x)), 
+  mean, sd, median, min, max
+  ) %>% 
+  map(
+  function(x) 
+    reg_df %>% 
+    dplyr::select(
+      admission_Arts_share,
+      admission_Sciences_share,
+      ) %>% 
+    summarise_all(x)
+  ) %>% 
+  bind_rows() 

### 2021-05-04 Writeups/paper.tex
am making slides for dev group meeting
fixed the first paragraph of intro & put linear specification into the appendix

@@
 Any errors in this draft are the sole responsibility of the author.}}
-\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison.
+\author{
+  Mizuhiro Suzuki\thanks{
+    Department of Agricultural and Applied Economics, University of Wisconsin-Madison.
     Contact: msuzuki7@wisc.edu.
-The authors would like to thank Laura Schechter for her numerous feedback and support.}}
+    The author would like to thank Laura Schechter for her numerous feedback and support.
+    I am also grateful to Daiji Kawaguchi for helpful comments and suggestions.
+    Any errors are the sole responsibility of the author.
+  }
+}
 \date{\today \\ \vspace{1cm} Preliminary draft \\ Please do not cite or circulate}
@@
 
-Climate change is expected to increase the frequency of extreme weather events.
-This is considered to have not only macro-level impacts but also micro-level impacts such as individual behaviors.
-To understand the effect, emerging literature has studied effects of high temperature on various outcomes.\footnote{
-  Examples include \citet{Dell2012, Burke2015, Heyes2019, Garg2020, Geruso2018, Park2020a, Park2020b, GraffZivi2018, GraffZivin2014}.
-  \citet{Carleton2016} thoroughly review this literature.
+University admission is an important step in life and can have consequences in later-life outcomes such as job occupation and earnings.\footnote{
+  \citet{Hout2012} reviews the returns to college education in the context of the United States.
 }
-What has been less studied in the literature is the economic impact of \textit{low} temperature.
-Given the possibility that the sea-ice loss, partly due to climate change, results in cold winters with severely low temperatures \citep{Kretschmer2016, Kim2014}, it is important to understand how low temperature can affect our economies and lives.
+For admission selection, standardized exams have been widely used in many countries.\footnote{
+  Examples include the Unites States, the United Kingdom, Brazil, China, South Korea, and Japan.
+}
+Given the importance, the results of the exams are expected to evaluate the exam takers' ability and knowledge correctly and are not supposed to be affected by seemingly irrelevant factors.
+However, recent studies have shown that exam performance is sensitive to external factors.
+One such factor is temperature:
+heat on the exam days has been shown to affect exam results in high-stakes settings \citep{Park2020a, GraffZivin2020}.
+What has been less studied in the literature is the impact of \textit{low} temperature.\footnote{
+  One might think that, considering the on-going global \textit{warming}, the effect of low temperature is becoming less important.
+  However, the future climate change can cause the sea-ice loss, would could result in the cold winters with severely low temperatures \citep{Kretschmer2016, Kim2014}.
+  Hence, it is important to understand how low temperature can affect our economies and lives.
+}
 
-This study analyzes the effect of winter weather on exam outcomes in Japan.
+To fill this gap in the literature, this study analyzes the effect of winter weather on exam outcomes in Japan.
 For admission, most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth).
@@
   \caption{Map of matriculation shares (\%)}
-  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}
+  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.pdf}
   \label{fig:admission_map}
@@
 In the analyses, the outcome variable, $Y_{jt}$, is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
-Let $T_{jt}$ be the average temperature across two exam dates in $j$ in year $t$.
-I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
-I include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates as a vector $X_{jt}$.
+%Let $T_{jt}$ be the average temperature across two exam dates in $j$ in year $t$.
+%I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
+The main right-hand side variable is temperature on the exam dates.
+To allow for non-linear effects of temperature on the outcome, I use the 3-$^o$C temperature intervals, $T_{jt}^k$.\footnote{
+  The results with a linear specification are shown in Appendix \ref{sec:appendix_table} and will be discussed below.
+}
+I also include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates as a vector $X_{jt}$.
 As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
@@
 
-I run the following regression equation:
+Given the above notation, I run the following regression equation:
 \begin{equation*}
-  Y_{jt} = f(T_{jt}) + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
+  Y_{jt} = \sum_k T_{jt}^k + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
 \end{equation*}
@@
 }$^,$\footnote{
-  The figure shows that temperature is low for most prefectures in some years (eg. 2017) and is high in other years (eg. 2019).
+  The figure shows that temperature is low for most prefectures in some years (eg. 2017) and high in other years (eg. 2019).
   This can bring up a concern that temperature \textit{deviations} from the prefecture average have limited variations within each year.
@@
 In 2020, 38\% of the admitted students are high-school graduates.
-Moreover, in the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
+In the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
 Hence, if I use this number as an approximation for the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of students whose exam-date weather is measured with errors for the reason above as $0.38 * 0.039 = 1.5\%$.
@@
       Average across two test days in each year is shown in the figure.
-      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
+      The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
   \end{tablenotes}
@@
 The standard errors are clustered at the prefecture level.
-Column (1) shows the result with a linear specification.
-While the point estimate is positive, which means matriculation shares are higher if an exam is held on warmer days, it is statistically insignificant. 
-The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impact of cold weather. 
+Without other weather variables, the estimates in column (1) show a negative and statistically significant impact of cold weather.
 Since the mean matriculation share is $2.08$\%, by reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest temperature bin (below 0 $^o$C), the matriculation share decreases by 9\%.
@@
 Therefore, the same temperature change decreases the matriculation share by 22\% of the median value.
-Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in column (1) could not capture the non-linear effect of temperature and the estimate is statistically insignificant.
+
+In column (2), I add rainfall and snowfall in the regressions.
+While temperature coefficients are barely affected, I find that rainfall and snowfall on the exam dates do not impact the matriculation shares.
+In column (3), instead of snowfall on the exam dates, I use cumulated snow on the ground and find its negative impact on the outcome. 
+To capture the effect of the existence of a certain amount of snow on the ground, column (4) allows a non-linear effect of cumulated snow.
+The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage point.\footnote{
+  Table \ref{tab:linear_reg} shows the result with linear specifications.
+  While the point estimates for temperature are positive, which means matriculation shares are higher if an exam is held on warmer days, they are statistically insignificant. 
+  This could due to the plateau effect of temperature above 6 $^o$C in Table \ref{tab:main_reg}.
   Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.
-
-In columns (3) and (4), I add rainfall and snowfall in the regressions.
-While temperature coefficients are barely affected, I find that rainfall and snowfall on the exam dates do not impact the matriculation shares.
-In columns (5) and (6), instead of snowfall on the exam dates, I use cumulated snow on the ground and find its negative impact on the outcome. 
-To capture the effect of the existence of a certain amount of snow on the ground, columns (7) and (8) allow a non-linear effect of cumulated snow.
-The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage point.\footnote{
+}$^,$\footnote{
   Following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual Center Test affect the matriculation shares.
@@
       I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      Temperature intervals do not contain the right ends.
       Standard errors are clustered at the prefecture level.
@@
 In other words, the effects found in Table \ref{tab:main_reg} could be interpreted as the effects on preparation for the exam. 
-For instance, cold weather can make it hard for students to focus on studying, suggested by existing studies \citep{Taylor2016}.
+For instance, cold weather can make it hard for students to focus on studying, as suggested by existing studies \citep{Taylor2016}.
 Also, snowfall can prevent students from going to high schools or cram schools for studying.
@@
       For weather variables with "(previous 10 days)", I use their averages at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
+      Temperature intervals do not contain the right ends.
       Standard errors are clustered at the prefecture level.
@@
 
+\section{Appendix tables}\label{sec:appendix_table}
+
+%\begin{table}[H]
+%  \center
+%  \caption{Regression: Matriculation share (\%) and weather on exam dates by gender}
+%  \input{"../Output/tex/reg_by_gender.tex"}
+%  \label{tab:reg_by_gender}
+%  \small
+%  \begin{tablenotes}
+%    \item
+%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+%      Standard errors are clustered at the prefecture level.
+%  \end{tablenotes}
+%\end{table}
+
+\begin{table}[H]
+  \center
+  \caption{Regression: Matriculation share (\%) and weather on exam dates (linear specification)}
+  \small
+  \input{"../Output/tex/linear_reg.tex"}
+  \label{tab:linear_reg}
+  \small
+  \begin{tablenotes}
+    \item
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{table}
+
+\begin{table}[H]
+  \center
+  \caption{Falsification test: Matriculation share (\%) and weather on exam dates and one year after}
+  \scriptsize
+  \input{"../Output/tex/reg_placebo_exam.tex"}
+  \label{tab:reg_placebo_exam}
+  \scriptsize
+  \begin{tablenotes}
+    \item
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      I represent the contemporaneous weather variables with ``($t$)'' and the weather one year after Center Test with ``($t + 1$).''
+      Temperature intervals do not contain the right ends.
+      Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{table}
+
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\renewcommand\thefigure{\Alph{section}.\arabic{figure}}
+\renewcommand\thetable{\Alph{section}.\arabic{table}}
+
 \section{Appendix figures}\label{sec:appendix_figure}
@@
 
-\setcounter{figure}{0}
-\setcounter{table}{0}
-\renewcommand\thefigure{\Alph{section}.\arabic{figure}}
-\renewcommand\thetable{\Alph{section}.\arabic{table}}
-
-\section{Appendix tables}
-
-%\begin{table}[H]
-%  \center
-%  \caption{Regression: Matriculation share (\%) and weather on exam dates by gender}
-%  \input{"../Output/tex/reg_by_gender.tex"}
-%  \label{tab:reg_by_gender}
-%  \small
-%  \begin{tablenotes}
-%    \item
-%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-%      Standard errors are clustered at the prefecture level.
-%  \end{tablenotes}
-%\end{table}
-
-\begin{table}[H]
-  \center
-  \caption{Falsification test: Matriculation share (\%) and weather on exam dates and one year after}
-  \scriptsize
-  \input{"../Output/tex/reg_placebo_exam.tex"}
-  \label{tab:reg_placebo_exam}
-  \scriptsize
-  \begin{tablenotes}
-    \item
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-      I represent the contemporaneous weather variables with ``($t$)'' and the weather one year after Center Test with ``($t + 1$).''
-      Standard errors are clustered at the prefecture level.
-  \end{tablenotes}
-\end{table}
-
 \end{document}

### 2021-05-04 Codes/R/Regression/linear_regression.R

@@ -1,0 +1,70 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer",
+  "latex2exp"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load regression data =================
+reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
+
+# Import function to make estimate figures
+source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
+
+# Regression with linear specification ==========================
+
+res_1 <- felm(
+  admission_total_share ~ daytime_temperature_degree | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_2 <- felm(
+  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_snowfall_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_3 <- felm(
+  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_cum_snow_m | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_4 <- felm(
+  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + factor(daytime_cum_snow_m > .1) | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+list(res_1, res_2, res_3, res_4) %>% 
+  stargazer(
+    dep.var.labels = "Matriculation share (\\%)",
+    covariate.labels = c(
+      "Temperature (\\degree C)",
+      "Rainfall (mm)",
+      "Snowfall (m)",
+      "Cumulated snow (m)",
+      "Cumulated snow $>$ .10 m"
+    ),
+    title = "",
+    add.lines = list(
+      c("Prefecture FE", rep("Yes", 8)),
+      c("Year FE", rep("Yes", 8))
+    ),
+    type = "latex",
+    out = file.path(git_dir, "Output/tex/linear_reg.tex"),
+    omit.stat = c("adj.rsq", "ser", "rsq"),
+    digits = 2,
+    float = FALSE
+  )
+

### 2021-05-04 Codes/R/Regression/main_regression.R

@@ -23,61 +23,36 @@ source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
 # Main regression ==========================
 
 res_1 <- felm(
-  admission_total_share ~ daytime_temperature_degree | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_2 <- felm(
   admission_total_share ~ temp_cut | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
   )
 
-res_3 <- felm(
-  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_snowfall_m | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_4 <- felm(
+res_2 <- felm(
   admission_total_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
 
-res_5 <- felm(
-  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_cum_snow_m | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_6 <- felm(
+res_3 <- felm(
   admission_total_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
 
-res_7 <- felm(
-  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + factor(daytime_cum_snow_m > .1) | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_8 <- felm(
+res_4 <- felm(
   admission_total_share ~ temp_cut + daytime_precipitation_mm + factor(daytime_cum_snow_m > .1) | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
 
-list(res_1, res_2, res_3, res_4, res_5, res_6, res_7, res_8) %>% 
+list(res_1, res_2, res_3, res_4) %>% 
   stargazer(
     dep.var.labels = "Matriculation share (\\%)",
     covariate.labels = c(
-      "Temperature (\\degree C)",
       "Temperature (\\degree C) $\\le$ 0",
[…]

### 2021-05-04 Codes/R/Regression/placebo_regression.R

@@ -55,15 +55,15 @@ list(res_1, res_2, res_3, res_4) %>%
     order = c(seq(1, 4), seq(5, 7), seq(8, 11), seq(12, 14)),
     covariate.labels = c(
       "Temperature (\\degree C) $\\le$ 0 ($t$)",
-      "Temperature (\\degree C) $>$ 0, $\\le$ 3 ($t$)",
-      "Temperature (\\degree C) $>$ 6, $\\le$ 9 ($t$)",
+      "Temperature (\\degree C) 0-3 ($t$)",
+      "Temperature (\\degree C) 6-9 ($t$)",
       "Temperature (\\degree C) $>$ 9 ($t$)",
       "Rainfall (mm) ($t$)",
       "Snowfall (m) ($t$)",
       "Cumulated snow (m) ($t$)",
       "Temperature (\\degree C) $\\le$ 0 ($t + 1$)",
-      "Temperature (\\degree C) $>$ 0, $\\le$ 3 ($t + 1$)",
-      "Temperature (\\degree C) $>$ 6, $\\le$ 9 ($t + 1$)",
+      "Temperature (\\degree C) 0-3 ($t + 1$)",
+      "Temperature (\\degree C) 6-9 ($t + 1$)",
       "Temperature (\\degree C) $>$ 9 ($t + 1$)",
       "Rainfall (mm) ($t + 1$)",
       "Snowfall (m) ($t + 1$)",

### 2021-05-04 Codes/R/Regression/pre10_regression.R

@@ -55,15 +55,15 @@ list(res_1, res_2, res_3, res_4) %>%
     order = c(seq(1, 4), seq(5, 7), seq(8, 11), seq(12, 14)),
     covariate.labels = c(
       "Temperature (\\degree C) $\\le$ 0 (exam dates)",
-      "Temperature (\\degree C) $>$ 0, $\\le$ 3 (exam dates)",
-      "Temperature (\\degree C) $>$ 6, $\\le$ 9 (exam dates)",
+      "Temperature (\\degree C) 0-3 (exam dates)",
+      "Temperature (\\degree C) 6-9 (exam dates)",
       "Temperature (\\degree C) $>$ 9 (exam dates)",
       "Rainfall (mm) (exam dates)",
       "Snowfall (m) (exam dates)",
       "Cumulated snow (m) (exam dates)",
       "Temperature (\\degree C) $\\le$ 0 (previous 10 days)",
-      "Temperature (\\degree C) $>$ 0, $\\le$ 3 (previous 10 days)",
-      "Temperature (\\degree C) $>$ 6, $\\le$ 9 (previous 10 days)",
+      "Temperature (\\degree C) 0-3 (previous 10 days)",
+      "Temperature (\\degree C) 6-9 (previous 10 days)",
       "Temperature (\\degree C) $>$ 9 (previous 10 days)",
       "Rainfall (mm) (previous 10 days)",
       "Snowfall (m) (previous 10 days)",

### 2021-05-04 Codes/R/Regression/regression.R

@@ -16,80 +16,6 @@ git_dir <- "~/Documents/GitHub/todai_center/"
 # Load regression data =================
 reg_df <- read_csv(file.path(dropbox_dir, "Data/temp/data_regression.csv"))
 
-reg_df %>% 
-  mutate(
-    # temp_cut = cut(daytime_temperature_degree, c(-10, 1, 3, 5, 7, 25)),
-    temp_cut = cut(daytime_temperature_degree, c(-10, 0, 3, 6, 9, 25)),
-    temp_cut_morning = cut(morning_temperature_degree, c(-10, -2, 0, 2, 4, 6, 25)),
-    temp_cut_exam = cut(exam_temperature_degree, c(-10, 0, 3, 6, 9, 25)),
-    l1_temp_cut = cut(l1_temperature_degree, c(-10, 0, 2, 4, 6, 8, 25)),
-    f1_temp_cut = cut(f1_temperature_degree, c(-10, 0, 2, 4, 6, 8, 25))
-    # temp_cut = relevel(as.factor(temp_cut), ref = 3),
-    ) %>%
-  # filter(year <= 2018) %>%
-  # select(year, temp_cut) %>%
-  # select(temp_cut) %>%
-  # select(year, f1_temp_cut) %>%
-  # select(f1_temp_cut) %>%
-  # select(year, l1_temp_cut) %>%
-  # select(l1_temp_cut) %>%
-  # select(year, temp_cut_morning) %>%
-  # select(temp_cut_morning) %>%
-  select(year, temp_cut_exam) %>%
-  select(temp_cut_exam) %>%
-  table()
-
-felm(
-  admission_total_share ~ 
-    temp_cut |
-    prefecture + year | 0 | prefecture, 
-  data = reg_df %>% 
-    mutate(
-      temp_cut = cut(daytime_temperature_degree, c(-10, 0, 3, 6, 9, 25)),
-      temp_cut = cut(daytime_temperature_degree, c(-10, 0, 2, 4, 6, 8, 25)),
-      temp_cut = relevel(temp_cut, ref = 3),
-      temp_cut_morning = cut(morning_temperature_degree, c(-10, -2, 0, 2, 4, 6, 25)),
-      temp_cut_exam = cut(exam_temperature_degree, c(-10, 0, 2, 4, 6, 25)),
-    )
-  ) %>% summary
-
-felm(
-  admission_total_share ~ 
-    temp_cut |
-    prefecture + year | 0 | prefecture, 
-  data = reg_df %>% 
-    mutate(
[…]

### 2021-05-04 Codes/R/SumStat/sumstat.R

@@ -78,17 +78,18 @@ list(
   ) %>% 
   save_kable(file.path(git_dir, "Output/tex/sum_stat.tex"))
 
-list(
-  function(x) sum(!is.na(x)), 
-  mean, sd, median, min, max
-  ) %>% 
-  map(
-  function(x) 
-    reg_df %>% 
-    dplyr::select(
-      admission_Arts_share,
-      admission_Sciences_share,
-      ) %>% 
-    summarise_all(x)
-  ) %>% 
-  bind_rows() 
+# list(
+#   function(x) sum(!is.na(x)), 
+#   mean, sd, median, min, max
+#   ) %>% 
+#   map(
+#   function(x) 
+#     reg_df %>% 
+#     dplyr::select(
+#       admission_Arts_share,
+#       admission_Sciences_share,
+#       ) %>% 
+#     summarise_all(x)
+#   ) %>% 
+#   bind_rows() 
+

### 2021-05-04 Writeups/paper.tex
revised the paper after proofreading

@@
   One might think that, considering the on-going global \textit{warming}, the effect of low temperature is becoming less important.
-  However, the future climate change can cause the sea-ice loss, would could result in the cold winters with severely low temperatures \citep{Kretschmer2016, Kim2014}.
+  However, the future climate change can cause the sea-ice loss, which could result in the cold winters with severely low temperatures \citep{Kretschmer2016, Kim2014}.
   Hence, it is important to understand how low temperature can affect our economies and lives.
@@
 One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take Center Test in the same municipality.
-This means that, for these students, the weather at the exam sites is measured with errors.
+This means that, for such students, the weather at the exam sites is measured with errors.
 The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get into any university and retake Center Test next year in his home prefecture.
@@
 To capture the effect of the existence of a certain amount of snow on the ground, column (4) allows a non-linear effect of cumulated snow.
-The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage point.\footnote{
-  Table \ref{tab:linear_reg} shows the result with linear specifications.
+The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage point.
+These results suggest that not only temperature but also snow on the ground on the exam dates affect exam performance.
+
+Two points are worth noting.
+First, Table \ref{tab:linear_reg} shows the results with linear specifications.
 While the point estimates for temperature are positive, which means matriculation shares are higher if an exam is held on warmer days, they are statistically insignificant. 
@@
 Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.
-}$^,$\footnote{
-  Following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual Center Test affect the matriculation shares.
+Secondly, following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual Center Test affect the matriculation shares.
 The results in Table \ref{tab:reg_placebo_exam} show not only that the weather one year after Center Test has insignificant impacts on matriculation shares but also including the weather variables one year after Center Test barely changes the coefficients on contemporaneous weather variables.
-}
+This indicates that the results in \ref{tab:main_reg} capture the effect of transitory shocks on the exam dates.
 
@@
 
-One possible interpretation of the results is that the temperature on exam dates captures the weather before the exam due to the serial correlation.
-In other words, the effects found in Table \ref{tab:main_reg} could be interpreted as the effects on preparation for the exam. 
+One possible interpretation of the results is that the estimates in Table \ref{tab:main_reg} reflect the effects of weather on preparation for the exam.
 For instance, cold weather can make it hard for students to focus on studying, as suggested by existing studies \citep{Taylor2016}.
 Also, snowfall can prevent students from going to high schools or cram schools for studying.
+Due to serial correlation between the weather on exam dates and the weather days or weeks before the exam, my regression in Table \ref{tab:main_reg} could capture these effects.
 To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
@@
 This paper studies the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
-I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
+I use the matriculation share for the most prestigious university in Japan, the University of Tokyo, as an outcome.
 Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
-This study fills the gap and identifies the causal impact of winter weather on matriculation.
+This study fills the gap by identifying the causal impact of winter weather on exam results.
 

### 2021-05-11 Slides/todai_center.tex
Made slides for dev group meeting on May 13th, 2021

@@
-\documentclass[9pt, pdfmx,hiresbb]{beamer}
+\documentclass[10pt, pdfmx,hiresbb]{beamer}
+\usetheme{metropolis}
 \usepackage{natbib}
@@
 \setbeamertemplate{navigation symbols}{}
-\title[Temperature and Exam]{Temperature and Bureaucracy: \\ Empirical Analysis on Auditing Reports in Brazil}
+\title[Temperature and Exam]{Winter weather on exam dates and matriculation for a prestigious university in Japan}
 \author[Suzuki]{Mizuhiro Suzuki}
@@
 
-\section{Background}
-\begin{frame}\frametitle{Roadmap}
+\begin{frame}\frametitle{Research Question \& Roadmap}
+  \begin{itemize}
+    \item Research Question: Does cold weather on the exam dates worsens performance at a high-stakes exam?
+    \item Roadmap:
       \begin{itemize}
@@
       \end{itemize}
-  \medskip
+    \item A quick heads-up\dots
       \begin{itemize}
@@
       \end{itemize}
+  \end{itemize}
 \end{frame}
+
+\begin{frame}\frametitle{Background - Center Test}
+  \begin{itemize}
+    \item In Japan, for public university admission, students need to take two exams:
+    \item First-stage: \textcolor{red}{Center Test}
+      \begin{itemize}
+        \item Held in mid-January (Saturday and Sunday)
+          \begin{itemize}
+            \item Social science, Japanese, and English on the first day (9:30 AM - 6:10 PM)
+            \item Mathematics and natural science on the second day (9:30 AM - 5:50 PM)
+          \end{itemize}
+        \item Questions are multiple-choice and common for all exam takers
+        \item Students take the exam in their own prefectures
+      \end{itemize}
+    \item Second-stage: University-specific exams
+      \begin{itemize}
+        \item Typically held in late February
+        \item Students take the exams at universities they apply for
+      \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Background - Admission for the University of Tokyo}
+  \begin{itemize}
+    \item The University of Tokyo (UTokyo) is the most prestigious university in Japan
+      \begin{itemize}
+        \item Highest-ranked univ. in Japan (73rd ranked in the world ranking) (U.S. News) \\
+          (The second highest-ranked univ. is Kyoto University, 125th ranked in the world ranking)
+        \item Kawaguchi and Ma (2008): ``The University of Tokyo has occupied the top position of the single-peaked university hierarchy since its establishment in 1877.''
+      \end{itemize}
+    \item Center Test scores for admission to UTokyo:
+      \begin{itemize}
+        \item Used for eligibility to take the second-stage exam
+          %Thresholds varying across years and majors are set, and if scores at Center Test are below the thresholds, the students cannot take the second-stage exam.
+        \item Taken into consideration for final admission 
+          \begin{itemize}
+            \item The final score of a student is the weighted sum of exam scores at the first- (20\%) and second-stage (80\%) exams
+          \end{itemize}
+      \end{itemize}
+  \end{itemize}
+\end{frame}
+
+%\begin{frame}\frametitle{Background - Winter weather and exam performance}
+%  \begin{itemize}
+%    \item 
+%  \end{itemize}
+%\end{frame}
 
@@
         \item Information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located
+          \begin{itemize}
+            \item By gender (male vs. female)
+            \item By major (humanity vs. science)
+          \end{itemize}
         \item I calculate the matriculation shares for UTokyo from a prefecture $j$ in year $t$ as 
@@
       \input{../Output/tex/sum_stat.tex}
+      \tiny
+      \begin{tablenotes}
+        \item 
+          Notes:
+          Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
+          The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+          I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      \end{tablenotes}
     \end{table}
@@
       %\caption{Map of matriculation shares (\%)}
-      \includegraphics[width=7.5cm]{../Output/images/admission_map.pdf}
+      \includegraphics[width=7cm]{../Output/images/admission_map.pdf}
       \tiny
@@
 
-\begin{frame}\frametitle{Empirical Strategy}
+\begin{frame}\frametitle{Empirical Strategy - Why UTokyo?}
+  \begin{itemize}
+    \item Suppose that low temperature negatively affects exam performance
+    \item If I consider a matriculation for a middle-ranked university,
+      \begin{enumerate}
+        \item students in the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
+        \item students in the prefecture who would get into a higher-ranked university may get into the middle-ranked university
+      \end{enumerate}
+    \item Considering the matriculation for UTokyo (= the most prestigious university in Japan) rules out the second possibility
+  \end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Empirical Strategy - Estimation equation}
+  \label{est_eq}
   \begin{equation*}
@@
   \end{itemize}
-\end{frame}
-
-\begin{frame}\frametitle{Temperature variations in each prefecture}
-  \begin{center}
-    \begin{figure}
-      %\caption{Map of matriculation shares (\%)}
-      \includegraphics[width=9.5cm]{../Output/images/temperature_diff.pdf}
-      \tiny
-      \begin{tablenotes}
-      \item Notes:
-        Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
-        Average across two test days in each year is shown in the figure.
-        The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
-      \end{tablenotes}
-    \end{figure}
-  \end{center}
-\end{frame}
-
-\begin{frame}\frametitle{Deviation of temperatures from within-prefecture averages}
-  \begin{center}
-    \begin{figure}
-      %\caption{Map of matriculation shares (\%)}
-      \includegraphics[width=7.5cm]{../Output/images/temperature_diff_by_year.pdf}
-      \tiny
-      \begin{tablenotes}
-      \item Notes:
-        Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
-        Deviations of average temperatures across two test days from their within-prefecture means are shown in the figure by year.
-        In each panel, red dots are the deviations in the year shown above and gray dots are the deviations in the other years.
-        The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
-      \end{tablenotes}
-    \end{figure}
-  \end{center}
+  \hyperlink{temp_dev_1}{\beamergotobutton{Temperature variation}}
+  \hyperlink{temp_dev_2}{\beamergotobutton{Within-prefecture temperature variation}}
 \end{frame}
@@
       \center
-      \fontsize{6}{8}\selectfont
+      \fontsize{6}{7}\selectfont
       \input{../Output/tex/main_reg_beamer.tex}
@@
     \center
-    \fontsize{6}{7}\selectfont
+    \fontsize{7}{5}\selectfont
     \input{../Output/tex/reg_pre10_beamer.tex}
@@
 
-\begin{frame}\frametitle{Female vs. Male}
+\begin{frame}\frametitle{Some additional analysis: Female vs. Male}
   \begin{minipage}{0.49\textwidth}
@@
 
-%\begin{frame}\frametitle{Humanity vs. Science}
-%  \begin{minipage}{0.49\textwidth}
-%    \begin{center}
-%      Humanity \\
-%      (mean: 2.07 \%, median: 0.76 \%)
-%    \end{center}
-%    \begin{figure}[h]
-%      \centering
-%      \includegraphics[width = \textwidth]{../Output/images/reg_major_2.pdf}
-%    \end{figure}
-%  \end{minipage}
-%  \begin{minipage}{0.49\textwidth}
-%    \begin{center}
-%      Science \\
-%      (mean: 2.09 \%, median: 0.76 \%)
-%    \end{center}
-%    \begin{figure}[h]
-%      \includegraphics[width = \textwidth]{../Output/images/reg_major_4.pdf}
-%      \centering
-%    \end{figure}
-%  \end{minipage}
-%  \tiny
-%  \begin{tablenotes}
-%  \item Notes;
-%    The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
-%    In the left figure, the outcome is the matriculation share to humanity major from each prefecture.
-%    In the right figure, the outcome is the matriculation share to science major from each prefecture.
-%    Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
-%    Each interval on the x-axis does not include the right end.
-%    The 90\% confidence intervals are shown.
-%    Prefecture fixed effects and year fixed effects are also included.
-%    Standard errors are clustered at the prefecture level.
-%  \end{tablenotes}
-%\end{frame}
+\begin{frame}\frametitle{Some additional analysis: Humanity vs. Science}
+  \begin{minipage}{0.49\textwidth}
+    \begin{center}
+      Humanity \\
+      (mean: 2.07 \%, median: 0.76 \%)
+    \end{center}
+    \begin{figure}[h]
+      \centering
+      \includegraphics[width = \textwidth]{../Output/images/reg_major_2.pdf}
+    \end{figure}
+  \end{minipage}
+  \begin{minipage}{0.49\textwidth}
+    \begin{center}
+      Science \\
+      (mean: 2.09 \%, median: 0.76 \%)
+    \end{center}
+    \begin{figure}[h]
+      \includegraphics[width = \textwidth]{../Output/images/reg_major_4.pdf}
+      \centering
+    \end{figure}
+  \end{minipage}
+  \tiny
+  \begin{tablenotes}
+  \item Notes;
+    The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
+    In the left figure, the outcome is the matriculation share to humanity major from each prefecture.
+    In the right figure, the outcome is the matriculation share to science major from each prefecture.
+    Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
+    Each interval on the x-axis does not include the right end.
+    The 90\% confidence intervals are shown.
+    Prefecture fixed effects and year fixed effects are also included.
+    Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{frame}
+
+\begin{frame}\frametitle{Conclusion}
+  \begin{itemize}
+    \item Weather on the exam dates affects the matriculations for UTokyo
+      \begin{itemize}
+        \item Reducing temperature from 3-6 \degree C to $<$0 \degree C decreases the probability of matriculation by 0.18 percentage point \\
+          (9\% of the average and 22\% of the median matriculation shares)
+        \item Snow on the ground cumulated more than 10cm decreases the probability of matriculation by 0.11 percentage point \\
+          (5\% of the average and 13\% of the median matriculation shares)
+      \end{itemize}
+    \item Suggests that the exam performance is negatively affected by winter weather
+    \item Implications for university admission process:
+      \begin{itemize}
+        \item Use other information such as extracurricular activities and personal statements for university admission?
+        \item Adjust weights for Center Test and the second-stage exam?
+      \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\appendix
+
+\begin{frame}\frametitle{Temperature variations in each prefecture}
+  \label{temp_dev_1}
+  \begin{center}
+    \begin{figure}
+      %\caption{Map of matriculation shares (\%)}
+      \includegraphics[width=9.5cm]{../Output/images/temperature_diff.pdf}
+      \tiny
+      \begin{tablenotes}
+      \item Notes:
+        Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
+        Average across two test days in each year is shown in the figure.
+        The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
+      \end{tablenotes}
+    \end{figure}
+  \end{center}
+  \hyperlink{est_eq}{\beamergotobutton{Estimation equation}}
+\end{frame}
+
+\begin{frame}\frametitle{Deviation of temperatures from within-prefecture averages}
+  \label{temp_dev_2}
+  \begin{center}
+    \begin{figure}
+      %\caption{Map of matriculation shares (\%)}
+      \includegraphics[width=6.6cm]{../Output/images/temperature_diff_by_year.pdf}
+      \tiny
+      \begin{tablenotes}
+      \item Notes:
+        Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
+        Deviations of average temperatures across two test days from their within-prefecture means are shown in the figure by year.
+        In each panel, red dots are the deviations in the year shown above and gray dots are the deviations in the other years.
+        The prefectures are ordered by the mean temperature across years (lowest to left and highest to right). \\
+      \item 
+        \hyperlink{est_eq}{\beamergotobutton{Estimation equation}}
+      \end{tablenotes}
+    \end{figure}
+  \end{center}
+\end{frame}
 

### 2021-05-11 Writeups/paper.tex
Made slides for dev group meeting on May 13th, 2021

@@
 Students take an exam on consecutive two days (Saturday and Sunday) in mid-January.
-Most public universities, including UTokyo, require students to take exams on social science, language, and English on the first day and mathematics and natural science on the second day.
+Most public universities, including UTokyo, require students to take exams on social science, Japanese, and English on the first day and mathematics and natural science on the second day.
 The exams start at 9:30 AM on both days and end at 6:10 PM on the first day and 5:50 PM on the second day.

### 2021-05-11 Codes/R/Regression/make_coef_figure.R

@@ -45,7 +45,7 @@ make_coef_figure <- function(res, temp_cut_str = "^temp_cut") {
         "" > 9
       )
     ) +
-    ylim(-0.4, 0.4)
+    ylim(-0.4, 0.48)
 
   
   return(fig)

### 2021-05-12 Slides/todai_center.tex
Revised slides for presentation

@@
   \begin{itemize}
-    \item Research Question: Does cold weather on the exam dates worsens performance at a high-stakes exam?
+    \item Research Question: Does cold weather on the exam date worsen performance in a high-stakes exam?
     \item Roadmap:
@@
       \begin{itemize}
-        \item Typically held in late February
+        \item Universities hold exams typically in \textcolor{red}{late February} and/or mid-March
         \item Students take the exams at universities they apply for
@@
       \begin{enumerate}
-        \item students in the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
-        \item students in the prefecture who would get into a higher-ranked university may get into the middle-ranked university
+        \item students in the prefecture who would have gotten into the middle-ranked university if the temperature were higher may end up in a lower-ranked university instead, but
+        \item students in the prefecture who would have gotten into a higher-ranked university may end up in the middle-ranked university instead
       \end{enumerate}
-    \item Considering the matriculation for UTokyo (= the most prestigious university in Japan) rules out the second possibility
+    \item Considering matriculation for UTokyo (the most prestigious university in Japan) rules out the second possibility
   \end{itemize}
@@
     \item $Y_{jt}$: matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$
-    \item $T_{jt}^k$: bin of average temperature across two exam dates in $j$ in year $t$
+    \item $T_{jt}^k$: $k$'th temperature interval 
+      \begin{itemize}
+        \item 3-$\degree$C intervals
+        \item Average across two exam dates in $j$ in year $t$
+      \end{itemize}
     \item $X_{jt}$: other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates
@@
 
-\begin{frame}\frametitle{Temperature effects on the matriculation shares (\%)}
+\begin{frame}\frametitle{Temperature effects on the matriculation shares (\%) \\ {\small Low temperature negatively affects exam performance}}
   \begin{center}
@@
 
-\begin{frame}\frametitle{Effects of other weather variables on the matriculation shares (\%)}
+\begin{frame}\frametitle{{\normalsize Effects of other weather variables on the matriculation shares (\%)} \\ {\small Cumulated snow on the ground negatively affects exam performance}}
     \begin{table}[h]
@@
 
-\begin{frame}\frametitle{Cognitive performance at the exam vs. Preparation}
-  \begin{minipage}{0.49\textwidth}
+\begin{frame}\frametitle{Cognitive performance at the exam vs. Preparation \\ {\small Temperature on the exam date matters}}
+  \begin{minipage}{0.43\textwidth}
     \begin{center}
@@
   \end{minipage}
-  \begin{minipage}{0.49\textwidth}
+  \begin{minipage}{0.43\textwidth}
     \begin{center}
@@
 
-\begin{frame}\frametitle{Effects of other weather variables on the matriculation shares (\%)}
+\begin{frame}\frametitle{{\normalsize Effects of other weather variables on the matriculation shares (\%)} \\ {\small Cumulated snow on the exam date matters}}
   \begin{table}[h]
@@
 
-\begin{frame}\frametitle{Some additional analysis: Female vs. Male}
-  \begin{minipage}{0.49\textwidth}
+\begin{frame}\frametitle{Some additional analysis: Female vs. Male \\ {\small Female students are less affected by temperature\dots or maybe not?}}
+  \begin{figure}
+    \center
+    \begin{minipage}{0.43\textwidth}
       \begin{center}
         Female \\
-      (mean: 0.38 \%, median: 0.13 \%)
+        {\small (mean: 0.38 \%, median: 0.13 \%)}
       \end{center}
@@
     \end{minipage}
-  \begin{minipage}{0.49\textwidth}
+    \begin{minipage}{0.43\textwidth}
       \begin{center}
         Male \\
-      (mean: 1.70 \%, median: 0.61 \%)
+        {\small (mean: 1.70 \%, median: 0.61 \%)}
       \end{center}
@@
     \end{tablenotes}
+  \end{figure}
 \end{frame}
 
-\begin{frame}\frametitle{Some additional analysis: Humanity vs. Science}
-  \begin{minipage}{0.49\textwidth}
+\begin{frame}\frametitle{Some additional analysis: Humanity vs. Science \\ {\small No significant difference in temperature effects}}
+  \begin{figure}
+    \center
+    \begin{minipage}{0.43\textwidth}
       \begin{center}
         Humanity \\
-      (mean: 2.07 \%, median: 0.76 \%)
+        {\small (mean: 2.07 \%, median: 0.76 \%)}
       \end{center}
@@
     \end{minipage}
-  \begin{minipage}{0.49\textwidth}
+    \begin{minipage}{0.43\textwidth}
       \begin{center}
         Science \\
-      (mean: 2.09 \%, median: 0.76 \%)
+        {\small (mean: 2.09 \%, median: 0.76 \%)}
       \end{center}
@@
     \end{tablenotes}
+  \end{figure}
 \end{frame}
 
-\begin{frame}\frametitle{Conclusion}
+\begin{frame}
+  \frametitle{Conclusion}
   \begin{itemize}
@@
       \begin{itemize}
-        \item Reducing temperature from 3-6 \degree C to $<$0 \degree C decreases the probability of matriculation by 0.18 percentage point \\
+        \item A decrease in temperature from 3-6 \degree C to $<$0 \degree C decreases the probability of matriculation by 0.18 percentage points \\
           (9\% of the average and 22\% of the median matriculation shares)
-        \item Snow on the ground cumulated more than 10cm decreases the probability of matriculation by 0.11 percentage point \\
+        \item Snow on the ground cumulated more than 10cm decreases the probability of matriculation by 0.11 percentage points \\
           (5\% of the average and 13\% of the median matriculation shares)
       \end{itemize}
-    \item Suggests that the exam performance is negatively affected by winter weather
-    \item Implications for university admission process:
+    \item Suggests that exam performance is negatively affected by winter weather
+      \begin{itemize}
+        \item Low temperature in the morning or during the exam negatively affects cognitive ability?
+        \item Snow on the ground makes feet wet, which further decreases body temperature?
+        \item Cumulated snow increases the risk of transportation delays?
+      \end{itemize}
+    \item Implications for university admissions process:
       \begin{itemize}
@@
 
-\begin{frame}\frametitle{Deviation of temperatures from within-prefecture averages}
+\begin{frame}\frametitle{Deviation of temperatures from within-prefecture averages \\ {\small Large variation in deviation of temperatures even within each year}} 
   \label{temp_dev_2}
@@
       %\caption{Map of matriculation shares (\%)}
-      \includegraphics[width=6.6cm]{../Output/images/temperature_diff_by_year.pdf}
+      \includegraphics[width=6.2cm]{../Output/images/temperature_diff_by_year.pdf}
       \tiny

### 2021-05-12 Writeups/paper.tex
Revised slides for presentation

@@
 
-I use the weather on the dates of Center Test and investigate its effect on the matriculation for the University of Tokyo (UTokyo henceforth).
+I use the weather on the dates of Center Test and investigate its effect on matriculation for the University of Tokyo (UTokyo henceforth).
 UTokyo is a national university and known to be the most prestigious in Japan.\footnote{
@@
 The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
-These include preparing waiting rooms for exam takers to warm up for equalizing their pre-exam conditions or adjusting the importance of the scores at Center Test in the admission process.
+These include preparing waiting rooms for exam takers to warm up for equalizing their pre-exam conditions or adjusting the importance of the scores at Center Test in the admissions process.
 
@@
   In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test (around 2\% of all admitted students).
-  Since the majority of students are admitted through the second-stage exam in February, below I focus on the admission process for those students. 
+  Since the majority of students are admitted through the second-stage exam in February, below I focus on the admissions process for those students. 
 }
@@
 Then, 
-(i) students in the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
-(ii) students in the prefecture who would get into a higher-ranked university may get into the middle-ranked university.
+(i) students in the prefecture who would have gotten into the middle-ranked university if the temperature were higher may end up in a lower-ranked university instead, but
+(ii) students in the prefecture who would have gotten into a higher-ranked university may end up in the middle-ranked university instead.
 Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
@@
 The main right-hand side variable is temperature on the exam dates.
-To allow for non-linear effects of temperature on the outcome, I use the 3-$^o$C temperature intervals, $T_{jt}^k$.\footnote{
+To allow for non-linear effects of temperature on the outcome, I use the 3-$^o$C temperature intervals.\footnote{
   The results with a linear specification are shown in Appendix \ref{sec:appendix_table} and will be discussed below.
 }
+Let $T_{jt}^k$ represent the $k$'th temperature bin.
 I also include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates as a vector $X_{jt}$.
@@
 To capture the effect of the existence of a certain amount of snow on the ground, column (4) allows a non-linear effect of cumulated snow.
-The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage point.
+The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage points.
 These results suggest that not only temperature but also snow on the ground on the exam dates affect exam performance.
@@
 The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam dates.
-Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
-Moreover, having more than 10cm of snow on the ground decreases the share by 0.11 percentage point.
+Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage points, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
+Moreover, having more than 10cm of snow on the ground decreases the share by 0.11 percentage points.
 
-The results in this study have implications for the admission process of universities.
+The results in this study have implications for the admissions process of universities.
 Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.

### 2021-05-19 Slides/todai_center.tex
After my presentation

@@
 \setbeamertemplate{navigation symbols}{}
-\title[Temperature and Exam]{Winter weather on exam dates and matriculation for a prestigious university in Japan}
+\title[Temperature and Exam]{Winter weather on exam date and matriculation for a prestigious university in Japan}
 \author[Suzuki]{Mizuhiro Suzuki}
@@
   \begin{itemize}
-    \item In Japan, for public university admission, students need to take two exams:
+    \item In Japan, for public university admission, students need to take two exams
     \item First-stage: \textcolor{red}{Center Test}
@@
       \begin{itemize}
-        \item Universities hold exams typically in \textcolor{red}{late February} and/or mid-March
+        \item Public universities hold exams typically in \textcolor{red}{late February} and/or mid-March
         \item Students take the exams at universities they apply for
@@
         Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
+        The darkest prefecture in the east part of Japan is Tokyo.
       \end{tablenotes}
@@
       \end{itemize}
-    \item $X_{jt}$: other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates
+    \item $X_{jt}$: other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam date
     \item $\mu_j$: prefecture fixed effects
@@
         I use temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-        Each interval on the x-axis does not include the right end.
         The 90\% confidence intervals are shown.
@@
 \begin{frame}\frametitle{Placebo test (including temperature one year after the exams)}
+  \begin{figure}
     \begin{minipage}{0.49\textwidth}
@@
       Rainfall and cumulated snow on the ground (both contemporaneous and one year later) are included in the regression.
-    Each interval on the x-axis does not include the right end.
       The 90\% confidence intervals are shown.
@@
     \end{tablenotes}
+  \end{figure}
 \end{frame}
@@
 \begin{frame}\frametitle{Cognitive performance at the exam vs. Preparation \\ {\small Temperature on the exam date matters}}
+  \begin{figure}
+    \center
     \begin{minipage}{0.43\textwidth}
       \begin{center}
-      Temperature at the exam dates
+        Temperature on the exam date \smallskip
       \end{center}
@@
       The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
-    In the left figure, the estimates on the temperature on the exam dates are shown.
+      In the left figure, the estimates on the temperature on the exam date are shown.
       In the right figure, the estimates on the average temperature for 10 days before the exam are shown.
       Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
-    Each interval on the x-axis does not include the right end.
       The 90\% confidence intervals are shown.
@@
     \end{tablenotes}
+  \end{figure}
 \end{frame}
 
-\begin{frame}\frametitle{{\normalsize Effects of other weather variables on the matriculation shares (\%)} \\ {\small Cumulated snow on the exam date matters}}
-  \begin{table}[h]
-    \Wider[4em]{
-    \center
-    \fontsize{7}{5}\selectfont
-    \input{../Output/tex/reg_pre10_beamer.tex}
+\begin{frame}
+  \frametitle{Additional analyses}
+  \begin{itemize}
+    \item Take population into account for the outcome variable:
+      \begin{equation*}
+        \frac{\text{\# matriculations for UTokyo from $j$ in year $t$}}{\text{Population (million) in $j$ in year $t$}}
+      \end{equation*}
+    \item Weather variables
+      \begin{itemize}
+        \item Average between 6AM and 6PM was used
+        \item See the effects of weather between 6AM-9AM (morning) and 9AM-6PM (during exam) separately
+      \end{itemize}
+    \item Male vs. Female
+      \begin{itemize}
+        \item Women are more sensitive to temperature changes?
+      \end{itemize}
+    \item Humanity vs. Science
+  \end{itemize}
+\end{frame}
+
+\begin{frame}\frametitle{Some additional analysis: Matriculation per population}
+  \begin{figure}
+    \begin{minipage}{0.44\textwidth}
+      \begin{center}
+        Matriculation per pop. (total) \\ (mean: 17.3)
+      \end{center}
+      \begin{figure}[h]
+        \centering
+        \includegraphics[width = \textwidth]{../Output/images/per_pop_reg_2.pdf}
+      \end{figure}
+    \end{minipage}
+    \begin{minipage}{0.44\textwidth}
+      \begin{center}
+        Matriculation per pop. (15-19-year-old) (mean: 361)
+      \end{center}
+      \begin{figure}[h]
+        \includegraphics[width = \textwidth]{../Output/images/per_pop_reg_4.pdf}
+        \centering
+      \end{figure}
+    \end{minipage}
     \tiny
     \begin{tablenotes}
-    \item 
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+    \item Notes;
+      The figures show the regression coefficients of the matriculation for UTokyo (\%) per population on temperature bins.
+      In the left figure, the matriculation per population (million) is used as an outcome.
+      In the right figure, the matriculation per 15-19-year-old population (million) is used as an outcome.
+      Rainfall and cumulated snow on the ground on the exam date are included in the regression.
+      Prefecture fixed effects and year fixed effects are also included.
+      The 90\% confidence intervals are shown.
       Standard errors are clustered at the prefecture level.
     \end{tablenotes}
-  }
-  \end{table}
+  \end{figure}
+\end{frame}
+
+\begin{frame}\frametitle{Some additional analysis: Matriculation per population \\ Placebo test (oh no!)}
+  \begin{figure}
+    \begin{minipage}{0.44\textwidth}
+      \begin{center}
+        Matriculation per pop. (total) \\ (contemporaneous temp.)
+      \end{center}
+      \begin{figure}[h]
+        \centering
+        \includegraphics[width = \textwidth]{../Output/images/per_pop_reg_t.pdf}
+      \end{figure}
+    \end{minipage}
+    \begin{minipage}{0.44\textwidth}
+      \begin{center}
+        Matriculation per pop. (total) (temp. one year after)
+      \end{center}
+      \begin{figure}[h]
+        \includegraphics[width = \textwidth]{../Output/images/per_pop_reg_f1.pdf}
+        \centering
+      \end{figure}
+    \end{minipage}
+    \tiny
+    \begin{tablenotes}
+    \item Notes;
+      The figures show the regression coefficients of the matriculation for UTokyo (\%) per population (total, million) on temperature bins.
+      In the left figure, the estimates on the contemporaneous temperature bins are shown.
+      In the right figure, the estimates on the temperature one year later are shown.
+      Rainfall and cumulated snow on the ground on the exam date are included in the regression.
+      Prefecture fixed effects and year fixed effects are also included.
+      The 90\% confidence intervals are shown.
+      Standard errors are clustered at the prefecture level.
+    \end{tablenotes}
+  \end{figure}
+\end{frame}
+
+\begin{frame}\frametitle{Some additional analysis: Population \\ Temperature on exam date affects population...?}
+  \begin{figure}
+    \begin{minipage}{0.44\textwidth}
+      \begin{center}
+        Total population (million) \\ (contemporaneous temp.)
+      \end{center}
+      \begin{figure}[h]
+        \centering
+        \includegraphics[width = \textwidth]{../Output/images/pop_reg_t.pdf}
+      \end{figure}
+    \end{minipage}
+    \begin{minipage}{0.44\textwidth}
+      \begin{center}
+        Total population (million) \\ (temp. one year after)
+      \end{center}
+      \begin{figure}[h]
+        \includegraphics[width = \textwidth]{../Output/images/pop_reg_f1.pdf}
+        \centering
+      \end{figure}
+    \end{minipage}
+    \tiny
+    \begin{tablenotes}
+    \item Notes;
+      The figures show the regression coefficients of the population (total, million) on temperature bins.
+      In the left figure, the estimates on the contemporaneous temperature bins are shown.
+      In the right figure, the estimates on the temperature one year later are shown.
+      Rainfall and cumulated snow on the ground on the exam date are included in the regression.
+      Prefecture fixed effects and year fixed effects are also included.
+      The 90\% confidence intervals are shown.
+      Standard errors are clustered at the prefecture level.
+    \end{tablenotes}
+  \end{figure}
+\end{frame}
+
+\begin{frame}\frametitle{{\normalsize Some additional analysis: Temperature in the morning vs. during exam} \\ {\small Temperature in the morning matters more, maybe?}}
+  \begin{figure}
+    \begin{minipage}{0.44\textwidth}
+      \begin{center}
+        Temperature in the morning \\ (6AM - 9AM)
+      \end{center}
+      \begin{figure}[h]
+        \centering
+        \includegraphics[width = \textwidth]{../Output/images/morning_exam_reg_6_morning.pdf}
+      \end{figure}
+    \end{minipage}
+    \begin{minipage}{0.44\textwidth}
+      \begin{center}
+        Temperature during exam \\ (9AM - 6PM)
+      \end{center}
+      \begin{figure}[h]
+        \includegraphics[width = \textwidth]{../Output/images/morning_exam_reg_6_exam.pdf}
+        \centering
+      \end{figure}
+    \end{minipage}
+    \tiny
+    \begin{tablenotes}
+    \item Notes;
+      The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
+      In the left figure, the estimates on the temperature (average between 6AM and 9AM) bins are shown.
+      In the right figure, the estimates on the temperature (average between 9AM and 6PM) bins are shown.
+      Rainfall and cumulated snow on the ground (both in the morning and during exam) are included in the regression.
+      The 90\% confidence intervals are shown.
+      Prefecture fixed effects and year fixed effects are also included.
+      Standard errors are clustered at the prefecture level.
+    \end{tablenotes}
+  \end{figure}
 \end{frame}
@@
       Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
-      Each interval on the x-axis does not include the right end.
       The 90\% confidence intervals are shown.
@@
   \begin{itemize}
-    \item Weather on the exam dates affects the matriculations for UTokyo
+    \item Weather on the exam date affects the matriculations for UTokyo
       \begin{itemize}
@@
 
+\begin{frame}\frametitle{{\normalsize Effects of other weather variables on the matriculation shares (\%)} \\ {\small Cumulated snow on the exam date, not before exams, matters}}
+  \begin{table}[h]
+    \Wider[4em]{
+    \center
+    \fontsize{7}{5}\selectfont
+    \input{../Output/tex/reg_pre10_beamer.tex}
+    \tiny
+    \begin{tablenotes}
+    \item 
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      Standard errors are clustered at the prefecture level.
+    \end{tablenotes}
+  }
+  \end{table}
+\end{frame}
+
 \end{document}

### 2021-05-19 Writeups/paper.tex
After my presentation

@@
 The first-stage test is Center Test.
-Students take an exam on consecutive two days (Saturday and Sunday) in mid-January.
+Students take an exam on two consecutive days (Saturday and Sunday) in mid-January.
 Most public universities, including UTokyo, require students to take exams on social science, Japanese, and English on the first day and mathematics and natural science on the second day.
@@
       Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
+      The darkest prefecture in the east part of Japan is Tokyo.
   \end{tablenotes}
@@
 Without other weather variables, the estimates in column (1) show a negative and statistically significant impact of cold weather.
-Since the mean matriculation share is $2.08$\%, by reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest temperature bin (below 0 $^o$C), the matriculation share decreases by 9\%.
+Since the mean matriculation share is $2.08$\%, a decrease in the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest temperature bin (below 0 $^o$C) results in the lower matriculation share by 9\%.
 Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$\%.
@@
       I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-      Temperature intervals do not contain the right ends.
+      Temperature intervals do not contain the left ends.
       Standard errors are clustered at the prefecture level.
@@
       For weather variables with "(previous 10 days)", I use their averages at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
-      Temperature intervals do not contain the right ends.
+      Temperature intervals do not contain the left ends.
       Standard errors are clustered at the prefecture level.
@@
       I represent the contemporaneous weather variables with ``($t$)'' and the weather one year after Center Test with ``($t + 1$).''
-      Temperature intervals do not contain the right ends.
+      Temperature intervals do not contain the left ends.
       Standard errors are clustered at the prefecture level.

### 2021-05-19 Codes/R/Data_clean/admission_clean.R

@@ -71,12 +71,12 @@ load_admission_df <- function(file_path, year) {
     dplyr::select(- c(
       admission_male_Arts, admission_male_Sciences, 
       admission_female_Arts, admission_female_Sciences, 
-      admission_total_Arts, admission_total_Sciences
+      # admission_total_Arts, admission_total_Sciences
       )) %>% 
     filter(prefecture != "その他") %>% 
     mutate(
       across(
-        .cols = starts_with("admission_"),
+        .cols = (starts_with("admission_") & ends_with("_share")),
         .fns = ~ . * 100
       )
     ) %>% 
@@ -123,5 +123,49 @@ admission_df_all <- bind_rows(
   )
 )
 
+admission_df_all <- admission_df_all %>% 
+  mutate(admission_total = admission_total_Arts + admission_total_Sciences) %>% 
+  left_join(
+    read_csv(file.path(dropbox_dir, "Data/population_data.csv")),
+    by = c("prefecture", "year")
+  ) %>% 
+  group_by(prefecture) %>% 
+  mutate(
+    avg_total_pop = mean(total_pop),
+    avg_pop_15_19 = mean(pop_15_19)
+    ) %>% 
+  mutate(
+    admission_per_pop = admission_total / total_pop,
+    admission_per_pop_15_19 = admission_total / pop_15_19,
+    admission_per_avg_pop = admission_total / avg_total_pop,
+    admission_per_avg_pop_15_19 = admission_total / avg_pop_15_19
+  ) 
+
 write_csv(admission_df_all, file.path(dropbox_dir, "Data/admission_data.csv"))
 
+goopy
+
+admission_df_all %>% 
+  # filter(prefecture %in% aa[1:10]) %>% 
+  group_by(prefecture) %>% 
+  mutate(dev = (admission_total_share - mean(admission_total_share))) %>% 
+  # mutate(dev = (admission_total_share - mean(admission_total_share)) / sd(admission_total_share)) %>% 
+  ggplot(aes(x = prefecture_eng, y = dev, color = factor(year))) +
+  geom_point() +
+  scale_x_discrete(
+    limits = admission_df_all %>% 
+        group_by(prefecture_eng) %>% 
+        summarise_at(vars(admission_total), sd) %>% 
+        arrange(admission_total) %>% 
+        .$prefecture_eng %>% 
+        as.vector
+  ) +
+  coord_flip()
+
[…]

### 2021-05-19 Codes/R/Data_clean/merge_data.R

@@ -8,7 +8,8 @@ packages <- c(
   "lubridate",
   "readxl",
   "lfe",
-  "stargazer"
+  "stargazer",
+  "RStata"
 )
 pacman::p_load(packages, character.only = TRUE)
 

### 2021-05-19 Codes/R/Data_clean/population_clean.R

@@ -1,0 +1,116 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+population_clean_func <- function(year) {
+  
+  print(year)
+   
+  if (year < 2020) {
+    file_path <- file.path(
+      dropbox_dir,
+      str_interp("Data/population_data/${year}_population.xls")
+      )
+  } else {
+    file_path <- file.path(
+      dropbox_dir,
+      str_interp("Data/population_data/2019_population.xls")
+      )
+  }
+
+  if (year != 2015) {
+    output_df <- read_excel(file_path, skip = 20, col_names = FALSE) %>% 
+      head(47) %>% 
+      select(10, 12, 13, 17) %>% 
+      set_colnames(c("prefecture", "prefecture_eng", "total_pop", "pop_15_19")) %>% 
+      mutate(
+        across(
+          c(total_pop, pop_15_19),
+          ~ as.numeric(.)
+        ),
+        year = year
+      )
+  } else {
+    output_df <- read_excel(file_path, skip = 18, col_names = FALSE) %>% 
+      head(47) %>% 
+      select(3, 5, 6, 10) %>% 
+      set_colnames(c("prefecture", "prefecture_eng", "total_pop", "pop_15_19")) %>% 
+      mutate(
+        across(
+          c(total_pop, pop_15_19),
+          ~ as.numeric(.)
+        ),
+        year = year 
+      )
+  }
+  
+  return(output_df)
+}
+
+pop_df <- map(
+  seq(2012, 2020),
+  population_clean_func
+  ) %>% 
+  bind_rows() %>% 
+  mutate(
+    prefecture = str_replace(prefecture, "県", ""),
+    prefecture = str_replace(prefecture, "府", ""),
+    prefecture = str_replace(prefecture, "東京都", "東京"),
+    prefecture = str_trim(prefecture, side = "both")
+  ) %>% 
+  mutate(
+    total_pop = total_pop / 1000,
+    pop_15_19 = pop_15_19 / 1000
+  )
+     
+# file_path <- file.path(
+#   dropbox_dir,
[…]

### 2021-05-19 Codes/R/Regression/art_science_regression.R

@@ -1,46 +1,25 @@
-packages <- c(
-  "tidyverse",
-  "curl",
-  "rvest",
-  "magrittr",
-  "lubridate",
-  "readxl",
-  "lfe",
-  "stargazer"
-)
-pacman::p_load(packages, character.only = TRUE)
-
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
-
-# Load regression data =================
-reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
-
-# Import function to make estimate figures
-source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
-
 # Regression for humanity and science majors separately =====================
 
 res_1 <- felm(
-  admission_Arts_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
+  admission_Arts_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
   )
 
 res_2 <- felm(
-  admission_Arts_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
+  admission_Arts_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
 
 res_3 <- felm(
-  admission_Sciences_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
+  admission_Sciences_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
   )
 
 res_4 <- felm(
-  admission_Sciences_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
+  admission_Sciences_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
@@ -54,9 +33,9 @@ list(res_1, res_2, res_3, res_4) %>%
       "Temperature (\\degree C) $>$ 6, $\\le$ 9",
       "Temperature (\\degree C) $>$ 9",
       "Rainfall (mm)",
-      "Snowfall (m)",
[…]

### 2021-05-19 Codes/R/Regression/gender_regression.R

@@ -1,46 +1,25 @@
-packages <- c(
-  "tidyverse",
-  "curl",
-  "rvest",
-  "magrittr",
-  "lubridate",
-  "readxl",
-  "lfe",
-  "stargazer"
-)
-pacman::p_load(packages, character.only = TRUE)
-
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
-
-# Load regression data =================
-reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
-
-# Import function to make estimate figures
-source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
-
 # Regression by male and female matriculations =====================
 
 res_1 <- felm(
-  admission_female_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
+  admission_female_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
   )
 
 res_2 <- felm(
-  admission_female_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
+  admission_female_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
 
 res_3 <- felm(
-  admission_male_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
+  admission_male_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
   )
 
 res_4 <- felm(
-  admission_male_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
+  admission_male_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
@@ -54,9 +33,9 @@ list(res_1, res_2, res_3, res_4) %>%
       "Temperature (\\degree C) $>$ 6, $\\le$ 9",
       "Temperature (\\degree C) $>$ 9",
       "Rainfall (mm)",
-      "Snowfall (m)",
-      "Cumulated snow (m)",
-      "Cumulated snow $>$ .10 m"
[…]

### 2021-05-19 Codes/R/Regression/linear_regression.R

@@ -1,25 +1,3 @@
-packages <- c(
-  "tidyverse",
-  "curl",
-  "rvest",
-  "magrittr",
-  "lubridate",
-  "readxl",
-  "lfe",
-  "stargazer",
-  "latex2exp"
-)
-pacman::p_load(packages, character.only = TRUE)
-
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
-
-# Load regression data =================
-reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
-
-# Import function to make estimate figures
-source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
-
 # Regression with linear specification ==========================
 
 res_1 <- felm(
@@ -29,13 +7,13 @@ res_1 <- felm(
   )
 
 res_2 <- felm(
-  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_snowfall_m | 
+  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_snowfall_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
   )
 
 res_3 <- felm(
-  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_cum_snow_m | 
+  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_cum_snow_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
   )
@@ -52,9 +30,9 @@ list(res_1, res_2, res_3, res_4) %>%
     covariate.labels = c(
       "Temperature (\\degree C)",
       "Rainfall (mm)",
-      "Snowfall (m)",
-      "Cumulated snow (m)",
-      "Cumulated snow $>$ .10 m"
+      "Snowfall (cm)",
+      "Cumulated snow (cm)",
+      "Cumulated snow $>$ 10 cm"
     ),
     title = "",
     add.lines = list(

### 2021-05-19 Codes/R/Regression/main_regression.R

@@ -1,25 +1,3 @@
-packages <- c(
-  "tidyverse",
-  "curl",
-  "rvest",
-  "magrittr",
-  "lubridate",
-  "readxl",
-  "lfe",
-  "stargazer",
-  "latex2exp"
-)
-pacman::p_load(packages, character.only = TRUE)
-
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
-
-# Load regression data =================
-reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
-
-# Import function to make estimate figures
-source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
-
 # Main regression ==========================
 
 res_1 <- felm(
@@ -29,13 +7,13 @@ res_1 <- felm(
   )
 
 res_2 <- felm(
-  admission_total_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
+  admission_total_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
 
 res_3 <- felm(
-  admission_total_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
+  admission_total_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
@@ -55,9 +33,9 @@ list(res_1, res_2, res_3, res_4) %>%
       "Temperature (\\degree C) 6-9",
       "Temperature (\\degree C) $>$ 9",
       "Rainfall (mm)",
-      "Snowfall (m)",
-      "Cumulated snow (m)",
-      "Cumulated snow $>$ .10 m"
+      "Snowfall (cm)",
+      "Cumulated snow (cm)",
+      "Cumulated snow $>$ 10 cm"
     ),
     title = "",
     add.lines = list(
@@ -80,9 +58,9 @@ list(res_2, res_3, res_4) %>%
     ),
     covariate.labels = c(
       "Rainfall (mm)",
-      "Snowfall (m)",
-      "Cumulated snow (m)",
-      "Cumulated snow $>$ .10 m"
+      "Snowfall (cm)",
+      "Cumulated snow (cm)",
+      "Cumulated snow $>$ 10 cm"
     ),
     title = "",
     add.lines = list(

### 2021-05-19 Codes/R/Regression/make_coef_figure.R

@@ -1,6 +1,6 @@
 # Function to make estimates coefficient figures
 
-make_coef_figure <- function(res, temp_cut_str = "^temp_cut") {
+make_coef_figure <- function(res, temp_cut_str = "^temp_cut", ylim_lb = -0.40, ylim_ub = 0.40) {
 
   temp_cut_names <- grepl(temp_cut_str, rownames(res$coefficients))
 
@@ -35,18 +35,17 @@ make_coef_figure <- function(res, temp_cut_str = "^temp_cut") {
     ylab("Coefficients") +
     xlab("Temperature bins (Celsius)") +
     theme(axis.title = element_text(size = 15),
-          axis.text = element_text(size = 12)) +
+          axis.text = element_text(size = 15)) +
     scale_x_discrete(
       labels = expression(
         "" <= 0,
-        0-3,
-        3-6,
-        6-9,
+        "(0, 3]",
+        "(3, 6]",
+        "(6, 9]",
         "" > 9
       )
     ) +
-    ylim(-0.4, 0.48)
-
+    ylim(ylim_lb, ylim_ub)
   
   return(fig)
 }

### 2021-05-19 Codes/R/Regression/morning_exam_regression.R

@@ -1,0 +1,199 @@
+# Main regression ==========================
+
+res_1 <- felm(
+  admission_total_share ~ temp_cut_morning + morning_precipitation_mm + morning_snowfall_cm | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_2 <- felm(
+  admission_total_share ~ temp_cut_morning + morning_precipitation_mm + morning_cum_snow_cm | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_3 <- felm(
+  admission_total_share ~ temp_cut_exam + exam_precipitation_mm + exam_snowfall_cm | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_4 <- felm(
+  admission_total_share ~ temp_cut_exam + exam_precipitation_mm + exam_cum_snow_cm | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_5 <- felm(
+  admission_total_share ~ 
+    temp_cut_morning + morning_precipitation_mm + morning_snowfall_cm +
+    temp_cut_exam + exam_precipitation_mm + exam_snowfall_cm | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_6 <- felm(
+  admission_total_share ~ 
+    temp_cut_morning + morning_precipitation_mm + morning_cum_snow_cm +
+    temp_cut_exam + exam_precipitation_mm + exam_cum_snow_cm | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+list(res_1, res_2, res_3, res_4, res_5, res_6) %>% 
+  stargazer(
+    dep.var.labels = "Matriculation share (\\%)",
+    covariate.labels = c(
+      "Temperature (\\degree C) $\\le$ -3 (morning)",
+      "Temperature (\\degree C) -3-0 (morning)",
+      "Temperature (\\degree C) 3-6 (morning)",
+      "Temperature (\\degree C) $>$ 6 (morning)",
+      "Rainfall (mm) (morning)",
+      "Snowfall (cm) (morning)",
+      "Cumulated snow (cm) (morning)",
+      "Temperature (\\degree C) $\\le$ -3 (during exam)",
[…]

### 2021-05-19 Codes/R/Regression/placebo_regression.R

@@ -1,50 +1,29 @@
-packages <- c(
-  "tidyverse",
-  "curl",
-  "rvest",
-  "magrittr",
-  "lubridate",
-  "readxl",
-  "lfe",
-  "stargazer"
-)
-pacman::p_load(packages, character.only = TRUE)
-
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
-
-# Load regression data =================
-reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
-
-# Import function to make estimate figures
-source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
-
 # Placebo regression with lead weather =====================
 
 res_1 <- felm(
-  admission_total_share ~ f1_temp_cut + f1_precipitation_mm + f1_snowfall_m |
+  admission_total_share ~ f1_temp_cut + f1_precipitation_mm + f1_snowfall_cm |
     prefecture + year | 0 | prefecture, 
   data = reg_df
   )
 
 res_2 <- felm(
-  admission_total_share ~ f1_temp_cut + f1_precipitation_mm + f1_cum_snow_m |
+  admission_total_share ~ f1_temp_cut + f1_precipitation_mm + f1_cum_snow_cm |
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
 
 res_3 <- felm(
   admission_total_share ~ 
-    temp_cut + daytime_precipitation_mm + daytime_snowfall_m +
-    f1_temp_cut + f1_precipitation_mm + f1_snowfall_m |
+    temp_cut + daytime_precipitation_mm + daytime_snowfall_cm +
+    f1_temp_cut + f1_precipitation_mm + f1_snowfall_cm |
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
 
 res_4 <- felm(
   admission_total_share ~ 
-    temp_cut + daytime_precipitation_mm + daytime_cum_snow_m +
-    f1_temp_cut + f1_precipitation_mm + f1_cum_snow_m |
+    temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm +
+    f1_temp_cut + f1_precipitation_mm + f1_cum_snow_cm |
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
[…]

### 2021-05-19 Codes/R/Regression/pre10_regression.R

@@ -1,50 +1,29 @@
-packages <- c(
-  "tidyverse",
-  "curl",
-  "rvest",
-  "magrittr",
-  "lubridate",
-  "readxl",
-  "lfe",
-  "stargazer"
-)
-pacman::p_load(packages, character.only = TRUE)
-
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
-
-# Load regression data =================
-reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
-
-# Import function to make estimate figures
-source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
-
 # Regression with weather for the previous 10 days =====================
 
 res_1 <- felm(
-  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10_m |
+  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10 |
     prefecture + year | 0 | prefecture, 
   data = reg_df
   )
 
 res_2 <- felm(
-  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10_m |
+  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10 |
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
 
 res_3 <- felm(
   admission_total_share ~ 
-    temp_cut + daytime_precipitation_mm + daytime_snowfall_m +
-    temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10_m |
+    temp_cut + daytime_precipitation_mm + daytime_snowfall_cm +
+    temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10 |
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
 
 res_4 <- felm(
   admission_total_share ~ 
-    temp_cut + daytime_precipitation_mm + daytime_cum_snow_m +
-    temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10_m |
+    temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm +
+    temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10 |
     prefecture + year | 0 | prefecture, 
   data = reg_df
 )
[…]

### 2021-05-19 Codes/R/Regression/regression.R

@@ -1,402 +1,0 @@
-packages <- c(
-  "tidyverse",
-  "curl",
-  "rvest",
-  "magrittr",
-  "lubridate",
-  "readxl",
-  "lfe",
-  "stargazer"
-)
-pacman::p_load(packages, character.only = TRUE)
-
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
-
-# Load regression data =================
-reg_df <- read_csv(file.path(dropbox_dir, "Data/temp/data_regression.csv"))
-
-# Main regression ==========================
-
-res_1 <- felm(
-  admission_total_share ~ daytime_temperature_degree | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_2 <- felm(
-  admission_total_share ~ temp_cut | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_3 <- felm(
-  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_snowfall_m | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_4 <- felm(
-  admission_total_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_m | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_5 <- felm(
-  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_cum_snow_m | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_6 <- felm(
-  admission_total_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_m | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_7 <- felm(
-  admission_total_share ~ temp_cut + daytime_precipitation_mm + factor(daytime_cum_snow_m > .1) | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-list(res_1, res_2, res_3, res_4, res_5, res_6, res_7) %>% 
-  stargazer(
-    dep.var.labels = "Matriculation share (\\%)",
-    covariate.labels = c(
-      "Temperature (degree C)",
[…]

### 2021-05-19 Codes/R/Regression/run_all_regression.R

@@ -1,0 +1,44 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Load regression data =================
+reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
+
+# Import function to make estimate figures
+source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
+
+# Main regression
+source(file.path(git_dir, "Codes/R/Regression/main_regression.R"))
+
+# Placebo regression
+source(file.path(git_dir, "Codes/R/Regression/placebo_regression.R"))
+
+# Regression with weather for the previous 10 days
+source(file.path(git_dir, "Codes/R/Regression/pre10_regression.R"))
+
+# Linear regression
+source(file.path(git_dir, "Codes/R/Regression/linear_regression.R"))
+
+# Regression by gender
+source(file.path(git_dir, "Codes/R/Regression/gender_regression.R"))
+
+# Regression by major
+source(file.path(git_dir, "Codes/R/Regression/art_science_regression.R"))
+
+# Regression (morning vs. during exam)
+source(file.path(git_dir, "Codes/R/Regression/morning_exam_regression.R"))
+
+
+

### 2021-05-19 Codes/R/Regression/share_per_pop_regression.R

@@ -1,0 +1,490 @@
+# Regression with matriculation per population (million) ==========================
+
+res_1 <- felm(
+  admission_per_pop ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_2 <- felm(
+  admission_per_pop ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_3 <- felm(
+  admission_per_pop_15_19 ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_4 <- felm(
+  admission_per_pop_15_19 ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+list(res_1, res_2, res_3, res_4) %>% 
+  stargazer(
+    dep.var.labels = "Matriculation per population (million)",
+    column.labels = c(rep("Total", 2), rep("15-19", 2)),
+    covariate.labels = c(
+      "Temperature (\\degree C) $\\le$ 0",
+      "Temperature (\\degree C) 0-3",
+      "Temperature (\\degree C) 6-9",
+      "Temperature (\\degree C) $>$ 9",
+      "Rainfall (mm)",
+      "Snowfall (cm)",
+      "Cumulated snow (cm)",
+      "Cumulated snow $>$ 10 cm"
+    ),
+    title = "",
+    add.lines = list(
+      c("Prefecture FE", rep("Yes", 8)),
+      c("Year FE", rep("Yes", 8))
+    ),
+    type = "latex",
+    out = file.path(git_dir, "Output/tex/per_pop_reg.tex"),
+    omit.stat = c("adj.rsq", "ser", "rsq"),
+    digits = 2,
+    float = FALSE
+  )
+
+# Non-linear regression figures ============
+walk2(
+  list(res_1, res_2),
+  c(1, 2), 
+  ~ ggsave(
+    filename = file.path(git_dir, str_interp("Output/images/per_pop_reg_${.y}.pdf")),
+    plot = make_coef_figure(.x, ylim_lb = -10, ylim_ub = 10),
+    height = 6,
+    width = 6
+    )
+  )
+
[…]

### 2021-05-19 Codes/R/SumStat/sumstat.R

@@ -47,8 +47,8 @@ list(
       admission_total_share,
       daytime_temperature_degree,
       daytime_precipitation_mm,
-      daytime_snowfall_m,
-      daytime_cum_snow_m
+      daytime_snowfall_cm,
+      daytime_cum_snow_cm
       ) %>% 
     summarise_all(x)
   ) %>% 
@@ -69,8 +69,8 @@ list(
     "Matriculation share (\\%)",
     "Temperature (\\degree C)",
     "Hourly precipitation (mm)",
-    "Hourly snowfall (m)",
-    "Cumulated snow (m)"
+    "Hourly snowfall (cm)",
+    "Cumulated snow (cm)"
   )) %>% 
   kbl("latex", booktabs = TRUE, escape = FALSE) %>% 
   add_header_above(

### 2021-05-19 Codes/R/SumStat/weather_diff.R

@@ -26,12 +26,12 @@ prefecture_order <- loc_df$prefecture
 
 weather_df_avg <- weather_df %>% 
   mutate(
-    daytime_cum_snow_m = daytime_cum_snow_cm / 100,
-    daytime_snowfall_m = daytime_snowfall_cm / 100,
+    daytime_cum_snow_cm = daytime_cum_snow_cm / 100,
+    daytime_snowfall_cm = daytime_snowfall_cm / 100,
     ) %>% 
   group_by(prefecture, exam_year, exam_month) %>% 
   summarise_at(
-    vars(daytime_temperature_degree, daytime_cum_snow_m, daytime_snowfall_m, daytime_precipitation_mm), 
+    vars(daytime_temperature_degree, daytime_cum_snow_cm, daytime_snowfall_cm, daytime_precipitation_mm), 
     mean
     ) %>% 
   mutate(prefecture = rev(factor(prefecture, levels = prefecture_order)))
@@ -129,12 +129,12 @@ ggsave(
 # Daytime cumulated snow
 prefecture_order <- weather_df_avg %>% 
   group_by(prefecture) %>% 
-  summarise_at(vars(daytime_cum_snow_m), mean, na.rm = TRUE) %>% 
-  arrange(daytime_cum_snow_m) %>% 
+  summarise_at(vars(daytime_cum_snow_cm), mean, na.rm = TRUE) %>% 
+  arrange(daytime_cum_snow_cm) %>% 
   .$prefecture %>% 
   as.vector()
 p <- weather_df_avg %>% 
-  ggplot(aes(x = prefecture, y = daytime_cum_snow_m, color = factor(exam_year))) +
+  ggplot(aes(x = prefecture, y = daytime_cum_snow_cm, color = factor(exam_year))) +
   geom_point() +
   scale_x_discrete(limits = prefecture_order) +
   scale_color_brewer(
@@ -165,12 +165,12 @@ ggsave(
 # Daytime snowfall
 prefecture_order <- weather_df_avg %>% 
   group_by(prefecture) %>% 
-  summarise_at(vars(daytime_snowfall_m), mean, na.rm = TRUE) %>% 
-  arrange(daytime_snowfall_m) %>% 
+  summarise_at(vars(daytime_snowfall_cm), mean, na.rm = TRUE) %>% 
+  arrange(daytime_snowfall_cm) %>% 
   .$prefecture %>% 
   as.vector()
 p <- weather_df_avg %>% 
[…]

### 2021-05-19 Codes/R/SumStat/weather_map.R

@@ -39,9 +39,9 @@ map <- shapefile(
 )
 
 weather_df_avg <- weather_df %>% 
-  mutate(daytime_cum_snow_m = daytime_cum_snow_cm / 100) %>% 
+  mutate(daytime_cum_snow_cm = daytime_cum_snow_cm / 100) %>% 
   group_by(prefecture) %>% 
-  summarise_at(vars(daytime_temperature_degree, daytime_cum_snow_m), mean)
+  summarise_at(vars(daytime_temperature_degree, daytime_cum_snow_cm), mean)
 
 map@data$ADM1_JA <- str_replace(map@data$ADM1_JA, "県|府", "")
 map@data$ADM1_JA <- str_replace(map@data$ADM1_JA, "東京都", "東京")
@@ -80,7 +80,7 @@ png(file = filepath)
 print(
   spplot(
     map_avg, 
-    "daytime_cum_snow_m", 
+    "daytime_cum_snow_cm", 
     sp.layout = list(map_Japan, lwd = 0.1), 
     col.regions = brewer.pal(n = 7, name = "OrRd"),
     # cuts = 6,

### 2021-05-21 Codes/R/Regression/share_per_pop_regression.R
Update share_per_pop_regression.R

@@ -487,4 +487,5 @@ ggsave(
 
 reg_df %>% 
   group_by(prefecture) %>% 
-  summarise_at(vars(admission_total_share), mean)
+  summarise_at(vars(admission_total_share), mean) %>% 
+  View

### 2023-10-25 Writeups/paper.tex
clean data cleaning codes

@@
 
-\title{Winter weather on exam dates and matriculation for a prestigious university in Japan}%: \\ Empirical analysis on auditing reports in Brazil}
-%\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison.
-Contact: msuzuki7@wisc.edu.
-The author would like to thank Laura Schechter for her numerous feedback and support.
-I am also grateful to Joshua Deutschmann, Paul Dower, Jeremy Foltz, Priya Mukherjee, Andrew Stevens, and seminar participants at the UW-Madison Agricultural and Applied Economics department for helpful comments and suggestions.
-Any errors in this draft are the sole responsibility of the author.}}
+\title{Winter weather on exam dates and matriculation for a prestigious university in Japan}
 \author{
   Mizuhiro Suzuki\thanks{
-    Department of Agricultural and Applied Economics, University of Wisconsin-Madison.
-    Contact: msuzuki7@wisc.edu.
+    Contact: mizuhiro.suzuki@gmail.com.
     The author would like to thank Laura Schechter for her numerous feedback and support.

### 2023-10-25 Codes/R/Data_clean/admission_clean.R

@@ -1,17 +1,5 @@
-packages <- c(
-  "tidyverse",
-  "curl",
-  "rvest",
-  "magrittr",
-  "lubridate",
-  "readxl"
-)
-pacman::p_load(packages, character.only = TRUE)
-
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
-
 # Load admission information =================
+read_excel(file.path(dropbox_dir, "Data/Raw/admission_data/2021_08go_G.xlsx"), skip=2)
 
 load_admission_df <- function(file_path, year) {
   
@@ -24,10 +12,17 @@ load_admission_df <- function(file_path, year) {
         department = 学部名,
         gender = 県別入学者数
       )
-  } else {
+  } else if (year <= 2020) {
     output_df <- read_excel(file_path, skip = 2) %>% 
       rename(
         univ = 学校名,
+        department = 学部名,
+        gender = 性別
+      )
+  } else {
+    output_df <- read_excel(file_path, skip = 2) %>% 
+      rename(
+        univ = 大学名,
         department = 学部名,
         gender = 性別
       )
@@ -51,15 +46,6 @@ load_admission_df <- function(file_path, year) {
     ) %>% 
     pivot_wider(names_from = gender, values_from = admission, names_prefix = "admission_") %>% 
     mutate(admission_total = admission_male + admission_female) %>% 
-    # group_by(department) %>% 
-    # mutate(
-    #   across(
-    #     .cols = starts_with("admission"),
-    #     .fns = ~ . / sum(admission_total),
-    #     .names = "{col}_share"
-    #   )
-    # ) %>% 
-    # ungroup() %>% 
     pivot_wider(names_from = department, values_from = starts_with("admission_")) %>% 
     mutate(
       admission_male_share = (admission_male_Arts + admission_male_Sciences) / (sum(admission_total_Arts) + sum(admission_total_Sciences)),
@@ -68,11 +54,6 @@ load_admission_df <- function(file_path, year) {
       admission_Sciences_share = (admission_male_Sciences + admission_female_Sciences) / sum(admission_total_Sciences),
[…]

### 2023-10-25 Codes/R/Data_clean/merge_data.R

@@ -1,41 +1,16 @@
 # Merge data for regressions
 
-packages <- c(
-  "tidyverse",
-  "curl",
-  "rvest",
-  "magrittr",
-  "lubridate",
-  "readxl",
-  "lfe",
-  "stargazer",
-  "RStata"
-)
-pacman::p_load(packages, character.only = TRUE)
-
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
-
 # Load admission information =================
-admission_df <- read_csv(file.path(dropbox_dir, "Data/admission_data.csv"))
+admission_df <- read_csv(file.path(dropbox_dir, "Data/Processed/admission_data.csv"))
 
 # Load weather information on exam days =================
-weather_exam_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_on_exam_day.csv"))
-
-# Load weather information on exam days (1 year lag) =================
-weather_l1_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_l1.csv"))
+weather_exam_df <- read_csv(file.path(dropbox_dir, "Data/Processed/weather_on_exam_day.csv"))
 
 # Load weather information on exam days (1 year lead) =================
-weather_f1_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_f1.csv"))
+weather_f1_df <- read_csv(file.path(dropbox_dir, "Data/Processed/weather_f1.csv"))
 
 # Load weather information (previous 10 days) =================
-weather_pre10_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_pre10.csv"))
-
-# Load weather information (Oct, Nov, Dec before the exams) =================
-weather_pre_oct_dec_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_pre_oct_dec.csv"))
-
-# Load weather information (Previous summer from May to September) =================
-weather_summer_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_summer.csv"))
+weather_pre10_df <- read_csv(file.path(dropbox_dir, "Data/Processed/weather_pre10.csv"))
 
 # Regression with average weather =====================
 
[…]

### 2023-10-25 Codes/R/Data_clean/run_all_cleaning.R

@@ -1,0 +1,27 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "stargazer",
+  "RStata"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+dropbox_dir <- "~/Dropbox/todai_center/"
+git_dir <- "~/Documents/GitHub/todai_center/"
+
+# Download weather data
+# source(file.path(git_dir, "Codes/R/Data_clean/weather_download.R"))
+
+# Cleaning weather data
+source(file.path(git_dir, "Codes/R/Data_clean/weather_clean.R"))
+
+# Cleaning admission data
+source(file.path(git_dir, "Codes/R/Data_clean/admission_clean.R"))
+
+# Merge data
+source(file.path(git_dir, "Codes/R/Data_clean/merge_data.R"))

### 2023-10-25 Codes/R/Regression/main_regression.R

@@ -1,7 +1,7 @@
 # Main regression ==========================
 
 res_1 <- felm(
-  admission_total_share ~ temp_cut | 
+  admission_total_share ~ temp_cut |
     prefecture + year | 0 | prefecture, 
   data = reg_df
   )

### 2023-10-25 Codes/R/Regression/share_per_pop_regression.R

@@ -489,3 +489,19 @@ reg_df %>%
   group_by(prefecture) %>% 
   summarise_at(vars(admission_total_share), mean) %>% 
   View
+
+
+felm(
+  admission_total_share ~ 
+    temp_cut + daytime_precipitation_mm + daytime_snowfall_cm +
+        f1_temp_cut + f1_precipitation_mm + f1_snowfall_cm | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  ) %>% 
+  summary
+
+reg_df %>% 
+  group_by(prefecture) %>% 
+  summarise_at(vars(admission_total_share), mean) %>% 
+  arrange(desc(admission_total_share))
+

### 2023-10-26 Writeups/paper.tex
reran all scripts and compiled paper

@@
 }
-\date{\today \\ \vspace{1cm} Preliminary draft \\ Please do not cite or circulate}
+\date{\today}
 
@@
     This result suggests that the winter weather on exam dates worsens exam performance.
-    %The implications on how to design university admissions are discussed.
 
@@
 For admission selection, standardized exams have been widely used in many countries.\footnote{
-  Examples include the Unites States, the United Kingdom, Brazil, China, South Korea, and Japan.
+  Examples include the United States, the United Kingdom, Brazil, China, South Korea, and Japan.
 }
@@
 One such factor is temperature:
-heat on the exam days has been shown to affect exam results in high-stakes settings \citep{Park2020a, GraffZivin2020}.
+heat on exam days has been shown to affect exam results in high-stakes settings \citep{Park2020a, GraffZivin2020}.
 What has been less studied in the literature is the impact of \textit{low} temperature.\footnote{
-  One might think that, considering the on-going global \textit{warming}, the effect of low temperature is becoming less important.
-  However, the future climate change can cause the sea-ice loss, which could result in the cold winters with severely low temperatures \citep{Kretschmer2016, Kim2014}.
+  One might think that, considering the ongoing global \textit{warming}, the effect of low temperature is becoming less important.
+  However, future climate change can cause sea-ice loss, which could result in the cold winters with severely low temperatures \citep{Kretschmer2016, Kim2014}.
   Hence, it is important to understand how low temperature can affect our economies and lives.
@@
 }
-This creates a variation in weathers to which they are exposed on the exam dates.
+This creates a variation in weather to which they are exposed on the exam dates.
 
-I use the weather on the dates of Center Test and investigate its effect on matriculation for the University of Tokyo (UTokyo henceforth).
-UTokyo is a national university and known to be the most prestigious in Japan.\footnote{
+I use the weather on the dates of the Center Test and investigate its effect on matriculation for the University of Tokyo (UTokyo henceforth).
+UTokyo is a national university known to be the most prestigious in Japan.\footnote{
   According to \citet{usnews}, UTokyo is the highest-ranked university in Japan (73rd ranked in the world ranking).
@@
 }
-This allows me to attribute a reduction in matriculation shares to the worse exam performance, instead of the better performance which could induce students to choose better universities.
+This allows me to attribute a reduction in matriculation shares to the worse exam performance, instead of the better performance, which could induce students to choose better universities.
 
@@
 The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
-These include preparing waiting rooms for exam takers to warm up for equalizing their pre-exam conditions or adjusting the importance of the scores at Center Test in the admissions process.
+These include preparing waiting rooms for exam takers to warm up to equalize their pre-exam conditions or adjusting the importance of the scores at the Center Test in the admissions process.
 
-This study mainly contributes to the recent but growing literature of the effects of climate factors on the outcome of high-stakes exams.
+This study mainly contributes to the recent but growing literature on the effects of climate factors on the outcome of high-stakes exams.
 Several previous studies have found the adverse effect of high temperature on learning, which exacerbates performance at exams \citep{Park2020b, Cho2017}.
@@
 However, evidence based on data in the field is scarce.
-Country-level studies have shown a non-linear effect of temperature on economic growth, that is, both low and high temperature has a negative impact \citep{Burke2015}.
+Country-level studies have shown a non-linear effect of temperature on economic growth, that is, both low and high temperature have a negative impact \citep{Burke2015}.
 One study based on microdata is \citet{Stevens2017}, who finds a negative impact of low temperature on labor productivity of blueberry pickers in California.
-I use prefecture-level information to investigate how low temperature affects the cognitive performance in a high-stakes exam.
+I use prefecture-level information to investigate how low temperature affects cognitive performance in a high-stakes exam.
 
@@
 In Japan, for admission to public universities, students are usually required to take two exams.
-The first-stage test is Center Test.
+The first-stage test is the Center Test.
 Students take an exam on two consecutive days (Saturday and Sunday) in mid-January.
@@
   Also, several municipalities in a prefecture can be sometimes considered to be a part of a neighboring prefecture.
-  For instance, students in a couple of municipalities in Saitama prefecture could take Center Test in Tokyo.
+  For instance, students in a couple of municipalities in Saitama prefecture could take the Center Test in Tokyo.
 } where their high schools are located.
 On the other hand, high-school graduates are assigned to test sites in the exam area where the homes used in their applications are located.\footnote{
-  \citet{Watanabe2013} provides detailed descriptions on the administrations of Center Test.
+  \citet{Watanabe2013} provides detailed descriptions of the administrations of the Center Test.
 }
@@
 
-After Center Test, applicants for public universities typically take the second-stage exam.
+After the Center Test, applicants for public universities typically take the second-stage exam.
 This exam is made by each university, and students physically go to the universities and take the exam.
@@
 UTokyo has the second-stage exam at the end of February for two days.\footnote{
-  Until 2015, UTokyo had another second-stage exam in March and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
-  In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test (around 2\% of all admitted students).
+  Until 2015, UTokyo had another second-stage exam in March, and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
+  In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at the Center Test (around 2\% of all admitted students).
   Since the majority of students are admitted through the second-stage exam in February, below I focus on the admissions process for those students. 
@@
 
-In admission for UTokyo, scores at Center Test are used for two purposes.
+In admission for UTokyo, scores at the Center Test are used for two purposes.
 First, the scores are used for eligibility to take the second-stage exam.
-Thresholds varying across years and majors are set, and if scores at Center Test are below the thresholds, the students cannot take the second-stage exam.
-Secondly, the scores at Center Test are taken into consideration for admission.
+Thresholds varying across years and majors are set, and if scores at the Center Test are below the thresholds, the students cannot take the second-stage exam.
+Secondly, the scores at the Center Test are taken into consideration for admission.
 The final score of a student is calculated by the weighted sum of exam scores at the first- and second-stage exams.\footnote{
-  In 2020, the weights for Center Test and the second-stage exam are 20\% and 80\%.
-  Faculty of Medicine additionally conducts interviews on the next day of the second-stage exam to screen applicants based on community skills and personal maturity.
+  In 2020, the weights for the Center Test and the second-stage exam are 20\% and 80\%.
+  The Faculty of Medicine additionally conducts interviews on the next day of the second-stage exam to screen applicants based on community skills and personal maturity.
 }
 
-In summary, results at Center Test are crucial for applicants for UTokyo.
-This study will investigate how external factors such as temperature and weather on the dates of Center Test affect matriculation for UTokyo.
+In summary, results at the Center Test are crucial for applicants for UTokyo.
+This study will investigate how external factors such as temperature and weather on the dates of the Center Test affect matriculation for UTokyo.
 
@@
 Their website maintains the past weather across Japan.
-Based on hourly weather on exam dates at prefecture capitals, I use average weather between 6 AM to 6 PM.
-Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
+Based on hourly weather on exam dates in prefecture capitals, I use average weather between 6 AM and 6 PM.
+Prefecture capitals tend to be the most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located in prefecture capitals.
 
@@
       The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
   \end{tablenotes}
@@
       The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      Average of the shares across years is shown in the map.
-      Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
+      The average of the shares across the years is shown in the map.
+      Although not shown in the legend due to the lack of space, the lightest color in the map means the matriculation share between 0 and 0.5\%.
       The darkest prefecture in the east part of Japan is Tokyo.
@@
 }
-Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse performance at Center Test.
+Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse performance at the Center Test.
 
@@
   This can bring up a concern that temperature \textit{deviations} from the prefecture average have limited variations within each year.
-  If this was the case, most variations for estimation would be absorbed by prefecture fixed effects and year fixed effects.
+  If this were the case, most variations for estimation would be absorbed by prefecture fixed effects and year fixed effects.
   Figure \ref{fig:temperature_diff_by_year} shows that, even within each year, the temperature deviations have large variations across prefectures.
@@
 
-One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take Center Test in the same municipality.
+One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take the Center Test in the same municipality.
 This means that, for such students, the weather at the exam sites is measured with errors.
-The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get into any university and retake Center Test next year in his home prefecture.
-In 2020, 38\% of the admitted students are high-school graduates.
+The primary reason for this to happen is that a senior student at a high school located in a prefecture different from his home prefecture fails to get into any university and retake the Center Test next year in his home prefecture.
+In 2020, 38\% of the admitted students were high school graduates.
 In the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
 Hence, if I use this number as an approximation for the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of students whose exam-date weather is measured with errors for the reason above as $0.38 * 0.039 = 1.5\%$.
-Given this small proportion of exam takers who are susceptible to the measurement error, I consider that the bias on the estimates is negligible.
-Another potential concern is that, as discussed in footnote \ref{footnote:prefecture}, students in several municipalities in a prefecture could take Center Test in a neighboring prefecture.
+Given this small proportion of exam takers who are susceptible to measurement error, I consider that the bias on the estimates is negligible.
+Another potential concern is that, as discussed in footnote \ref{footnote:prefecture}, students in several municipalities in a prefecture could take the Center Test in a neighboring prefecture.
 Since neighboring prefectures are geographically close, I consider that the magnitude of the measurement error is small.
@@
     \item Notes:
-      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
-      Average across two test days in each year is shown in the figure.
+      Temperature in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
+      The average across two test days in each year is shown in the figure.
       The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
@@
 While the point estimates for temperature are positive, which means matriculation shares are higher if an exam is held on warmer days, they are statistically insignificant. 
-This could due to the plateau effect of temperature above 6 $^o$C in Table \ref{tab:main_reg}.
+This could be due to the plateau effect of temperature above 6 $^o$C in Table \ref{tab:main_reg}.
 Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.
-Secondly, following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual Center Test affect the matriculation shares.
-The results in Table \ref{tab:reg_placebo_exam} show not only that the weather one year after Center Test has insignificant impacts on matriculation shares but also including the weather variables one year after Center Test barely changes the coefficients on contemporaneous weather variables.
+Secondly, following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual the Center Test affect the matriculation shares.
+The results in Table \ref{tab:reg_placebo_exam} show not only that the weather one year after the Center Test has insignificant impacts on matriculation shares but also including the weather variables one year after the Center Test barely changes the coefficients on contemporaneous weather variables.
 This indicates that the results in \ref{tab:main_reg} capture the effect of transitory shocks on the exam dates.
@@
       The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
       Temperature intervals do not contain the left ends.
@@
 Also, snowfall can prevent students from going to high schools or cram schools for studying.
-Due to serial correlation between the weather on exam dates and the weather days or weeks before the exam, my regression in Table \ref{tab:main_reg} could capture these effects.
+Due to the serial correlation between the weather on exam dates and the weather days or weeks before the exam, my regression in Table \ref{tab:main_reg} could capture these effects.
 To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
 The results in columns (1) and (2) in Table \ref{tab:reg_pre10} show statistically insignificant estimates for the temperature variables.
-Moreover, including the weather variables for 10 days before the exams barely changes the estimates on the weather variables on the exam dates (columns (3) and (4)).
+Moreover, including the weather variables for 10 days before the exams barely changes the estimates of the weather variables on the exam dates (columns (3) and (4)).
 These suggest that the negative impacts of low temperature found in Table \ref{tab:main_reg} are mainly caused by the temperature on exam dates rather than temperature before exams.
@@
 (ii) snowfall before the exams cumulates snow on the ground and students' performance is negatively affected by the cumulated snow on the exam dates.
-Including the weather variables on the exam dates, columns (3) and (4) show that only cumulated snow on exam dates has significant impact on the outcome.
+Including the weather variables on the exam dates, columns (3) and (4) show that only cumulated snow on exam dates has a significant impact on the outcome.
 This suggests that the second mechanism is dominant.
@@
       The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      For weather variables with "(exam dates)", I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-      For weather variables with "(previous 10 days)", I use their averages at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
+      For weather variables with "(exam dates)", I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
+      For weather variables with "(previous 10 days)", I use their averages in prefecture capitals between 10 days before and 1 day before the first day of the Center Test.
       Temperature intervals do not contain the left ends.
@@
 The results in this study have implications for the admissions process of universities.
-Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
+Recognizing the limitation of measuring students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
 Examples include extracurricular activities and personal statements, which are actively utilized in other countries such as the United States.
-Also, universities may adjust the weights for Center Test and the second-stage exam.
+Also, universities may adjust the weights for the Center Test and the second-stage exam.
 Since the second-stage exams are held at each university, all exam takers are exposed to similar environments.
@@
 \bibliography{todai}
-
-%\section{Figures}
-%
-%\begin{figure}[H]
-%  \centering
-%  \caption{Map of matriculation shares (\%)}
-%  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.png}
-%  \label{fig:admission_map}
-%  \footnotesize
-%  \begin{tablenotes}
-%    \item Notes:
-%      This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
-%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      Average of the shares across years is shown in the map.
-%      Although not shown in the legend due to the lack of the space, the lightest color in the map means the matriculation share between 0 to 0.5\% 
-%  \end{tablenotes}
-%\end{figure}
-%
-%\begin{figure}[H]
-%  \centering
-%  \caption{Average temperature on two exam dates in each prefecture each year}
-%  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
-%  \label{fig:temperature_diff}
-%  \footnotesize
-%  \begin{tablenotes}
-%    \item Notes:
-%      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
-%      Average across two test days in each year is shown in the figure.
-%      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
-%  \end{tablenotes}
-%\end{figure}
-%
-%\section{Tables}
-%
-%\begin{table}[H]
-%  \centering
-%  \caption{Summary Statistics}
-%  \resizebox{0.8\linewidth}{!}{
-%  \input{"../Output/tex/sum_stat.tex"}
-%  }
-%  \label{tab:sum_stat}
-%  \footnotesize
-%  \begin{tablenotes}
-%    \item 
-%      Notes:
-%      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
-%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-%  \end{tablenotes}
-%\end{table}
-%
-%\begin{table}[H]
-%  \center
-%  \caption{Regression: Matriculation share (\%) and weather on exam dates}
-%  \small
-%  \input{"../Output/tex/main_reg.tex"}
-%  \label{tab:main_reg}
-%  \small
-%  \begin{tablenotes}
-%    \item
-%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-%      Standard errors are clustered at the prefecture level.
-%  \end{tablenotes}
-%\end{table}
-%
-%\begin{table}[H]
-%  \center
-%  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
-%  \input{"../Output/tex/reg_pre10.tex"}
-%  \label{tab:reg_pre10}
-%  \small
-%  \begin{tablenotes}
-%    \item
-%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
-%      Standard errors are clustered at the prefecture level.
-%  \end{tablenotes}
-%\end{table}
 
@@
 \section{Appendix tables}\label{sec:appendix_table}
-
-%\begin{table}[H]
-%  \center
-%  \caption{Regression: Matriculation share (\%) and weather on exam dates by gender}
-%  \input{"../Output/tex/reg_by_gender.tex"}
-%  \label{tab:reg_by_gender}
-%  \small
-%  \begin{tablenotes}
-%    \item
-%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-%      Standard errors are clustered at the prefecture level.
-%  \end{tablenotes}
-%\end{table}
 
@@
       The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
+      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
       Standard errors are clustered at the prefecture level.
@@
       The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
-      I represent the contemporaneous weather variables with ``($t$)'' and the weather one year after Center Test with ``($t + 1$).''
+      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
+      I represent the contemporaneous weather variables with ``($t$)'' and the weather one year after the Center Test with ``($t + 1$).''
       Temperature intervals do not contain the left ends.
@@
     \item Notes:
-      Rainfall (mm) at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
+      Rainfall (mm) in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
       Average across two test days in each year is shown in the figure.
@@
     \item Notes:
-      Snowfall (m) at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
+      Snowfall (m) in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
       Average across two test days in each year is shown in the figure.
@@
     \item Notes:
-      Cumulated snow (m) at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
+      Cumulated snow (m) in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
       Average across two test days in each year is shown in the figure.
@@
     \item Notes:
-      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
+      Temperature in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
       Deviations of average temperatures across two test days from their within-prefecture means are shown in the figure by year.
@@
 
-%\begin{figure}[H]
-%  \centering
-%  \caption{Map of average temperature on two exam dates (average across years)}
-%  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_map.png}
-%  \label{fig:temperature_map}
-%  \footnotesize
-%  \begin{tablenotes}
-%    \item Notes:
-%      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
-%      Average of the temperatures across years is shown in the map.
-%  \end{tablenotes}
-%\end{figure}
-%
-%\begin{figure}[H]
-%  \centering
-%  \caption{Map of average cumulated snow (m) on two exam dates (average across years)}
-%  \includegraphics[width = 0.9\textwidth]{../Output/images/cum_snow_map.png}
-%  \label{fig:cum_snow_map}
-%  \footnotesize
-%  \begin{tablenotes}
-%    \item Notes:
-%      Cumulated snow (m) on the ground at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
-%      Average of the values across years is shown in the map.
-%  \end{tablenotes}
-%\end{figure}
-
 \end{document}

### 2023-10-26 Codes/R/Data_clean/run_all_cleaning.R

@@ -11,8 +11,9 @@ packages <- c(
 )
 pacman::p_load(packages, character.only = TRUE)
 
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
+args <- commandArgs(trailingOnly = TRUE)
+dropbox_dir <- args[1]
+git_dir <- args[2]
 
 # Download weather data
 # source(file.path(git_dir, "Codes/R/Data_clean/weather_download.R"))

### 2023-10-26 Codes/R/Regression/art_science_regression.R

@@ -1,74 +1,0 @@
-# Regression for humanity and science majors separately =====================
-
-res_1 <- felm(
-  admission_Arts_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_2 <- felm(
-  admission_Arts_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_3 <- felm(
-  admission_Sciences_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_4 <- felm(
-  admission_Sciences_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-list(res_1, res_2, res_3, res_4) %>% 
-  stargazer(
-    dep.var.labels = c("Matriculation share (\\%, Humanity)", "Matriculation share (\\%, Science)"),
-    covariate.labels = c(
-      "Temperature (\\degree C) $\\le$ 0",
-      "Temperature (\\degree C) $>$ 0, $\\le$ 3",
-      "Temperature (\\degree C) $>$ 6, $\\le$ 9",
-      "Temperature (\\degree C) $>$ 9",
-      "Rainfall (mm)",
-      "Snowfall (cm)",
-      "Cumulated snow (cm)",
-      "Cumulated snow $>$ 10 cm"
-    ),
-    title = "",
-    add.lines = list(
-      c("Prefecture FE", rep("Yes", 4)),
-      c("Year FE", rep("Yes", 4))
-    ),
-    type = "latex",
-    out = file.path(git_dir, "Output/tex/reg_by_major.tex"),
-    omit.stat = c("adj.rsq", "ser", "rsq"),
-    digits = 2,
-    float = FALSE
-  )
-
-# Non-linear regression figures ============
-
-walk2(
-  list(res_1, res_2),
-  seq(1, 2), 
-  ~ ggsave(
-    filename = file.path(git_dir, str_interp("Output/images/reg_major_${.y}.pdf")),
[…]

### 2023-10-26 Codes/R/Regression/gender_regression.R

@@ -1,76 +1,0 @@
-# Regression by male and female matriculations =====================
-
-res_1 <- felm(
-  admission_female_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_2 <- felm(
-  admission_female_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_3 <- felm(
-  admission_male_share ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_4 <- felm(
-  admission_male_share ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-list(res_1, res_2, res_3, res_4) %>% 
-  stargazer(
-    dep.var.labels = c("Matriculation share (\\%, female)", "Matriculation share (\\%, male)"),
-    covariate.labels = c(
-      "Temperature (\\degree C) $\\le$ 0",
-      "Temperature (\\degree C) $>$ 0, $\\le$ 3",
-      "Temperature (\\degree C) $>$ 6, $\\le$ 9",
-      "Temperature (\\degree C) $>$ 9",
-      "Rainfall (mm)",
-      "Snowfall (cm)",
-      "Cumulated snow (cm)",
-      "Cumulated snow $>$ 10 cm"
-    ),
-    title = "",
-    add.lines = list(
-      c("Prefecture FE", rep("Yes", 4)),
-      c("Year FE", rep("Yes", 4))
-    ),
-    type = "latex",
-    out = file.path(git_dir, "Output/tex/reg_by_gender.tex"),
-    omit.stat = c("adj.rsq", "ser", "rsq"),
-    digits = 2,
-    float = FALSE
-  )
-
-# Non-linear regression figures ============
-
-walk2(
-  list(res_1, res_2),
-  seq(1, 2), 
-  ~ ggsave(
-    filename = file.path(git_dir, str_interp("Output/images/reg_gender_${.y}.pdf")),
-    plot = make_coef_figure(.x, temp_cut_str = "^temp_cut"),
-    height = 6,
[…]

### 2023-10-26 Codes/R/Regression/linear_regression.R

@@ -1,48 +1,0 @@
-# Regression with linear specification ==========================
-
-res_1 <- felm(
-  admission_total_share ~ daytime_temperature_degree | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_2 <- felm(
-  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_snowfall_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_3 <- felm(
-  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + daytime_cum_snow_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_4 <- felm(
-  admission_total_share ~ daytime_temperature_degree + daytime_precipitation_mm + factor(daytime_cum_snow_m > .1) | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-list(res_1, res_2, res_3, res_4) %>% 
-  stargazer(
-    dep.var.labels = "Matriculation share (\\%)",
-    covariate.labels = c(
-      "Temperature (\\degree C)",
-      "Rainfall (mm)",
-      "Snowfall (cm)",
-      "Cumulated snow (cm)",
-      "Cumulated snow $>$ 10 cm"
-    ),
-    title = "",
-    add.lines = list(
-      c("Prefecture FE", rep("Yes", 8)),
-      c("Year FE", rep("Yes", 8))
-    ),
-    type = "latex",
-    out = file.path(git_dir, "Output/tex/linear_reg.tex"),
-    omit.stat = c("adj.rsq", "ser", "rsq"),
-    digits = 2,
-    float = FALSE
-  )
-

### 2023-10-26 Codes/R/Regression/main_regression.R

@@ -1,4 +1,5 @@
-# Main regression ==========================
+# Main regression
+# Table 2 -------------
 
 res_1 <- felm(
   admission_total_share ~ temp_cut |
@@ -75,15 +76,94 @@ list(res_2, res_3, res_4) %>%
     float = FALSE
   )
 
-# Non-linear regression figures ============
-walk2(
-  list(res_1, res_2, res_3, res_4),
-  c(1, 2, 3, 4), 
-  ~ ggsave(
-    filename = file.path(git_dir, str_interp("Output/images/main_reg_${.y}.pdf")),
-    plot = make_coef_figure(.x),
-    height = 6,
-    width = 6
-    )
+# Table 3 -------------
+# Regression with weather for the previous 10 days =====================
+
+res_1 <- felm(
+  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10 |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_2 <- felm(
+  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10 |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_3 <- felm(
+  admission_total_share ~ 
+    temp_cut + daytime_precipitation_mm + daytime_snowfall_cm +
+    temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10 |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_4 <- felm(
+  admission_total_share ~ 
+    temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm +
+    temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10 |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+list(res_1, res_2, res_3, res_4) %>% 
+  stargazer(
+    dep.var.labels = "Matriculation share (\\%)",
+    order = c(seq(1, 4), seq(5, 7), seq(8, 11), seq(12, 14)),
+    covariate.labels = c(
+      "Temperature (\\degree C) $\\le$ 0 (exam dates)",
+      "Temperature (\\degree C) 0-3 (exam dates)",
+      "Temperature (\\degree C) 6-9 (exam dates)",
+      "Temperature (\\degree C) $>$ 9 (exam dates)",
[…]

### 2023-10-26 Codes/R/Regression/morning_exam_regression.R

@@ -1,199 +1,0 @@
-# Main regression ==========================
-
-res_1 <- felm(
-  admission_total_share ~ temp_cut_morning + morning_precipitation_mm + morning_snowfall_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_2 <- felm(
-  admission_total_share ~ temp_cut_morning + morning_precipitation_mm + morning_cum_snow_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_3 <- felm(
-  admission_total_share ~ temp_cut_exam + exam_precipitation_mm + exam_snowfall_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_4 <- felm(
-  admission_total_share ~ temp_cut_exam + exam_precipitation_mm + exam_cum_snow_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_5 <- felm(
-  admission_total_share ~ 
-    temp_cut_morning + morning_precipitation_mm + morning_snowfall_cm +
-    temp_cut_exam + exam_precipitation_mm + exam_snowfall_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_6 <- felm(
-  admission_total_share ~ 
-    temp_cut_morning + morning_precipitation_mm + morning_cum_snow_cm +
-    temp_cut_exam + exam_precipitation_mm + exam_cum_snow_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-list(res_1, res_2, res_3, res_4, res_5, res_6) %>% 
-  stargazer(
-    dep.var.labels = "Matriculation share (\\%)",
-    covariate.labels = c(
-      "Temperature (\\degree C) $\\le$ -3 (morning)",
-      "Temperature (\\degree C) -3-0 (morning)",
-      "Temperature (\\degree C) 3-6 (morning)",
-      "Temperature (\\degree C) $>$ 6 (morning)",
-      "Rainfall (mm) (morning)",
-      "Snowfall (cm) (morning)",
-      "Cumulated snow (cm) (morning)",
-      "Temperature (\\degree C) $\\le$ -3 (during exam)",
[…]

### 2023-10-26 Codes/R/Regression/pre10_regression.R

@@ -1,114 +1,0 @@
-# Regression with weather for the previous 10 days =====================
-
-res_1 <- felm(
-  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10 |
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_2 <- felm(
-  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10 |
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_3 <- felm(
-  admission_total_share ~ 
-    temp_cut + daytime_precipitation_mm + daytime_snowfall_cm +
-    temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10 |
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_4 <- felm(
-  admission_total_share ~ 
-    temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm +
-    temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10 |
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-list(res_1, res_2, res_3, res_4) %>% 
-  stargazer(
-    dep.var.labels = "Matriculation share (\\%)",
-    order = c(seq(1, 4), seq(5, 7), seq(8, 11), seq(12, 14)),
-    covariate.labels = c(
-      "Temperature (\\degree C) $\\le$ 0 (exam dates)",
-      "Temperature (\\degree C) 0-3 (exam dates)",
-      "Temperature (\\degree C) 6-9 (exam dates)",
-      "Temperature (\\degree C) $>$ 9 (exam dates)",
-      "Rainfall (mm) (exam dates)",
-      "Snowfall (cm) (exam dates)",
-      "Cumulated snow (cm) (exam dates)",
-      "Temperature (\\degree C) $\\le$ 0 (previous 10 days)",
-      "Temperature (\\degree C) 0-3 (previous 10 days)",
-      "Temperature (\\degree C) 6-9 (previous 10 days)",
-      "Temperature (\\degree C) $>$ 9 (previous 10 days)",
-      "Rainfall (mm) (previous 10 days)",
-      "Snowfall (cm) (previous 10 days)",
-      "Cumulated snow (cm) (previous 10 days)"
-    ),
[…]

### 2023-10-26 Codes/R/Regression/run_all_regression.R

@@ -10,11 +10,12 @@ packages <- c(
 )
 pacman::p_load(packages, character.only = TRUE)
 
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
+args <- commandArgs(trailingOnly = TRUE)
+dropbox_dir <- args[1]
+git_dir <- args[2]
 
 # Load regression data =================
-reg_df <- readRDS(file.path(dropbox_dir, "Data/temp/data_regression.rds"))
+reg_df <- readRDS(file.path(dropbox_dir, "Data/Processed/data_regression.rds"))
 
 # Import function to make estimate figures
 source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
@@ -22,23 +23,5 @@ source(file.path(git_dir, "Codes/R/Regression/make_coef_figure.R"))
 # Main regression
 source(file.path(git_dir, "Codes/R/Regression/main_regression.R"))
 
-# Placebo regression
-source(file.path(git_dir, "Codes/R/Regression/placebo_regression.R"))
-
-# Regression with weather for the previous 10 days
-source(file.path(git_dir, "Codes/R/Regression/pre10_regression.R"))
-
-# Linear regression
-source(file.path(git_dir, "Codes/R/Regression/linear_regression.R"))
-
-# Regression by gender
-source(file.path(git_dir, "Codes/R/Regression/gender_regression.R"))
-
-# Regression by major
-source(file.path(git_dir, "Codes/R/Regression/art_science_regression.R"))
-
-# Regression (morning vs. during exam)
-source(file.path(git_dir, "Codes/R/Regression/morning_exam_regression.R"))
-
-
-
+# Appendix regression
+source(file.path(git_dir, "Codes/R/Regression/appendix_regression.R"))

### 2023-10-26 Codes/R/Regression/share_per_pop_regression.R

@@ -1,507 +1,0 @@
-# Regression with matriculation per population (million) ==========================
-
-res_1 <- felm(
-  admission_per_pop ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_2 <- felm(
-  admission_per_pop ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_3 <- felm(
-  admission_per_pop_15_19 ~ temp_cut + daytime_precipitation_mm + daytime_snowfall_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_4 <- felm(
-  admission_per_pop_15_19 ~ temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm | 
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-list(res_1, res_2, res_3, res_4) %>% 
-  stargazer(
-    dep.var.labels = "Matriculation per population (million)",
-    column.labels = c(rep("Total", 2), rep("15-19", 2)),
-    covariate.labels = c(
-      "Temperature (\\degree C) $\\le$ 0",
-      "Temperature (\\degree C) 0-3",
-      "Temperature (\\degree C) 6-9",
-      "Temperature (\\degree C) $>$ 9",
-      "Rainfall (mm)",
-      "Snowfall (cm)",
-      "Cumulated snow (cm)",
-      "Cumulated snow $>$ 10 cm"
-    ),
-    title = "",
-    add.lines = list(
-      c("Prefecture FE", rep("Yes", 8)),
-      c("Year FE", rep("Yes", 8))
-    ),
-    type = "latex",
-    out = file.path(git_dir, "Output/tex/per_pop_reg.tex"),
-    omit.stat = c("adj.rsq", "ser", "rsq"),
-    digits = 2,
-    float = FALSE
-  )
-
-# Non-linear regression figures ============
-walk2(
-  list(res_1, res_2),
-  c(1, 2), 
-  ~ ggsave(
-    filename = file.path(git_dir, str_interp("Output/images/per_pop_reg_${.y}.pdf")),
-    plot = make_coef_figure(.x, ylim_lb = -10, ylim_ub = 10),
-    height = 6,
-    width = 6
-    )
-  )
-
[…]

### 2023-10-26 Codes/R/SumStat/run_all_sumstat.R

@@ -1,0 +1,29 @@
+packages <- c(
+  "tidyverse",
+  "curl",
+  "rvest",
+  "magrittr",
+  "lubridate",
+  "readxl",
+  "lfe",
+  "kableExtra",
+  "raster",
+  "RColorBrewer",
+  "gridExtra",
+  "grid",
+  "stargazer"
+)
+pacman::p_load(packages, character.only = TRUE)
+
+args <- commandArgs(trailingOnly = TRUE)
+dropbox_dir <- args[1]
+git_dir <- args[2]
+
+# Summary statistics table
+source(file.path(git_dir, "Codes/R/SumStat/sumstat.R"))
+
+# Admission map
+source(file.path(git_dir, "Codes/R/SumStat/admission_map.R"))
+
+# Weather difference
+source(file.path(git_dir, "Codes/R/SumStat/weather_diff.R"))

### 2023-10-26 Codes/R/SumStat/weather_diff.R

@@ -1,27 +1,8 @@
-packages <- c(
-  "tidyverse",
-  "curl",
-  "rvest",
-  "magrittr",
-  "lubridate",
-  "readxl",
-  "grid",
-  "gridExtra",
-  "cowplot",
-  "lfe",
-  "stargazer",
-  "kableExtra"
-)
-pacman::p_load(packages, character.only = TRUE)
-
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
-
 # Load weather information =================
-weather_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_on_exam_day.csv"))
+weather_df <- read_csv(file.path(dropbox_dir, "Data/Processed/weather_on_exam_day.csv"))
 
 # Load location information
-loc_df <- read_delim(file.path(dropbox_dir, "Data/weather_station_id.txt"), delim = ",")
+loc_df <- read_delim(file.path(dropbox_dir, "Data/Raw/weather_station/weather_station_id.txt"), delim = ",")
 prefecture_order <- loc_df$prefecture
 
 weather_df_avg <- weather_df %>% 

### 2023-10-26 Codes/R/SumStat/weather_map.R

@@ -1,99 +1,0 @@
-packages <- c(
-  "rgdal",
-  "sp",
-  "raster",
-  "tidyverse",
-  "curl",
-  "rvest",
-  "magrittr",
-  "lubridate",
-  "readxl",
-  "lfe",
-  "stargazer",
-  "RColorBrewer",
-  "kableExtra"
-)
-pacman::p_load(packages, character.only = TRUE)
-
-dropbox_dir <- "~/Dropbox/todai_center/"
-git_dir <- "~/Documents/GitHub/todai_center/"
-
-# Load weather information =================
-weather_df <- read_csv(file.path(dropbox_dir, "Data/temp/weather_on_exam_day.csv"))
-
-# Draw map of average temperature  ===============
-
-map_Japan <- shapefile(
-  file.path(
-    dropbox_dir,
-    "Data/shapefile",
-    "jpn_admbnda_adm0_2019.shp"
-  )
-)
-map <- shapefile(
-  file.path(
-    dropbox_dir,
-    "Data/shapefile",
-    "jpn_admbnda_adm1_2019.shp"
-  )
-)
-
-weather_df_avg <- weather_df %>% 
-  mutate(daytime_cum_snow_cm = daytime_cum_snow_cm / 100) %>% 
-  group_by(prefecture) %>% 
-  summarise_at(vars(daytime_temperature_degree, daytime_cum_snow_cm), mean)
-
-map@data$ADM1_JA <- str_replace(map@data$ADM1_JA, "県|府", "")
-map@data$ADM1_JA <- str_replace(map@data$ADM1_JA, "東京都", "東京")
-
-map_avg <- merge(map, weather_df_avg, by.x = "ADM1_JA", by.y = "prefecture")
-
-# Average temperature -------------------
-
-filepath = file.path(git_dir, 'Output/images/temperature_map.png')
-png(file = filepath)
-print(
-  spplot(
-    map_avg, 
-    "daytime_temperature_degree", 
-    sp.layout = list(map_Japan, lwd = 0.1), 
-    col.regions = brewer.pal(n = 7, name = "OrRd"),
-    # cuts = 6,
-    at = seq(-5, 20, 5),
-    par.settings = list(axis.line = list(col = "transparent")),
-    colorkey = list(
-      labels = list(
-        at = seq(-5, 20, 5),
-        labels = as.character(seq(-5, 20, 5)),
-        cex = 1.0
-      )
-    ),
-    col = "transparent"
-  )
-)
[…]

### 2023-12-11 Writeups/title.tex

--- 2023-10-26 Writeups/paper.tex
@@
     Any errors are the sole responsibility of the author.
+    The author declares that he has no relevant or material financial interests that relate to the research described in this paper.
+  }\\Capital One
 }
-}
-\date{\today}
+\date{}
 
@@
 \maketitle
-\begin{abstract}
-  \singlespacing
-    \noindent 
-    Whereas there are growing numbers of studies on how heat affects cognitive performance at high-stakes settings, the effect of cold weather has been less studied.
-    To fill this gap, I analyze the effects of winter weather on exam dates on performance at the centralized exam for university admission in Japan.
-    Since students take the exam in their own prefectures, they are exposed to different weather conditions on the exam dates. 
-    I find that low temperature and snow cumulated on the ground reduce matriculation shares for the most prestigious university in Japan, the University of Tokyo.
-    This result suggests that the winter weather on exam dates worsens exam performance.
-
-  \medskip
-  \vspace{1cm}
-  \noindent Keywords: Temperature, Education, University matriculation, Cognitive performance
-\end{abstract}
-
-\newpage
-
-\section{Introduction}
-
-University admission is an important step in life and can have consequences in later-life outcomes such as job occupation and earnings.\footnote{
-  \citet{Hout2012} reviews the returns to college education in the context of the United States.
-}
-For admission selection, standardized exams have been widely used in many countries.\footnote{
-  Examples include the United States, the United Kingdom, Brazil, China, South Korea, and Japan.
-}
-Given the importance, the results of the exams are expected to evaluate the exam takers' ability and knowledge correctly and are not supposed to be affected by seemingly irrelevant factors.
-However, recent studies have shown that exam performance is sensitive to external factors.
-One such factor is temperature:
-heat on exam days has been shown to affect exam results in high-stakes settings \citep{Park2020a, GraffZivin2020}.
-What has been less studied in the literature is the impact of \textit{low} temperature.\footnote{
-  One might think that, considering the ongoing global \textit{warming}, the effect of low temperature is becoming less important.
-  However, future climate change can cause sea-ice loss, which could result in the cold winters with severely low temperatures \citep{Kretschmer2016, Kim2014}.
-  Hence, it is important to understand how low temperature can affect our economies and lives.
-}
-
-To fill this gap in the literature, this study analyzes the effect of winter weather on exam outcomes in Japan.
-For admission, most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth).
-Students take the exam on the same dates in mid-January in their prefectures.\footnote{
-  There are 47 prefectures in Japan.
-}
-This creates a variation in weather to which they are exposed on the exam dates.
-
-I use the weather on the dates of the Center Test and investigate its effect on matriculation for the University of Tokyo (UTokyo henceforth).
-UTokyo is a national university known to be the most prestigious in Japan.\footnote{
-  According to \citet{usnews}, UTokyo is the highest-ranked university in Japan (73rd ranked in the world ranking).
-  The second highest-ranked university in Japan is Kyoto University, which is 125th ranked in the world ranking.
-}
-This allows me to attribute a reduction in matriculation shares to the worse exam performance, instead of the better performance, which could induce students to choose better universities.
-
-The econometric analyses show that low temperature and snow cumulated on the ground on exam dates reduce the matriculation share.
-The estimates are not only statistically but also economically significant.
-Changing the temperature on the exam dates from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
-The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
-These include preparing waiting rooms for exam takers to warm up to equalize their pre-exam conditions or adjusting the importance of the scores at the Center Test in the admissions process.
-
-This study mainly contributes to the recent but growing literature on the effects of climate factors on the outcome of high-stakes exams.
-Several previous studies have found the adverse effect of high temperature on learning, which exacerbates performance at exams \citep{Park2020b, Cho2017}.
-More closely to my study, \citet{GraffZivin2020} and \citet{Park2020a} show that heat on exam dates decreases the scores at high-stakes exams in China and the U.S., respectively.
-Considering the importance of the exam results for later life outcomes, it is important to understand how external factors such as temperature affect exam performance and what can be done to ameliorate such effects.
-To complement the literature, I investigate the effect of \textit{low} temperature on exam performance.
-
-This study also has a contribution to the literature on the economic impact of low temperature.
-It has been shown with controlled experiments that cold stresses negatively affect such things as cognitive ability and memory, as reviewed in \citet{Taylor2016}.
-However, evidence based on data in the field is scarce.
-Country-level studies have shown a non-linear effect of temperature on economic growth, that is, both low and high temperature have a negative impact \citep{Burke2015}.
-One study based on microdata is \citet{Stevens2017}, who finds a negative impact of low temperature on labor productivity of blueberry pickers in California.
-I use prefecture-level information to investigate how low temperature affects cognitive performance in a high-stakes exam.
-
-This study proceeds as follows.
-In Section \ref{sec:background}, the context of this study is introduced.
-Section \ref{sec:data} describes the data. 
-I introduce my empirical strategy in Section \ref{sec:empirical_strategy}.
-In Section \ref{sec:results}, I present the empirical results, and Section \ref{sec:conclusion} concludes.
-
-\section{Background}\label{sec:background}
-
-In Japan, for admission to public universities, students are usually required to take two exams.
-The first-stage test is the Center Test.
-Students take an exam on two consecutive days (Saturday and Sunday) in mid-January.
-Most public universities, including UTokyo, require students to take exams on social science, Japanese, and English on the first day and mathematics and natural science on the second day.
-The exams start at 9:30 AM on both days and end at 6:10 PM on the first day and 5:50 PM on the second day.
-Questions are multiple-choice and common for all exam takers across Japan.
-High-school seniors take the test at designated sites in the exam area\footnote{ \label{footnote:prefecture}
-  Typically, an exam area coincides with a prefecture (i.e. there is one exam area in one prefecture).
-  Large prefectures such as Hokkaido and Okinawa have several exam areas.
-  Also, several municipalities in a prefecture can be sometimes considered to be a part of a neighboring prefecture.
-  For instance, students in a couple of municipalities in Saitama prefecture could take the Center Test in Tokyo.
-} where their high schools are located.
-On the other hand, high-school graduates are assigned to test sites in the exam area where the homes used in their applications are located.\footnote{
-  \citet{Watanabe2013} provides detailed descriptions of the administrations of the Center Test.
-}
-
-Since January is the middle of winter in Japan, heavy snow can affect public transportation on exam dates.
-This sometimes makes it difficult for exam takers to arrive at exam sites on time.
-For the affected students, the following accommodations can be provided:
-(i) delaying the start of exams by a few hours for all exam takers at a test site,
-(ii) allowing the affected students to take exams in a separate room, and
-(iii) allowing the affected students to take make-up exams a week later.
-These accommodations can be given to students who could not take exams for other reasons such as sickness or accidents.
-
-After the Center Test, applicants for public universities typically take the second-stage exam.
-This exam is made by each university, and students physically go to the universities and take the exam.
-Therefore, every applicant for a university takes the second-stage exam at the same location on the same days.
-UTokyo has the second-stage exam at the end of February for two days.\footnote{
-  Until 2015, UTokyo had another second-stage exam in March, and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
-  In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at the Center Test (around 2\% of all admitted students).
-  Since the majority of students are admitted through the second-stage exam in February, below I focus on the admissions process for those students. 
-}
-
-In admission for UTokyo, scores at the Center Test are used for two purposes.
-First, the scores are used for eligibility to take the second-stage exam.
-Thresholds varying across years and majors are set, and if scores at the Center Test are below the thresholds, the students cannot take the second-stage exam.
-Secondly, the scores at the Center Test are taken into consideration for admission.
-The final score of a student is calculated by the weighted sum of exam scores at the first- and second-stage exams.\footnote{
-  In 2020, the weights for the Center Test and the second-stage exam are 20\% and 80\%.
-  The Faculty of Medicine additionally conducts interviews on the next day of the second-stage exam to screen applicants based on community skills and personal maturity.
-}
-
-In summary, results at the Center Test are crucial for applicants for UTokyo.
-This study will investigate how external factors such as temperature and weather on the dates of the Center Test affect matriculation for UTokyo.
-
-\section{Data}\label{sec:data}
-
-I use two sets of data: weather and matriculation for UTokyo.
-For weather information, I obtain data from \Citeauthor{jma}.
-Their website maintains the past weather across Japan.
-Based on hourly weather on exam dates in prefecture capitals, I use average weather between 6 AM and 6 PM.
-Prefecture capitals tend to be the most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located in prefecture capitals.
-
-For matriculation information for UTokyo, I use University Basic Information by \Citeauthor{univ_info}.
-This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
-I calculate the matriculation shares of each prefecture as the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
-  Due to the lack of information on the number of admitted students by prefecture, I use the information on matriculation.
-  For UTokyo, the number of admissions and the number of matriculations are very close:
-  In 2020, among 3,083 admitted students, 3,064 students matriculated at UTokyo.
-}
-
-The summary statistics are provided in Table \ref{tab:sum_stat}.
-Whereas the mean matriculation share is $2.08 \%$, the median share is much smaller ($0.79 \%$).\footnote{
-  Since there are matriculations from foreign high schools, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
-  I do not consider matriculations of students from foreign high schools in the analyses since the majority of the students are admitted through a process called Special Screening Tests, which does not require Center Test scores.
-}
-This is because the distribution of the matriculation share is starkly skewed:
-while the matriculation shares of the top 5 prefectures amount to more than 60\%, many prefectures have less than 1\% shares (Figure \ref{fig:admission_map}).
-
-\begin{table}[H]
-  \centering
-  \caption{Summary Statistics}
-  \resizebox{0.8\linewidth}{!}{
-  \input{"../Output/tex/sum_stat.tex"}
-  }
-  \label{tab:sum_stat}
-  \footnotesize
-  \begin{tablenotes}
-    \item 
-      Notes:
-      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
-  \end{tablenotes}
-\end{table}
-
-\begin{figure}[H]
-  \centering
-  \caption{Map of matriculation shares (\%)}
-  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.pdf}
-  \label{fig:admission_map}
-  \footnotesize
-  \begin{tablenotes}
-    \item Notes:
-      This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      The average of the shares across the years is shown in the map.
-      Although not shown in the legend due to the lack of space, the lightest color in the map means the matriculation share between 0 and 0.5\%.
-      The darkest prefecture in the east part of Japan is Tokyo.
-  \end{tablenotes}
-\end{figure}
-
-\section{Empirical Strategy}\label{sec:empirical_strategy}
-
-I analyze the effect of temperature and other weather variables on exam dates on the matriculation share for UTokyo.
-The reason why I use the matriculation share for UTokyo is as follows:
-consider a matriculation share for a middle-ranked university.
-Suppose also that low temperature has a negative impact on exam scores.
-Then, 
-(i) students in the prefecture who would have gotten into the middle-ranked university if the temperature were higher may end up in a lower-ranked university instead, but
-(ii) students in the prefecture who would have gotten into a higher-ranked university may end up in the middle-ranked university instead.
-Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
-However, the second effect is unlikely to be large for UTokyo since it is known to be the best university in Japan.\footnote{
-  \citet{Kawaguchi2008} describes that ``The University of Tokyo has occupied the top position of the single-peaked university hierarchy since its establishment in 1877.''
-}
-Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse performance at the Center Test.
-
-In the analyses, the outcome variable, $Y_{jt}$, is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
-%Let $T_{jt}$ be the average temperature across two exam dates in $j$ in year $t$.
-%I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
-The main right-hand side variable is temperature on the exam dates.
-To allow for non-linear effects of temperature on the outcome, I use the 3-$^o$C temperature intervals.\footnote{
-  The results with a linear specification are shown in Appendix \ref{sec:appendix_table} and will be discussed below.
-}
-Let $T_{jt}^k$ represent the $k$'th temperature bin.
-I also include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates as a vector $X_{jt}$.
-As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
-Finally, the error term is represented as $\epsilon_{jt}$.
-
-Given the above notation, I run the following regression equation:
-\begin{equation*}
-  Y_{jt} = \sum_k T_{jt}^k + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
-\end{equation*}
-I exploit the variation of temperature on exam dates, which I consider exogenous after controlling for prefecture-specific time-invariant factors and time-varying aggregate shocks through prefecture and year fixed effects.
-As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam dates.\footnote{
-  Figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
-}$^,$\footnote{
-  The figure shows that temperature is low for most prefectures in some years (eg. 2017) and high in other years (eg. 2019).
-  This can bring up a concern that temperature \textit{deviations} from the prefecture average have limited variations within each year.
-  If this were the case, most variations for estimation would be absorbed by prefecture fixed effects and year fixed effects.
-  Figure \ref{fig:temperature_diff_by_year} shows that, even within each year, the temperature deviations have large variations across prefectures.
-}
-
-One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take the Center Test in the same municipality.
-This means that, for such students, the weather at the exam sites is measured with errors.
-The primary reason for this to happen is that a senior student at a high school located in a prefecture different from his home prefecture fails to get into any university and retake the Center Test next year in his home prefecture.
-In 2020, 38\% of the admitted students were high school graduates.
-In the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
-Hence, if I use this number as an approximation for the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of students whose exam-date weather is measured with errors for the reason above as $0.38 * 0.039 = 1.5\%$.
-Given this small proportion of exam takers who are susceptible to measurement error, I consider that the bias on the estimates is negligible.
-Another potential concern is that, as discussed in footnote \ref{footnote:prefecture}, students in several municipalities in a prefecture could take the Center Test in a neighboring prefecture.
-Since neighboring prefectures are geographically close, I consider that the magnitude of the measurement error is small.
-
-\begin{figure}[H]
-  \centering
-  \caption{Average temperature (\degree C) on two exam dates in each prefecture each year}
-  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
-  \label{fig:temperature_diff}
-  \footnotesize
-  \begin{tablenotes}
-    \item Notes:
-      Temperature in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
-      The average across two test days in each year is shown in the figure.
-      The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
-  \end{tablenotes}
-\end{figure}
-
-\section{Results}\label{sec:results}
-
-The main empirical results are provided in Table \ref{tab:main_reg}.
-The standard errors are clustered at the prefecture level.
-Without other weather variables, the estimates in column (1) show a negative and statistically significant impact of cold weather.
-Since the mean matriculation share is $2.08$\%, a decrease in the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest temperature bin (below 0 $^o$C) results in the lower matriculation share by 9\%.
-Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$\%.
-Therefore, the same temperature change decreases the matriculation share by 22\% of the median value.
-
-In column (2), I add rainfall and snowfall in the regressions.
-While temperature coefficients are barely affected, I find that rainfall and snowfall on the exam dates do not impact the matriculation shares.
-In column (3), instead of snowfall on the exam dates, I use cumulated snow on the ground and find its negative impact on the outcome. 
-To capture the effect of the existence of a certain amount of snow on the ground, column (4) allows a non-linear effect of cumulated snow.
-The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage points.
-These results suggest that not only temperature but also snow on the ground on the exam dates affect exam performance.
-
-Two points are worth noting.
-First, Table \ref{tab:linear_reg} shows the results with linear specifications.
-While the point estimates for temperature are positive, which means matriculation shares are higher if an exam is held on warmer days, they are statistically insignificant. 
-This could be due to the plateau effect of temperature above 6 $^o$C in Table \ref{tab:main_reg}.
-Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.
-Secondly, following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual the Center Test affect the matriculation shares.
-The results in Table \ref{tab:reg_placebo_exam} show not only that the weather one year after the Center Test has insignificant impacts on matriculation shares but also including the weather variables one year after the Center Test barely changes the coefficients on contemporaneous weather variables.
-This indicates that the results in \ref{tab:main_reg} capture the effect of transitory shocks on the exam dates.
-
-\begin{table}[H]
-  \center
-  \caption{Regression: Matriculation share (\%) and weather on exam dates}
-  \footnotesize
-  \input{"../Output/tex/main_reg.tex"}
-  \label{tab:main_reg}
-  \small
-  \begin{tablenotes}
-    \item
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
-      Temperature intervals do not contain the left ends.
-      Standard errors are clustered at the prefecture level.
-  \end{tablenotes}
-\end{table}
-
-One possible interpretation of the results is that the estimates in Table \ref{tab:main_reg} reflect the effects of weather on preparation for the exam.
-For instance, cold weather can make it hard for students to focus on studying, as suggested by existing studies \citep{Taylor2016}.
-Also, snowfall can prevent students from going to high schools or cram schools for studying.
-Due to the serial correlation between the weather on exam dates and the weather days or weeks before the exam, my regression in Table \ref{tab:main_reg} could capture these effects.
-To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
-The results in columns (1) and (2) in Table \ref{tab:reg_pre10} show statistically insignificant estimates for the temperature variables.
-Moreover, including the weather variables for 10 days before the exams barely changes the estimates of the weather variables on the exam dates (columns (3) and (4)).
-These suggest that the negative impacts of low temperature found in Table \ref{tab:main_reg} are mainly caused by the temperature on exam dates rather than temperature before exams.
-
-In columns (1) and (2), the coefficients on snowfall and cumulated snow on the ground are statistically significant.
-Combined with the finding in Table \ref{tab:main_reg} that cumulated snow on the ground on the exam dates decreases students' performance, two potential explanations can be given:
-(i) snow before the exams can adversely affect students' preparation due to, for instance, more difficulty in going to high schools or cram schools, and
-(ii) snowfall before the exams cumulates snow on the ground and students' performance is negatively affected by the cumulated snow on the exam dates.
-Including the weather variables on the exam dates, columns (3) and (4) show that only cumulated snow on exam dates has a significant impact on the outcome.
-This suggests that the second mechanism is dominant.
-
-\begin{table}[H]
-  \center
-  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
-  \scriptsize
-  \input{"../Output/tex/reg_pre10.tex"}
-  \label{tab:reg_pre10}
-  \scriptsize
-  \begin{tablenotes}
-    \item
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      For weather variables with "(exam dates)", I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
-      For weather variables with "(previous 10 days)", I use their averages in prefecture capitals between 10 days before and 1 day before the first day of the Center Test.
-      Temperature intervals do not contain the left ends.
-      Standard errors are clustered at the prefecture level.
-  \end{tablenotes}
-\end{table}
-
-\section{Conclusion}\label{sec:conclusion}
-
-This paper studies the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
-I use the matriculation share for the most prestigious university in Japan, the University of Tokyo, as an outcome.
-Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
-This study fills the gap by identifying the causal impact of winter weather on exam results.
-
-The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam dates.
-Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage points, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
-Moreover, having more than 10cm of snow on the ground decreases the share by 0.11 percentage points.
-
-The results in this study have implications for the admissions process of universities.
-Recognizing the limitation of measuring students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
-Examples include extracurricular activities and personal statements, which are actively utilized in other countries such as the United States.
-Also, universities may adjust the weights for the Center Test and the second-stage exam.
-Since the second-stage exams are held at each university, all exam takers are exposed to similar environments.
-This rules out the possibility that exam takers at different places are affected differently by their conditions.
-Given the importance of exam results for later life outcomes of students, it is desirable that universities take measures to mitigate the effect of seemingly irrelevant factors on admission.
-
-\clearpage
-\bibliographystyle{apalike}
-\bibliography{todai}
-
-\appendix
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-\renewcommand\thefigure{\Alph{section}.\arabic{figure}}
-\renewcommand\thetable{\Alph{section}.\arabic{table}}
-
-\section{Appendix tables}\label{sec:appendix_table}
-
-\begin{table}[H]
-  \center
-  \caption{Regression: Matriculation share (\%) and weather on exam dates (linear specification)}
-  \small
-  \input{"../Output/tex/linear_reg.tex"}
-  \label{tab:linear_reg}
-  \small
-  \begin{tablenotes}
-    \item
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
-      Standard errors are clustered at the prefecture level.
-  \end{tablenotes}
-\end{table}
-
-\begin{table}[H]
-  \center
-  \caption{Falsification test: Matriculation share (\%) and weather on exam dates and one year after}
-  \scriptsize
-  \input{"../Output/tex/reg_placebo_exam.tex"}
-  \label{tab:reg_placebo_exam}
-  \scriptsize
-  \begin{tablenotes}
-    \item
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
-      I represent the contemporaneous weather variables with ``($t$)'' and the weather one year after the Center Test with ``($t + 1$).''
-      Temperature intervals do not contain the left ends.
-      Standard errors are clustered at the prefecture level.
-  \end{tablenotes}
-\end{table}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-\renewcommand\thefigure{\Alph{section}.\arabic{figure}}
-\renewcommand\thetable{\Alph{section}.\arabic{table}}
-
-\section{Appendix figures}\label{sec:appendix_figure}
-
-\begin{figure}[H]
-  \centering
-  \caption{Average hourly rainfall (m) on two exam dates in each prefecture each year}
-  \includegraphics[width = 0.9\textwidth]{../Output/images/rainfall_diff.pdf}
-  \label{fig:rainfall_diff}
-  \footnotesize
-  \begin{tablenotes}
-    \item Notes:
-      Rainfall (mm) in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
-      Average across two test days in each year is shown in the figure.
-      The prefectures are ordered by the mean rainfall across years (lowest to left and highest to right).
-  \end{tablenotes}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \caption{Average hourly snowfall (m) on two exam dates in each prefecture each year}
-  \includegraphics[width = 0.9\textwidth]{../Output/images/snowfall_diff.pdf}
-  \label{fig:snowfall_diff}
-  \footnotesize
-  \begin{tablenotes}
-    \item Notes:
-      Snowfall (m) in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
-      Average across two test days in each year is shown in the figure.
-      The prefectures are ordered by the mean snowfall across years (lowest to left and highest to right).
-  \end{tablenotes}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \caption{Average cumulated snow (m) on two exam dates in each prefecture each year}
-  \includegraphics[width = 0.9\textwidth]{../Output/images/cum_snow_diff.pdf}
-  \label{fig:cum_snow_diff}
-  \footnotesize
-  \begin{tablenotes}
-    \item Notes:
-      Cumulated snow (m) in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
-      Average across two test days in each year is shown in the figure.
-      The prefectures are ordered by the mean cumulated snow across years (lowest to left and highest to right).
-  \end{tablenotes}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \caption{Deviation of temperatures from within-prefecture averages}
-  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff_by_year.pdf}
-  \label{fig:temperature_diff_by_year}
-  \footnotesize
-  \begin{tablenotes}
-    \item Notes:
-      Temperature in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
-      Deviations of average temperatures across two test days from their within-prefecture means are shown in the figure by year.
-      In each panel, red dots are the deviations in the year shown above and gray dots are the deviations in the other years.
-      The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
-  \end{tablenotes}
-\end{figure}
 

### 2023-12-11 Writeups/paper.tex
updated

@@
     Any errors are the sole responsibility of the author.
+    The author declares that he has no relevant or material financial interests that relate to the research described in this paper.
   }
@@
   \noindent Keywords: Temperature, Education, University matriculation, Cognitive performance
+  \vspace{1cm}
+  JEL Codes: I21, Q54, J24
 \end{abstract}
@@
 One such factor is temperature:
-heat on exam days has been shown to affect exam results in high-stakes settings \citep{Park2020a, GraffZivin2020}.
+heat on exam days has been shown to affect exam results in high-stakes settings \citep{Park2020a, GraffZivin2020, Melo2019}.
 What has been less studied in the literature is the impact of \textit{low} temperature.\footnote{
@@
 
-I use the weather on the dates of the Center Test and investigate its effect on matriculation for the University of Tokyo (UTokyo henceforth).
+Unlike the settings in the previous studies looking at the heat effects on exam scores, the score data of individual exam takers or even the aggregated exam score information are not easily accessible to researchers.
+To overcome this limitation, I use the weather on the dates of the Center Test and investigate its effect on matriculation for the University of Tokyo (UTokyo henceforth).
 UTokyo is a national university known to be the most prestigious in Japan.\footnote{
@@
 Changing the temperature on the exam dates from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
-The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
-These include preparing waiting rooms for exam takers to warm up to equalize their pre-exam conditions or adjusting the importance of the scores at the Center Test in the admissions process.
+%The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
+%These include preparing waiting rooms for exam takers to warm up to equalize their pre-exam conditions or adjusting the importance of the scores at the Center Test in the admissions process.
 
-This study mainly contributes to the recent but growing literature on the effects of climate factors on the outcome of high-stakes exams.
-Several previous studies have found the adverse effect of high temperature on learning, which exacerbates performance at exams \citep{Park2020b, Cho2017}.
-More closely to my study, \citet{GraffZivin2020} and \citet{Park2020a} show that heat on exam dates decreases the scores at high-stakes exams in China and the U.S., respectively.
-Considering the importance of the exam results for later life outcomes, it is important to understand how external factors such as temperature affect exam performance and what can be done to ameliorate such effects.
-To complement the literature, I investigate the effect of \textit{low} temperature on exam performance.
-
-This study also has a contribution to the literature on the economic impact of low temperature.
-It has been shown with controlled experiments that cold stresses negatively affect such things as cognitive ability and memory, as reviewed in \citet{Taylor2016}.
-However, evidence based on data in the field is scarce.
-Country-level studies have shown a non-linear effect of temperature on economic growth, that is, both low and high temperature have a negative impact \citep{Burke2015}.
-One study based on microdata is \citet{Stevens2017}, who finds a negative impact of low temperature on labor productivity of blueberry pickers in California.
+This study mainly contributes to the recent but growing literature on the effects of climate factors on the outcome of high-stakes exams \citep{Park2020b, Cho2017}.
+I also contribute to the literature on the economic impact of low temperature.
+Whereas it has been shown with controlled experiments that cold stresses negatively affect such things as cognitive ability and memory, as reviewed in \citet{Taylor2016}, evidence based on data in the field is scarce \citep{Burke2015, Stevens2017}.
 I use prefecture-level information to investigate how low temperature affects cognitive performance in a high-stakes exam.
@@
 This study proceeds as follows.
-In Section \ref{sec:background}, the context of this study is introduced.
 Section \ref{sec:data} describes the data. 
@@
 In Section \ref{sec:results}, I present the empirical results, and Section \ref{sec:conclusion} concludes.
+
+\section{Data}\label{sec:data}
+
+I use two sets of data: weather and matriculation for UTokyo.
+For weather information, I obtain data from \Citeauthor{jma}.
+Their website maintains the past weather across Japan.
+Based on hourly weather on exam dates in prefecture capitals, I use average weather between 6 AM and 6 PM.
+Prefecture capitals tend to be the most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located in prefecture capitals.
+
+For matriculation information for UTokyo, I use University Basic Information by \Citeauthor{univ_info}.
+This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
+I calculate the matriculation shares of each prefecture as the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.
+The summary statistics are provided in Table \ref{tab:sum_stat}.
+
+\begin{table}[!htbp]
+  \centering
+  \caption{Summary Statistics}
+  \resizebox{0.8\linewidth}{!}{
+  \input{"../Output/tex/sum_stat.tex"}
+  }
+  \label{tab:sum_stat}
+  \footnotesize
+  \begin{tablenotes}
+    \item 
+      Notes:
+      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
+  \end{tablenotes}
+\end{table}
+
+\section{Empirical Strategy}\label{sec:empirical_strategy}
+
+I analyze the effect of temperature and other weather variables on exam dates on the matriculation share for UTokyo.
+The reason why I use the matriculation share for UTokyo is as follows:
+consider a matriculation share for a middle-ranked university.
+Suppose also that low temperature has a negative impact on exam scores.
+Then, 
+(i) students in the prefecture who would have gotten into the middle-ranked university if the temperature were higher may end up in a lower-ranked university instead, but
+(ii) students in the prefecture who would have gotten into a higher-ranked university may end up in the middle-ranked university instead.
+Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
+However, the second effect is unlikely to be large for UTokyo since it is known to be the best university in Japan.\footnote{
+  \citet{Kawaguchi2008} describes that ``The University of Tokyo has occupied the top position of the single-peaked university hierarchy since its establishment in 1877.''
+}
+Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse performance at the Center Test.\footnote{
+  Appendix \ref{sec:background} details the admission system for UTokyo.
+}
+
+In the analyses, the outcome variable, $Y_{jt}$, is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
+The main right-hand side variable is temperature on the exam dates.
+To allow for non-linear effects of temperature on the outcome, I use the 3-$^o$C temperature intervals.
+%\footnote{
+%  The results with a linear specification are shown in Appendix \ref{sec:appendix_table} and will be discussed below.
+%}
+Let $T_{jt}^k$ represent the $k$'th temperature bin.
+I also include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates as a vector $X_{jt}$.
+As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
+Finally, the error term is represented as $\epsilon_{jt}$.
+
+Given the above notation, I run the following regression equation:
+\begin{equation*}
+  Y_{jt} = \sum_k T_{jt}^k + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
+\end{equation*}
+I exploit the variation of temperature on exam dates, which I consider exogenous after controlling for prefecture-specific time-invariant factors and time-varying aggregate shocks through prefecture and year fixed effects.
+The standard errors are clustered at the prefecture level.
+As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam dates.\footnote{
+  Figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
+}$^,$\footnote{
+  The figure shows that temperature is low for most prefectures in some years (eg. 2017) and high in other years (eg. 2019).
+  This can bring up a concern that temperature \textit{deviations} from the prefecture average have limited variations within each year.
+  If this were the case, most variations for estimation would be absorbed by prefecture fixed effects and year fixed effects.
+  Figure \ref{fig:temperature_diff_by_year} shows that, even within each year, the temperature deviations have large variations across prefectures.
+}
+
+\begin{figure}[H]
+  \centering
+  \caption{Average temperature (\degree C) on two exam dates in each prefecture each year}
+  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
+  \label{fig:temperature_diff}
+  \footnotesize
+  \begin{tablenotes}
+    \item Notes:
+      Temperature in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
+      The average across two test days in each year is shown in the figure.
+      The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
+  \end{tablenotes}
+\end{figure}
+
+\section{Results}\label{sec:results}
+
+The main empirical results are provided in Table \ref{tab:main_reg}.
+Without other weather variables, the estimates in column (1) show a negative and statistically significant impact of cold weather.
+Since the mean matriculation share is $2.08$\%, a decrease in the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest temperature bin (below 0 $^o$C) results in the lower matriculation share by 9\%.
+Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$\%.
+Therefore, the same temperature change decreases the matriculation share by 22\% of the median value.
+
+In column (2), I add rainfall and snowfall in the regressions.
+While temperature coefficients are barely affected, I find that rainfall and snowfall on the exam dates do not impact the matriculation shares.
+In column (3), instead of snowfall on the exam dates, I use cumulated snow on the ground and find its negative impact on the outcome. 
+To capture the effect of the existence of a certain amount of snow on the ground, column (4) allows a non-linear effect of cumulated snow.
+The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage points.
+These results suggest that not only temperature but also snow on the ground on the exam dates affect exam performance.
+
+Two points are worth noting.
+First, Table \ref{tab:linear_reg} shows the results with linear specifications.
+While the point estimates for temperature are positive, which means matriculation shares are higher if an exam is held on warmer days, they are statistically insignificant. 
+This could be due to the plateau effect of temperature above 6 $^o$C in Table \ref{tab:main_reg}.
+Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.
+Secondly, following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual the Center Test affect the matriculation shares.
+The results in Table \ref{tab:reg_placebo_exam} show not only that the weather one year after the Center Test has insignificant impacts on matriculation shares but also including the weather variables one year after the Center Test barely changes the coefficients on contemporaneous weather variables.
+This indicates that the results in \ref{tab:main_reg} capture the effect of transitory shocks on the exam dates.
+In Table \ref{tab:reg_pre10}, I include the average weather variables for 10 days before the exams and run regressions.
+The coefficients are statistically insignificant, which suggests that the effects of weather on preparation for the exam is secondary and the weather on the exam dates has the primary impact on exam scores.
+
+\begin{table}[H]
+  \center
+  \caption{Regression: Matriculation share (\%) and weather on exam dates}
+  \footnotesize
+  \input{"../Output/tex/main_reg.tex"}
+  \label{tab:main_reg}
+  \small
+  \begin{tablenotes}
+    \item
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
+      Temperature intervals do not contain the left ends.
+      Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{table}
+
+\section{Conclusion}\label{sec:conclusion}
+
+This paper studies the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
+I use the matriculation share for the most prestigious university in Japan, the University of Tokyo, as an outcome.
+Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
+This study fills the gap by identifying the causal impact of winter weather on exam results.
+
+The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam dates.
+Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage points, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
+Moreover, having more than 10cm of snow on the ground decreases the share by 0.11 percentage points.
+
+The results in this study have implications for the admissions process of universities.
+Recognizing the limitation of measuring students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
+Examples include extracurricular activities and personal statements, which are actively utilized in other countries such as the United States.
+Also, universities may adjust the weights for the Center Test and the second-stage exam.
+Since the second-stage exams are held at each university, this rules out the possibility that exam takers at different places are affected differently by their conditions.
+Given the importance of exam results for later life outcomes of students, it is desirable that universities take measures to mitigate the effect of seemingly irrelevant factors on admission.
+
+\clearpage
+\bibliographystyle{apalike}
+\bibliography{todai}
+
+\appendix
 
@@
 
-In summary, results at the Center Test are crucial for applicants for UTokyo.
-This study will investigate how external factors such as temperature and weather on the dates of the Center Test affect matriculation for UTokyo.
-
-\section{Data}\label{sec:data}
-
-I use two sets of data: weather and matriculation for UTokyo.
-For weather information, I obtain data from \Citeauthor{jma}.
-Their website maintains the past weather across Japan.
-Based on hourly weather on exam dates in prefecture capitals, I use average weather between 6 AM and 6 PM.
-Prefecture capitals tend to be the most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located in prefecture capitals.
-
-For matriculation information for UTokyo, I use University Basic Information by \Citeauthor{univ_info}.
-This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
-I calculate the matriculation shares of each prefecture as the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
-  Due to the lack of information on the number of admitted students by prefecture, I use the information on matriculation.
-  For UTokyo, the number of admissions and the number of matriculations are very close:
-  In 2020, among 3,083 admitted students, 3,064 students matriculated at UTokyo.
-}
-
-The summary statistics are provided in Table \ref{tab:sum_stat}.
-Whereas the mean matriculation share is $2.08 \%$, the median share is much smaller ($0.79 \%$).\footnote{
-  Since there are matriculations from foreign high schools, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
-  I do not consider matriculations of students from foreign high schools in the analyses since the majority of the students are admitted through a process called Special Screening Tests, which does not require Center Test scores.
-}
-This is because the distribution of the matriculation share is starkly skewed:
-while the matriculation shares of the top 5 prefectures amount to more than 60\%, many prefectures have less than 1\% shares (Figure \ref{fig:admission_map}).
-
-\begin{table}[H]
-  \centering
-  \caption{Summary Statistics}
-  \resizebox{0.8\linewidth}{!}{
-  \input{"../Output/tex/sum_stat.tex"}
-  }
-  \label{tab:sum_stat}
-  \footnotesize
-  \begin{tablenotes}
-    \item 
-      Notes:
-      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
-  \end{tablenotes}
-\end{table}
-
-\begin{figure}[H]
-  \centering
-  \caption{Map of matriculation shares (\%)}
-  \includegraphics[width = 0.7\textwidth]{../Output/images/admission_map.pdf}
-  \label{fig:admission_map}
-  \footnotesize
-  \begin{tablenotes}
-    \item Notes:
-      This map shows the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      The average of the shares across the years is shown in the map.
-      Although not shown in the legend due to the lack of space, the lightest color in the map means the matriculation share between 0 and 0.5\%.
-      The darkest prefecture in the east part of Japan is Tokyo.
-  \end{tablenotes}
-\end{figure}
-
-\section{Empirical Strategy}\label{sec:empirical_strategy}
-
-I analyze the effect of temperature and other weather variables on exam dates on the matriculation share for UTokyo.
-The reason why I use the matriculation share for UTokyo is as follows:
-consider a matriculation share for a middle-ranked university.
-Suppose also that low temperature has a negative impact on exam scores.
-Then, 
-(i) students in the prefecture who would have gotten into the middle-ranked university if the temperature were higher may end up in a lower-ranked university instead, but
-(ii) students in the prefecture who would have gotten into a higher-ranked university may end up in the middle-ranked university instead.
-Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
-However, the second effect is unlikely to be large for UTokyo since it is known to be the best university in Japan.\footnote{
-  \citet{Kawaguchi2008} describes that ``The University of Tokyo has occupied the top position of the single-peaked university hierarchy since its establishment in 1877.''
-}
-Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse performance at the Center Test.
-
-In the analyses, the outcome variable, $Y_{jt}$, is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
-%Let $T_{jt}$ be the average temperature across two exam dates in $j$ in year $t$.
-%I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
-The main right-hand side variable is temperature on the exam dates.
-To allow for non-linear effects of temperature on the outcome, I use the 3-$^o$C temperature intervals.\footnote{
-  The results with a linear specification are shown in Appendix \ref{sec:appendix_table} and will be discussed below.
-}
-Let $T_{jt}^k$ represent the $k$'th temperature bin.
-I also include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates as a vector $X_{jt}$.
-As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
-Finally, the error term is represented as $\epsilon_{jt}$.
-
-Given the above notation, I run the following regression equation:
-\begin{equation*}
-  Y_{jt} = \sum_k T_{jt}^k + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
-\end{equation*}
-I exploit the variation of temperature on exam dates, which I consider exogenous after controlling for prefecture-specific time-invariant factors and time-varying aggregate shocks through prefecture and year fixed effects.
-As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam dates.\footnote{
-  Figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
-}$^,$\footnote{
-  The figure shows that temperature is low for most prefectures in some years (eg. 2017) and high in other years (eg. 2019).
-  This can bring up a concern that temperature \textit{deviations} from the prefecture average have limited variations within each year.
-  If this were the case, most variations for estimation would be absorbed by prefecture fixed effects and year fixed effects.
-  Figure \ref{fig:temperature_diff_by_year} shows that, even within each year, the temperature deviations have large variations across prefectures.
-}
-
-One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take the Center Test in the same municipality.
-This means that, for such students, the weather at the exam sites is measured with errors.
-The primary reason for this to happen is that a senior student at a high school located in a prefecture different from his home prefecture fails to get into any university and retake the Center Test next year in his home prefecture.
-In 2020, 38\% of the admitted students were high school graduates.
-In the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
-Hence, if I use this number as an approximation for the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of students whose exam-date weather is measured with errors for the reason above as $0.38 * 0.039 = 1.5\%$.
-Given this small proportion of exam takers who are susceptible to measurement error, I consider that the bias on the estimates is negligible.
-Another potential concern is that, as discussed in footnote \ref{footnote:prefecture}, students in several municipalities in a prefecture could take the Center Test in a neighboring prefecture.
-Since neighboring prefectures are geographically close, I consider that the magnitude of the measurement error is small.
-
-\begin{figure}[H]
-  \centering
-  \caption{Average temperature (\degree C) on two exam dates in each prefecture each year}
-  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
-  \label{fig:temperature_diff}
-  \footnotesize
-  \begin{tablenotes}
-    \item Notes:
-      Temperature in prefecture capitals between 6 AM and 6 PM on days of the Center Test is used.
-      The average across two test days in each year is shown in the figure.
-      The prefectures are ordered by the mean temperature across years (lowest to left and highest to right).
-  \end{tablenotes}
-\end{figure}
-
-\section{Results}\label{sec:results}
-
-The main empirical results are provided in Table \ref{tab:main_reg}.
-The standard errors are clustered at the prefecture level.
-Without other weather variables, the estimates in column (1) show a negative and statistically significant impact of cold weather.
-Since the mean matriculation share is $2.08$\%, a decrease in the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest temperature bin (below 0 $^o$C) results in the lower matriculation share by 9\%.
-Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$\%.
-Therefore, the same temperature change decreases the matriculation share by 22\% of the median value.
-
-In column (2), I add rainfall and snowfall in the regressions.
-While temperature coefficients are barely affected, I find that rainfall and snowfall on the exam dates do not impact the matriculation shares.
-In column (3), instead of snowfall on the exam dates, I use cumulated snow on the ground and find its negative impact on the outcome. 
-To capture the effect of the existence of a certain amount of snow on the ground, column (4) allows a non-linear effect of cumulated snow.
-The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage points.
-These results suggest that not only temperature but also snow on the ground on the exam dates affect exam performance.
-
-Two points are worth noting.
-First, Table \ref{tab:linear_reg} shows the results with linear specifications.
-While the point estimates for temperature are positive, which means matriculation shares are higher if an exam is held on warmer days, they are statistically insignificant. 
-This could be due to the plateau effect of temperature above 6 $^o$C in Table \ref{tab:main_reg}.
-Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.
-Secondly, following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual the Center Test affect the matriculation shares.
-The results in Table \ref{tab:reg_placebo_exam} show not only that the weather one year after the Center Test has insignificant impacts on matriculation shares but also including the weather variables one year after the Center Test barely changes the coefficients on contemporaneous weather variables.
-This indicates that the results in \ref{tab:main_reg} capture the effect of transitory shocks on the exam dates.
-
-\begin{table}[H]
-  \center
-  \caption{Regression: Matriculation share (\%) and weather on exam dates}
-  \footnotesize
-  \input{"../Output/tex/main_reg.tex"}
-  \label{tab:main_reg}
-  \small
-  \begin{tablenotes}
-    \item
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
-      Temperature intervals do not contain the left ends.
-      Standard errors are clustered at the prefecture level.
-  \end{tablenotes}
-\end{table}
-
-One possible interpretation of the results is that the estimates in Table \ref{tab:main_reg} reflect the effects of weather on preparation for the exam.
-For instance, cold weather can make it hard for students to focus on studying, as suggested by existing studies \citep{Taylor2016}.
-Also, snowfall can prevent students from going to high schools or cram schools for studying.
-Due to the serial correlation between the weather on exam dates and the weather days or weeks before the exam, my regression in Table \ref{tab:main_reg} could capture these effects.
-To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
-The results in columns (1) and (2) in Table \ref{tab:reg_pre10} show statistically insignificant estimates for the temperature variables.
-Moreover, including the weather variables for 10 days before the exams barely changes the estimates of the weather variables on the exam dates (columns (3) and (4)).
-These suggest that the negative impacts of low temperature found in Table \ref{tab:main_reg} are mainly caused by the temperature on exam dates rather than temperature before exams.
-
-In columns (1) and (2), the coefficients on snowfall and cumulated snow on the ground are statistically significant.
-Combined with the finding in Table \ref{tab:main_reg} that cumulated snow on the ground on the exam dates decreases students' performance, two potential explanations can be given:
-(i) snow before the exams can adversely affect students' preparation due to, for instance, more difficulty in going to high schools or cram schools, and
-(ii) snowfall before the exams cumulates snow on the ground and students' performance is negatively affected by the cumulated snow on the exam dates.
-Including the weather variables on the exam dates, columns (3) and (4) show that only cumulated snow on exam dates has a significant impact on the outcome.
-This suggests that the second mechanism is dominant.
-
-\begin{table}[H]
-  \center
-  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
-  \scriptsize
-  \input{"../Output/tex/reg_pre10.tex"}
-  \label{tab:reg_pre10}
-  \scriptsize
-  \begin{tablenotes}
-    \item
-      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
-      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
-      For weather variables with "(exam dates)", I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
-      For weather variables with "(previous 10 days)", I use their averages in prefecture capitals between 10 days before and 1 day before the first day of the Center Test.
-      Temperature intervals do not contain the left ends.
-      Standard errors are clustered at the prefecture level.
-  \end{tablenotes}
-\end{table}
-
-\section{Conclusion}\label{sec:conclusion}
-
-This paper studies the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
-I use the matriculation share for the most prestigious university in Japan, the University of Tokyo, as an outcome.
-Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
-This study fills the gap by identifying the causal impact of winter weather on exam results.
-
-The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam dates.
-Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage points, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
-Moreover, having more than 10cm of snow on the ground decreases the share by 0.11 percentage points.
-
-The results in this study have implications for the admissions process of universities.
-Recognizing the limitation of measuring students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
-Examples include extracurricular activities and personal statements, which are actively utilized in other countries such as the United States.
-Also, universities may adjust the weights for the Center Test and the second-stage exam.
-Since the second-stage exams are held at each university, all exam takers are exposed to similar environments.
-This rules out the possibility that exam takers at different places are affected differently by their conditions.
-Given the importance of exam results for later life outcomes of students, it is desirable that universities take measures to mitigate the effect of seemingly irrelevant factors on admission.
-
-\clearpage
-\bibliographystyle{apalike}
-\bibliography{todai}
-
-\appendix
+%In summary, results at the Center Test are crucial for applicants for UTokyo.
+%This study will investigate how external factors such as temperature and weather on the dates of the Center Test affect matriculation for UTokyo.
 
@@
       I represent the contemporaneous weather variables with ``($t$)'' and the weather one year after the Center Test with ``($t + 1$).''
+      Temperature intervals do not contain the left ends.
+      Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{table}
+
+\begin{table}[H]
+  \center
+  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
+  \scriptsize
+  \input{"../Output/tex/reg_pre10.tex"}
+  \label{tab:reg_pre10}
+  \scriptsize
+  \begin{tablenotes}
+    \item
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      For weather variables with "(exam dates)", I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
+      For weather variables with "(previous 10 days)", I use their averages in prefecture capitals between 10 days before and 1 day before the first day of the Center Test.
       Temperature intervals do not contain the left ends.

### 2023-12-11 Codes/R/SumStat/sumstat.R

@@ -22,7 +22,11 @@ reg_df <- left_join(
 
 list(
   function(x) sum(!is.na(x)), 
-  mean, sd, median, min, max
+  function(x) mean(x, na.rm = TRUE),
+  function(x) sd(x, na.rm = TRUE),
+  function(x) median(x, na.rm = TRUE),
+  function(x) min(x, na.rm = TRUE),
+  function(x) max(x, na.rm = TRUE)
   ) %>% 
   map(
   function(x) 

### 2024-02-10 Writeups/paper.tex
revision

@@
 
+Not only low temperature but also snow can negatively affect students' performance.
+Snow-covered roads can reduce students' body temperature on their way to exam sites.
+Furthermore, snow can delay public transportation, which can impose an additional mental burden on exam takers.
+This manuscript considers the effect of snow in the empirical analyses as well.
+
 Unlike the settings in the previous studies looking at the heat effects on exam scores, the score data of individual exam takers or even the aggregated exam score information are not easily accessible to researchers.
@@
 
+In admission for UTokyo, scores at the Center Test are used for two purposes.
+First, the scores are used for eligibility to take the second-stage exam.
+Thresholds varying across years and majors are set, and if scores at the Center Test are below the thresholds, the students cannot take the second-stage exam.
+Secondly, the scores at the Center Test are taken into consideration for admission.
+The final score of a student is calculated by the weighted sum of exam scores at the first- and second-stage exams.
+Through both of these channels, the cold and snowy weather on exam days can affect the admission for UTokyo.
+
 The econometric analyses show that low temperature and snow cumulated on the ground on exam dates reduce the matriculation share.
 The estimates are not only statistically but also economically significant.
-Changing the temperature on the exam dates from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
+Changing the temperature on the exam dates from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share by 0.18 percentage points, which amounts to 9\% of the average or 22\% of the median matriculation shares.
 %The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
@@
 Their website maintains the past weather across Japan.
-Based on hourly weather on exam dates in prefecture capitals, I use average weather between 6 AM and 6 PM.
+Based on hourly weather on exam dates in prefecture capitals, I use average weather between 6 AM and 6 PM across both exam days.\footnote{
+  Later in the paper, I also discuss the analyses using average weather on the first and second exam days separately.
+}
 Prefecture capitals tend to be the most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located in prefecture capitals.
+
+I use the average between 6 AM and 6 PM to holistically consider the effect of temperature both during going to exam sites and during exam time.
+\citet{Heyes2019} point out the potential importance of temperature during commute on decision making of court judges, and temperature during exams can directly affect the cognitive ability of exam takers.
+In the appendix, I investigate the differential impacts of temperature before the exam and during the exam.
 
@@
 I also include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates as a vector $X_{jt}$.
+This allows me to explore the distinct role in the winter weather's effect.
+For instance, low temperature primarily affects exam performance through lower body temperature.
+On the other hand, on top of the effect on body temperature, snow can affect public transportation to exam sites, which can impose more stress on exam takers.
 As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
@@
 Since the mean matriculation share is $2.08$\%, a decrease in the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest temperature bin (below 0 $^o$C) results in the lower matriculation share by 9\%.
-Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$\%.
+Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.76$\%.
 Therefore, the same temperature change decreases the matriculation share by 22\% of the median value.
@@
 \end{table}
+
+I further conduct the following sets of analyses.
+First, to explore the differential impacts of temperature and snow before and during exams, I run regressions with average weather variables between 6 AM and 9 AM and between 10 AM and 6 PM.
+The results are shown in Appendix Table \ref{tab:morning_exam_reg}.
+It suggests that the low temperature in the morning has a large impact on exam performance, while the point estimates of the effects are similar between the two weather measures.
+Note that the results need to be interpreted with caution due to the high correlation between the weather variables before and during exams.
+For example, the correlation between temperatures before and during exams is 0.87.
+
+I also conduct additional analyses on the differential impact of weather on the first and second days.
+The results are provided in Appendix Table \ref{tab:first_second_day_reg}.
+The weather on these two days has quantitatively similar impacts on the outcome.
+Note that since there is no subject-specific weight on Center Test scores, weathers on both days are equally important.
+Although Column (3) suggests that the cumulated snow on the first day is important, this needs to be interpreted cautiously since this variable is highly correlated between two days (the correlation coefficient is 0.99).
+
+Finally, I investigate if low temperature and snow have an interaction effect.
+For this, first I separate the analysis samples by whether snow is cumulated less than 10 cm or not.
+I also interact the temperature variables with an indicator for snow cumulated more than 10 cm in the regressions.
+The results are provided in Appendix Table \ref{tab:hetero_exam_reg}.
+Although the interpretation requires caution due to the small variation in temperature for observations with less snow cumulated, the estimates suggest that there is a limited interactive effect between temperature and snow.
 
@@
 
+\begin{table}[!htbp]
+  \centering
+  \caption{Weather effect (morning vs during-exam)}
+  \resizebox{0.6\linewidth}{!}{
+  \input{"../Output/tex/morning_exam_reg.tex"}
+  }
+  \label{tab:morning_exam_reg}
+  \footnotesize
+  \begin{tablenotes}
+    \item 
+      Notes:
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables in prefecture capitals between 6 AM and 9 AM for morning variables and 10 AM to 6 PM for during-exam variables on days of the Center Test.
+      Temperature intervals do not contain the left ends.
+      Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{table}
+
+\begin{table}[!htbp]
+  \centering
+  \caption{Weather effect (1st day vs 2nd day)}
+  \resizebox{0.6\linewidth}{!}{
+  \input{"../Output/tex/first_second_day_reg.tex"}
+  }
+  \label{tab:first_second_day_reg}
+  \footnotesize
+  \begin{tablenotes}
+    \item 
+      Notes:
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
+      Temperature intervals do not contain the left ends.
+      Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{table}
+
+\begin{table}[!htbp]
+  \centering
+  \caption{Weather effect (interaction between temperature and snow)}
+  \resizebox{0.6\linewidth}{!}{
+  \input{"../Output/tex/hetero_exam_reg.tex"}
+  }
+  \label{tab:hetero_exam_reg}
+  \footnotesize
+  \begin{tablenotes}
+    \item 
+      Notes:
+      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
+      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
+      I use weather variables in prefecture capitals between 6 AM and 6 PM on days of the Center Test.
+      Temperature intervals do not contain the left ends.
+      Standard errors are clustered at the prefecture level.
+  \end{tablenotes}
+\end{table}
+
 \setcounter{figure}{0}

### 2024-02-10 Codes/R/Data_clean/merge_data.R

@@ -18,12 +18,14 @@ reg_df <- left_join(
   admission_df,
   weather_exam_df %>% 
     group_by(prefecture, exam_year) %>% 
+    select(-c(exam_month, exam_day, exam_first_second)) %>% 
     summarise_all(mean),
   by = c("prefecture", "year" = "exam_year")
   ) %>% 
   left_join(
     weather_f1_df %>% 
       group_by(prefecture, exam_year) %>% 
+      select(-c(exam_month, exam_day, exam_first_second)) %>% 
       summarise_all(mean),
     by = c("prefecture", "year" = "exam_year")
   ) %>% 
@@ -33,6 +35,14 @@ reg_df <- left_join(
     temp_cut = relevel(as.factor(temp_cut), ref = 3),
     daytime_snowfall_m = daytime_snowfall_cm / 100,
     daytime_cum_snow_m = daytime_cum_snow_cm / 100,
+    morning_temp_cut = cut(morning_temperature_degree, c(-10, 0, 3, 6, 9, 25)),
+    morning_temp_cut = relevel(as.factor(morning_temp_cut), ref = 3),
+    morning_snowfall_m = morning_snowfall_cm / 100,
+    morning_cum_snow_m = morning_cum_snow_cm / 100,
+    exam_temp_cut = cut(exam_temperature_degree, c(-10, 0, 3, 6, 9, 25)),
+    exam_temp_cut = relevel(as.factor(exam_temp_cut), ref = 3),
+    exam_snowfall_m = exam_snowfall_cm / 100,
+    exam_cum_snow_m = exam_cum_snow_cm / 100,
     f1_temp_cut = cut(f1_temperature_degree, c(-10, 0, 3, 6, 9, 25)),
     f1_temp_cut = relevel(as.factor(f1_temp_cut), ref = 3),
     f1_snowfall_m = f1_snowfall_cm / 100,
@@ -43,7 +53,31 @@ reg_df <- left_join(
     cum_snow_pre10_m = cum_snow_pre10 / 100,
     )
 
+reg_df <- reg_df %>% 
+  left_join(
+    weather_exam_df %>% 
+      select(-c(exam_month, exam_day)) %>% 
+      pivot_wider(
+        id_cols = c(prefecture, exam_year),
+        names_from = exam_first_second,
[…]

### 2024-02-10 Codes/R/Data_clean/weather_clean.R

@@ -24,6 +24,38 @@ weather_hour_output <- weather_hour_df %>%
       ),
     by = c("prefecture", "year", "month", "day")
   ) %>% 
+  left_join(
+    weather_hour_df %>% 
+      filter(hour >= 6, hour <= 9) %>% 
+      group_by(prefecture, year, month, day) %>% 
+      summarise_at(
+          vars(temperature_degree, precipitation_mm, snowfall_cm, cum_snow_cm),
+          mean, na.rm = TRUE
+      ) %>% 
+      rename(
+        morning_temperature_degree = temperature_degree,
+        morning_precipitation_mm = precipitation_mm,
+        morning_snowfall_cm = snowfall_cm,
+        morning_cum_snow_cm = cum_snow_cm
+      ),
+    by = c("prefecture", "year", "month", "day")
+  ) %>% 
+  left_join(
+    weather_hour_df %>% 
+      filter(hour >= 10, hour <= 18) %>% 
+      group_by(prefecture, year, month, day) %>% 
+      summarise_at(
+          vars(temperature_degree, precipitation_mm, snowfall_cm, cum_snow_cm),
+          mean, na.rm = TRUE
+      ) %>% 
+      rename(
+        exam_temperature_degree = temperature_degree,
+        exam_precipitation_mm = precipitation_mm,
+        exam_snowfall_cm = snowfall_cm,
+        exam_cum_snow_cm = cum_snow_cm
+      ),
+    by = c("prefecture", "year", "month", "day")
+  ) %>% 
   group_by(prefecture, year, month) %>% 
   arrange(day, .by_group = TRUE) %>% 
   mutate(exam_first_second = row_number()) %>% 

### 2024-02-10 Codes/R/Regression/main_regression.R

@@ -167,3 +167,182 @@ list(res_1, res_2, res_3, res_4) %>%
     float = FALSE
   )
 
+# ===========================
+
+# day1 vs day2
+res1 <- felm(
+  admission_total_share ~  temp_cut_1 + daytime_precipitation_mm_1 + factor(daytime_cum_snow_m_1 > .1) | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res2 <- felm(
+  admission_total_share ~  temp_cut_2 + daytime_precipitation_mm_2 + factor(daytime_cum_snow_m_2 > .1) | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res3 <- felm(
+  admission_total_share ~ 
+    temp_cut_1 + temp_cut_2 + 
+    daytime_precipitation_mm_1 + daytime_precipitation_mm_2 + 
+    factor(daytime_cum_snow_m_1 > .1) + factor(daytime_cum_snow_m_2 > .1) | 
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+list(res1, res2, res3) %>% 
+  stargazer(
+    dep.var.labels = "Matriculation share (\\%)",
+    covariate.labels = c(
+      "Temperature (\\degree C) $\\le$ 0 (1st day)",
+      "Temperature (\\degree C) 0-3 (1st day)",
+      "Temperature (\\degree C) 6-9 (1st day)",
+      "Temperature (\\degree C) $>$ 9 (1st day)",
+      "Rainfall (mm) (1st day)",
+      "Cumulated snow $>$ 10 cm (1st day)",
+      "Temperature (\\degree C) $\\le$ 0 (2nd day)",
+      "Temperature (\\degree C) 0-3 (2nd day)",
+      "Temperature (\\degree C) 6-9 (2nd day)",
+      "Temperature (\\degree C) $>$ 9 (2nd day)",
+      "Rainfall (mm) (2nd day)",
+      "Cumulated snow $>$ 10 cm (2nd day)"
+    ),
+    title = "",
+    add.lines = list(
+      c("Prefecture FE", rep("Yes", 8)),
+      c("Year FE", rep("Yes", 8))
+    ),
+    type = "latex",
+    out = file.path(git_dir, "Output/tex/first_second_day_reg.tex"),
+    omit.stat = c("adj.rsq", "ser", "rsq"),
+    digits = 2,
[…]

### 2024-03-02 Codes/R/Data_clean/merge_data.R
updated for final revision

@@ -60,8 +60,13 @@ reg_df <- reg_df %>%
       pivot_wider(
         id_cols = c(prefecture, exam_year),
         names_from = exam_first_second,
-        values_from = c(daytime_temperature_degree, daytime_precipitation_mm, daytime_snowfall_cm, daytime_cum_snow_cm)
-        ),
+        values_from = c(
+          daytime_temperature_degree, 
+          daytime_precipitation_mm, 
+          daytime_snowfall_cm, 
+          daytime_cum_snow_cm
+        )
+      ),
   by = c("prefecture", "year" = "exam_year")
   ) %>% 
   mutate(

### 2024-03-02 Codes/R/Data_clean/weather_clean.R

@@ -1,6 +1,11 @@
 # Hourly weather ====================
 # Load data
-weather_hour_df <- read_csv(file.path(dropbox_dir, "Data/Raw/weather_hourly/all_weather_hour.csv"))
+weather_hour_df <- read_csv(
+  file.path(
+    dropbox_dir, 
+    "Data/Raw/weather_hourly/all_weather_hour.csv"
+  )
+)
 
 weather_hour_output <- weather_hour_df %>% 
   group_by(prefecture, year, month, day) %>% 

### 2024-03-02 Codes/R/Regression/appendix_regression.R

@@ -1,5 +1,5 @@
 # Appendix ==============
-# Table A.1
+# Table B.1
 # Regression with linear specification ==========================
 
 res_1 <- felm(
@@ -48,7 +48,7 @@ list(res_1, res_2, res_3, res_4) %>%
     float = FALSE
   )
 
-# Table A.2
+# Table B.2
 # Placebo regression with lead weather =====================
 
 res_1 <- felm(
@@ -106,6 +106,240 @@ list(res_1, res_2, res_3, res_4) %>%
     ),
     type = "latex",
     out = file.path(git_dir, "Output/tex/reg_placebo_exam.tex"),
+    omit.stat = c("adj.rsq", "ser", "rsq"),
+    digits = 2,
+    float = FALSE
+  )
+
+# Table B.3
+# Regression with weather for the previous 10 days =====================
+
+res_1 <- felm(
+  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10 |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+  )
+
+res_2 <- felm(
+  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10 |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_3 <- felm(
+  admission_total_share ~ 
+    temp_cut + daytime_precipitation_mm + daytime_snowfall_cm +
+    temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10 |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+res_4 <- felm(
+  admission_total_share ~ 
+    temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm +
+    temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10 |
+    prefecture + year | 0 | prefecture, 
+  data = reg_df
+)
+
+list(res_1, res_2, res_3, res_4) %>% 
+  stargazer(
+    dep.var.labels = "Matriculation share (\\%)",
+    order = c(seq(1, 4), seq(5, 7), seq(8, 11), seq(12, 14)),
+    covariate.labels = c(
+      "Temperature (\\degree C) $\\le$ 0 (exam dates)",
+      "Temperature (\\degree C) 0-3 (exam dates)",
[…]

### 2024-03-02 Codes/R/Regression/main_regression.R

@@ -50,299 +50,3 @@ list(res_1, res_2, res_3, res_4) %>%
     float = FALSE
   )
 
-# Regression table for beamer
-list(res_2, res_3, res_4) %>% 
-  stargazer(
-    dep.var.labels = "Matriculation share (\\%)",
-    keep = c(
-      "^[^temp_cut]"
-    ),
-    covariate.labels = c(
-      "Rainfall (mm)",
-      "Snowfall (cm)",
-      "Cumulated snow (cm)",
-      "Cumulated snow $>$ 10 cm"
-    ),
-    title = "",
-    add.lines = list(
-      c("Temperature bins", rep("Yes", 3)),
-      c("Prefecture FE", rep("Yes", 3)),
-      c("Year FE", rep("Yes", 3))
-    ),
-    type = "latex",
-    out = file.path(git_dir, "Output/tex/main_reg_beamer.tex"),
-    omit.stat = c("adj.rsq", "ser", "rsq"),
-    digits = 2,
-    float = FALSE
-  )
-
-# Table 3 -------------
-# Regression with weather for the previous 10 days =====================
-
-res_1 <- felm(
-  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10 |
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-  )
-
-res_2 <- felm(
-  admission_total_share ~ temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10 |
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_3 <- felm(
-  admission_total_share ~ 
-    temp_cut + daytime_precipitation_mm + daytime_snowfall_cm +
-    temp_cut_pre10 + precipitation_pre10_sum + snowfall_pre10 |
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-res_4 <- felm(
-  admission_total_share ~ 
-    temp_cut + daytime_precipitation_mm + daytime_cum_snow_cm +
-    temp_cut_pre10 + precipitation_pre10_sum + cum_snow_pre10 |
-    prefecture + year | 0 | prefecture, 
-  data = reg_df
-)
-
-list(res_1, res_2, res_3, res_4) %>% 
-  stargazer(
-    dep.var.labels = "Matriculation share (\\%)",
[…]

### 2024-03-02 Codes/R/SumStat/weather_diff.R

@@ -2,7 +2,13 @@
 weather_df <- read_csv(file.path(dropbox_dir, "Data/Processed/weather_on_exam_day.csv"))
 
 # Load location information
-loc_df <- read_delim(file.path(dropbox_dir, "Data/Raw/weather_station/weather_station_id.txt"), delim = ",")
+loc_df <- read_delim(
+  file.path(
+    dropbox_dir, 
+    "Data/Raw/weather_station/weather_station_id.txt"
+  ), 
+  delim = ","
+)
 prefecture_order <- loc_df$prefecture
 
 weather_df_avg <- weather_df %>% 
@@ -12,7 +18,12 @@ weather_df_avg <- weather_df %>%
     ) %>% 
   group_by(prefecture, exam_year, exam_month) %>% 
   summarise_at(
-    vars(daytime_temperature_degree, daytime_cum_snow_cm, daytime_snowfall_cm, daytime_precipitation_mm), 
+    vars(
+      daytime_temperature_degree, 
+      daytime_cum_snow_cm, 
+      daytime_snowfall_cm, 
+      daytime_precipitation_mm
+    ), 
     mean
     ) %>% 
   mutate(prefecture = rev(factor(prefecture, levels = prefecture_order)))
@@ -64,7 +75,11 @@ temp_diff_list <- map(
   seq(2012, 2020),
   function(x) weather_df_avg %>% 
     group_by(prefecture) %>% 
-    mutate(daytime_temperature_degree = daytime_temperature_degree - mean(daytime_temperature_degree)) %>% 
+    mutate(
+      daytime_temperature_degree = (
+        daytime_temperature_degree - mean(daytime_temperature_degree)
+      )
+    ) %>% 
     ggplot(aes(
       x = prefecture, y = daytime_temperature_degree, color = (exam_year == x),
       alpha = (exam_year == x) * 1.0 + (exam_year != x) * 0.9
